---
title: "AICc_bodycomp"
author: "Abby Host"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

## Body Size as response variable, lower river
```{r}
## Explanatory variables can include: 
  # run-timing group
  # year
  # sex

# control for = river mile/collection_location, so include this in all models 

#first model, null model
  # body size ~ 1 

#second model
  # body size ~ collection_location (categorical variable of site)

#third model 
  # body size ~ collection_location + run-timing

#fourth model
  # body size ~ collection_location + sex

#fifth model
  # body size ~ collection_location + year

#sixth model
  # body size ~ collection_location + run-timing group + sex

#seventh model
  # body size ~ collection_location + run-timing group + year

#eighth model
  # body size ~ collection_location + sex + year

#ninth model 
  # body size ~ collection_location + year + sex + sex:year

#tenth model
  # body size ~ collection_location + run-timing group + sex + run-timing group:sex

#eleventh model 
  #body size ~ collection_location + run-timing group + year + run-timing group:year

#GLOBAL model
  # body size ~ collection_location + run-timing group + sex + year 

```

## Body Size as response variable, genetic stock
```{r}
## Explanatory variables can include: 
  # genetic stock
  # year
  # sex

# control for = river mile/collection_location, so include this in all models 

#first model, null model
  # body size ~ 1 

#second model
  # body size ~ collection_location (categorical variable of site)

#third model 
  # body size ~ collection_location + GSI

#fourth model
  # body size ~ collection_location + sex

#fifth model
  # body size ~ collection_location + year

#sixth model
  # body size ~ collection_location + GSI + sex

#seventh model
  # body size ~ collection_location + GSI + year

#eighth model
  # body size ~ collection_location + sex + year

#ninth model 
  # body size ~ collection_location + year + sex + sex:year

#tenth model
  # body size ~ collection_location + GSI + sex + GSI:sex

#eleventh model 
  #body size ~ collection_location + GSO + year + GSI:year

#GLOBAL model
  # body size ~ collection_location + GSI + sex + year 

```

## size-corrected mass as response variable, lower river
``` {r}
## Explanatory variables can include: 
  # run-timing group
  # year
  # sex

# control for = river mile/collection_location, so include this in all models 

#first model, null model
  # size-corrected mass ~ 1 

#second model
  # size-corrected mass ~ collection_location (categorical variable of site)

#third model 
  # size-corrected mass ~ collection_location + run-timing

#fourth model
  # size-corrected mass ~ collection_location + sex

#fifth model
  # size-corrected mass ~ collection_location + year

#sixth model
  # size-corrected mass ~ collection_location + run-timing group + sex

#seventh model
  # size-corrected mass ~ collection_location + run-timing group + year

#eighth model
  # size-corrected mass ~ collection_location + sex + year

#ninth model 
  # size-corrected mass ~ collection_location + year + sex + sex:year

#tenth model
  # size-corrected mass ~ collection_location + run-timing group + sex + run-timing group:sex

#eleventh model 
  #size-corrected mass ~ collection_location + run-timing group + year + run-timing group:year

#GLOBAL model
  # size-corrected mass ~ collection_location + run-timing group + sex + year 

```

## size-corrected mass as response variable, GSI
``` {r}
## Explanatory variables can include: 
  # GSI
  # year
  # sex

# control for = river mile/collection_location, so include this in all models 

#first model, null model
  # size-corrected mass ~ 1 

#second model
  # size-corrected mass ~ collection_location (categorical variable of site)

#third model 
  # size-corrected mass ~ collection_location + GSI

#fourth model
  # size-corrected mass ~ collection_location + sex

#fifth model
  # size-corrected mass ~ collection_location + year

#sixth model
  # size-corrected mass ~ collection_location + GSI + sex

#seventh model
  # size-corrected mass ~ collection_location + GSI + year

#eighth model
  # size-corrected mass ~ collection_location + sex + year

#ninth model 
  # size-corrected mass ~ collection_location + year + sex + sex:year

#tenth model
  # size-corrected mass ~ collection_location + GSI + sex + GSI:sex

#eleventh model 
  #size-corrected mass ~ collection_location + GSI + year + GSI:year

#GLOBAL model
  # size-corrected mass ~ collection_location + GSI + sex + year 

```

## energy density as response variable, lower river
``` {r}
## Explanatory variables can include: 
  # run-timing group
  # year
  # sex

# control for = river mile/collection_location, so include this in all models 

#first model, null model
  # energy density ~ 1 

#second model
  # energy density ~ collection_location (categorical variable of site)

#third model 
  # energy density ~ collection_location + run-timing

#fourth model
  # energy density ~ collection_location + sex

#fifth model
  # energy density ~ collection_location + year

#sixth model
  # energy density ~ collection_location + run-timing group + sex

#seventh model
  # energy density ~ collection_location + run-timing group + year

#eighth model
  # energy density ~ collection_location + sex + year

#ninth model 
  # energy density ~ collection_location + year + sex + sex:year

#tenth model
  # energy density ~ collection_location + run-timing group + sex + run-timing group:sex

#eleventh model 
  # energy density ~ collection_location + run-timing group + year + run-timing group:year

#GLOBAL model
  # energy density ~ collection_location + run-timing group + sex + year 

```

## energy density as response variable, GSI
``` {r}
## Explanatory variables can include: 
  # GSI
  # year
  # sex

# control for = river mile/collection_location, so include this in all models 

#first model, null model
  # energy density ~ 1 

#second model
  # energy density ~ collection_location (categorical variable of site)

#third model 
  # energy density ~ collection_location + GSI

#fourth model
  # energy density ~ collection_location + sex

#fifth model
  # energy density ~ collection_location + year

#sixth model
  # energy density ~ collection_location + GSI + sex

#seventh model
  # energy density ~ collection_location + GSI + year

#eighth model
  # energy density ~ collection_location + sex + year

#ninth model 
  # energy density ~ collection_location + year + sex + sex:year

#tenth model
  # energy density ~ collection_location + GSI+ sex + GSI:sex

#eleventh model 
  # energy density ~ collection_location + GSI + year + GSI:year

#GLOBAL model
  # energy density ~ collection_location + GSI + sex + year 

```

## total energy as response variable, lower river
``` {r}
## Explanatory variables can include: 
  # run-timing group
  # year
  # sex

# control for = river mile/collection_location, so include this in all models 

#first model, null model
  # total energy ~ 1 

#second model
  # total energy ~ collection_location (categorical variable of site)

#third model 
  # total energy ~ collection_location + run-timing

#fourth model
  # total energy ~ collection_location + sex

#fifth model
  # total energy ~ collection_location + year

#sixth model
  # total energy ~ collection_location + run-timing group + sex

#seventh model
  # total energy ~ collection_location + run-timing group + year

#eighth model
  # total energy ~ collection_location + sex + year

#ninth model 
  # total energy ~ collection_location + year + sex + sex:year

#tenth model
  # total energy ~ collection_location + run-timing group + sex + run-timing group:sex

#eleventh model 
  # total energy ~ collection_location + run-timing group + year + run-timing group:year

#GLOBAL model
  # total energy ~ collection_location + run-timing group + sex + year 

```

## total energy as response variable, GSI
``` {r}
## Explanatory variables can include: 
  # GSI
  # year
  # sex

# control for = river mile/collection_location, so include this in all models 

#first model, null model
  # total energy ~ 1 

#second model
  # total energy ~ collection_location (categorical variable of site)

#third model 
  # total energy ~ collection_location + GSI

#fourth model
  # total energy ~ collection_location + sex

#fifth model
  # total energy ~ collection_location + year

#sixth model
  # total energy ~ collection_location + GSI + sex

#seventh model
  # total energy ~ collection_location + GSI + year

#eighth model
  # total energy ~ collection_location + sex + year

#ninth model 
  # total energy ~ collection_location + year + sex + sex:year

#tenth model
  # total energy ~ collection_location + GSI+ sex + GSI:sex

#eleventh model 
  # total energy ~ collection_location + GSI + year + GSI:year

#GLOBAL model
  # total energy ~ collection_location + GSI + sex + year 

```
