---
title: "cr_sockeye"
author: "Abby Host"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

## Downloading Data
```{r}
if(!require(tidyverse))install.packages("tidyverse");library(tidyverse)
if(!require(gsheet))install.packages("gsheet");library(gsheet)

write.csv(read.csv(text=gsheet2text("https://docs.google.com/spreadsheets/d/1PuZgbr8eBlCNh1ygfhuv2W_xsryhhezn/edit#gid=1548316807",format="csv"),stringsAsFactors = F),
          row.names = FALSE,
          "odata/crbody_2019.csv") #downloads 2019 body comp data from google sheets, make sure shareable by link in google

write.csv(read.csv(text=gsheet2text("https://docs.google.com/spreadsheets/d/1zOiVbDwnPme8mJdAlvX1QJ30etYJGBwA/edit#gid=1261110748",format="csv"),stringsAsFactors = F),
          row.names = FALSE,
          "odata/crpathogens_2019.csv") 

write.csv(read.csv(text=gsheet2text("https://docs.google.com/spreadsheets/d/1PuZgbr8eBlCNh1ygfhuv2W_xsryhhezn/edit#gid=1571451659",format="csv"),stringsAsFactors = F),
          row.names = FALSE,
          "odata/bodypath_2019.csv") 

bodycomp <- read.csv("odata/crbody_2019.csv")
path <- read.csv("odata/crpathogens_2019.csv")
bodypath <- read.csv("odata/bodypath_2019.csv") #full dataset w/ body comp AND pathogen results for 2019
```

## donwloading packages & adjusted data files
```{r}
library(lme4)
library(Matrix)
library(MASS)
library(dplyr)

#making site a factor in bodypath dataframe
bodypath$site <- as.factor(bodypath$site)
str(bodypath)
```

## Energy Density Analysis for CC & Upper River
```{r}
write.csv(read.csv(text=gsheet2text("https://docs.google.com/spreadsheets/d/1PuZgbr8eBlCNh1ygfhuv2W_xsryhhezn/edit#gid=1774874016",format="csv"),stringsAsFactors = F),
          row.names = FALSE,
          "odata/lowerriverdata_2019.csv")

lowerriver <- read.csv("odata/lowerriverdata_2019.csv")
lowerriver$runtime <- factor(lowerriver$runtime,
                             levels = c("Early",
                                        "Mid",
                                        "Late"),
                             labels = c("Early",
                                        "Mid",
                                        "Late"))

write.csv(lowerriver, "wdata/workinglowerriverbodycomp_2019.csv")
str(lowerriver)
runtimeEmodel <- lm(EnergyDensity_mJ.kg_1~runtime, data = lowerriver)
anova(runtimeEmodel)

ggplot(lowerriver, aes(runtime, y=EnergyDensity_mJ.kg_1, fill = runtime)) + xlab("Run Timing Group") + ylab("Energy Density (mJ/kg)") + ggtitle("Energy Density (mJ/kg) across run-timing group in Canyon Creek") + geom_boxplot() +  scale_fill_manual(values = c("#1F78B4", "#E31A1C", "#FDBF6F")) +  theme(axis.title=element_text(size=14, face="bold"), axis.text.x = element_text(size=12), axis.text.y=element_text(size=12), title = element_text(size=16, face="bold"), legend.text = element_text(size=12)) + geom_jitter()



#Upper River Energy vs site analysis
upperriver <- bodycomp[61:172,]
upperriver <- upperriver[-(32:72),]
upperriver <- upperriver[-(21),]#All upper river data samples (subtracting Eyak, Power Creek, and KL)

upperriver$site <- factor(upperriver$site,
                             levels = c("TN",
                                        "MN",
                                        "GH",
                                        "SA",
                                        "MA",
                                        "LL"),
                             labels = c("TN",
                                        "MN",
                                        "GH",
                                        "SA",
                                        "MA",
                                        "LL"))

write.csv(upperriver, "wdata/upperriverbodycomp_2019.csv")
str(upperriver)
upperriverEmodel <- lm(EnergyDensity_mJ.kg_1~site, data = upperriver)
anova(upperriverEmodel)

ggplot(upperriver, aes(site, y=EnergyDensity_mJ.kg_1, fill = site)) + xlab("Sampling Site") + ylab("Energy Density (mJ/kg)") + ggtitle("Energy Density (mJ/kg) across 6 spawning sites in the Copper River, AK") + geom_boxplot() +  scale_fill_manual(values = c("#CAB2D6", "#FB9A99", "#33A02C","#FF7F00", "#E31A1C","#B2DF8A")) + theme(axis.title=element_text(size=14, face="bold"), axis.text.x = element_text(size=12), axis.text.y=element_text(size=12), title = element_text(size=16, face="bold"), legend.text = element_text(size=12)) + geom_jitter()

```
## Eliminating EW and PC rows
```{r}
bodypath
#subset bodypath to get rid of Eyak and Power Creek rows
bodypath1 <- bodypath[-(33:48),]
#bodypath1$pathprevalence <- (bodypath1$path_richness / 37)

```

## Response Variables
```{r}
# size-corrected body mass
# regression with body weight and body length (size corrected body mass AKA sc_bm)
bodypath1 <- bodypath1[-(57),] #eliminates TN1 b/c it lacks data
sc_bm_lm <- lm(bodypath1$Fish_Wt ~ bodypath1$Fish_Leng_1)
sc_bm_resid <- residuals(sc_bm_lm) 
sc_bm_resid
plot(sc_bm_resid, bodypath1$Fish_Leng_1)
length(bodypath1$Fish_Leng_1)

sc_bodymass <- as.data.frame(sc_bm_resid)
bodypath1 <- cbind(bodypath1, sc_bodymass) #adding residuals as a column for size corrected body mass
library(dplyr)
names(bodypath1)[names(bodypath1)== "sc_bm_resid"] <- "sc_bodymass" #rename column

bodypath1 <- bodypath1[-(45),] #eliminates LL6, which has a -999 value of ihnv, which i eliminated via NA in the path loadings

#may need to eliminate SA5 because no data for E content -- maybe not though?
write.csv(bodypath1, "wdata/bodypathogenanalysis_data2019.csv")

# energy density
bodypath1$EnergyDensity_mJ.kg_1

#total energy??
#how to calculate this? == E density * Fish Weight
bodypath1$totalE <- (bodypath1$EnergyDensity_mJ.kg_1*bodypath1$Fish_Wt)


```

## Pathogen Richness (Explanatory Variable)
```{r}
pathrichness <- bodypath1[,c(1:2,6,49:86)]
write.csv(pathrichness, "wdata/2019_pathogenrichness.csv") # smaller data frame with pathogen richness, for presentation

# prevalence was calculated in excel spreadsheet for simplicity, not used for code

#bodypath1$path_richness 
## path richness column, all adjusted for columns that needed to be removed/rows that needed to be removed

```


## Pathogen Analysis, transformed data-- new datasheet
```{r}
write.csv(read.csv(text=gsheet2text("https://docs.google.com/spreadsheets/d/1zOiVbDwnPme8mJdAlvX1QJ30etYJGBwA/edit#gid=855164179",format="csv"),stringsAsFactors = F),
          row.names = FALSE,
          "odata/updatedpathogens_2019.csv") 

path <- read.csv("odata/updatedpathogens_2019.csv")
#path <- path[-c(9:16,57:64,73),] #eliminate PC and EW data, and TN1 which lacks body comp data in other datasheet
str(path)


path_loads <- subset(path, select = c(unique_id,site, fluidigm_num, 10:55))
str(path_loads)
path_work <- subset(path_loads, select = c(1:6, 8:9, 11:15, 17:18, 20:25, 27:30, 32:34, 36, 38, 40:49))
str(path_work)

#transforming data, testing w/ histograms
path_work <- path_work %>%
  mutate(c_b_cys = log(c_b_cys + 1))

path_work <- path_work %>%
  mutate(de_sal = log(de_sal + 1))

path_work <- path_work %>%
  mutate(fa_mar = log(fa_mar + 1))

path_work <- path_work %>%
  mutate(fl_psy = log(fl_psy + 1))

path_work <- path_work %>%
  mutate(ic_hof = log(ic_hof + 1))

path_work <- path_work %>%
  mutate(ic_mul = log(ic_mul + 1))

path_work <- path_work %>%
  mutate(ihnv = log(ihnv + 1))

path_work <- path_work %>%
  mutate(lo_sal = log(lo_sal + 1))

path_work <- path_work %>%
  mutate(pa_kab = log(pa_kab + 1))

path_work <- path_work %>%
  mutate(pa_min = log(pa_min + 1))

path_work <- path_work %>%
  mutate(pa_pse = log(pa_pse + 1))

path_work <- path_work %>%
  mutate(pa_ther = log(pa_ther + 1))

path_work <- path_work %>%
  mutate(sch = log(sch + 1))

path_work <- path_work %>%
  mutate(sp_des = log(sp_des + 1))

path_work <- path_work %>%
  mutate(te_bry = log(te_bry + 1))

str(path_work)


#remove pathogens with all 0 loads
path_work <- subset(path_work, select = c(1:3, 7, 11:17, 22:25, 31, 33:34))
path_work <- path_work[-c(9:16,57:64,73),] #eliminates EW and PC data rows, eliminates TN1 because it lacks bodycomp data for analysis in future

path_work <- path_work[,-(15:16)] #eliminates sch and path_ther, b/c no prevalence without EW and PC
pairs(path_work[,4:16])
write.csv(path_work, "wdata/workingpathogendata.csv") #saving this datafile, in case -- log transformations, only includes pathogens with loadings present for at least one fish in one CR location

#PCA
path_work <- drop_na(path_work) #dropping NA values from data (this drops LL6 ======= NEED TO ADDENDUM THIS IN BODYPATH1 for future analysis)
path_pca <- princomp(path_work[,4:16],cor=T, scores=T, covmat = NULL)
summary(path_pca, loadings=T, cutoff=0.000001) #use to interpret
library("knitr")
library(kableExtra)

#organize sites with colors
path_work$site <- factor(path_work$site,
                             levels = c("CC",
                                        "LL",
                                        "MA",
                                        "SA",
                                        "GH",
                                        "MN",
                                        "TN"),
                             labels = c("CC",
                                        "LL",
                                        "MA",
                                        "SA",
                                        "GH",
                                        "MN",
                                        "TN"))

#vegan() for analysis, plotting, and ordination of multivariate datasets.
install.packages("vegan")
library(vegan)
pca_vec <- envfit(path_pca$scores[,1:2], path_work[,4:16], permutations=0)
plot(path_pca$scores[,1:2], cex=1.5, asp=1, pch=c(16), col=c("#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), ylab="", xlab="", cex.main=1.5, main = "PC 2 vs PC 1, with vectors indicating the correlation between the component scores")
mtext("Principal Component 2", side=2, line=2.2, cex=1.5)
mtext("Principal Component 1", side=1, line=2.2, cex=1.5)
legend(7,4.5, legend = sort(unique(path_work[,2])), col = c("#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C",  "#FF7F00", "#CAB2D6"), pch=c(16), cex=1.2, title ="Site")
plot(pca_vec, col="black", new = F, cex=1) #The envfit() function fits vectors indicating the correlation between the component scores (plotted in the scatterplot)


## For Principal component analysis, interpretation is based on finding which variables are most strongly correlated with each component, i.e., which of these numbers are large in magnitude, the farthest from zero in either direction. 
## Looking at loadings, the following pathogens are the largest in magnitude and therefore the most strongly correlated with Principle Component #1: fl_psy > hkg > c_b_cys > ihnv > ic_mul
#for principle component #2: pa_min > pa_pse > te_bry > de_sal > sch

#why the PCA? --  simplifies the complexity in high-dimensional data while retaining trends and patterns

path_pca
path_pca$scores

screeplot(path_pca, type=c('lines'), main = "Line Screeplot for Pathogen PCA")

path_work$site <- as.factor(path_work$site)
site_scores<-cbind(path_work$site, path_pca$scores[,1:4])
site_scores <- as.data.frame(site_scores)
str(site_scores)
site_scores$V1 <- as.factor(site_scores$V1)
site_scores$Comp.1 <- as.numeric(site_scores$Comp.1)
site_scores$Comp.2 <- as.numeric(site_scores$Comp.2)
site_scores$Comp.3 <- as.numeric(site_scores$Comp.3)
site_scores$Comp.4 <- as.numeric(site_scores$Comp.4)

library(RColorBrewer)
display.brewer.all()
display.brewer.pal(n=9, name = "Paired")
brewer.pal(n = 9, name = "Paired")
# "#A6CEE3"  "#B2DF8A" "#33A02C" "#FB9A99" "#E31A1C" "#FDBF6F" "#FF7F00" "#CAB2D6"



#PC2 vs PC1 figure
plot(site_scores[,2], site_scores[,3], col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, xlab= "PC-1", ylab = "PC-2", main="PC-2 vs PC-1")
legend("bottomleft", legend = unique(site_scores[,1]), col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, cex=0.5)


#PC3 vs PC1 figure
plot(site_scores[,2], site_scores[,4], col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, xlab= "PC-1", ylab = "PC-3", main="PC-3 vs PC-1")
legend("bottomleft", legend = unique(site_scores[,1]),col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, cex=0.5)

#PC3 vs PC2 figure
plot(site_scores[,3], site_scores[,4], col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, xlab= "PC-2", ylab = "PC-3", main="PC-3 vs PC-2")
legend("bottomleft", legend = unique(site_scores[,1]),col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, cex=0.5)

#PC4 vs PC1 figure
plot(site_scores[,2], site_scores[,5], col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, xlab= "PC-1", ylab = "PC-4", main="PC-4 vs PC-1")
legend("bottomleft", legend = unique(site_scores[,1]), col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, cex=0.5)

#PC4 vs PC2 figure
plot(site_scores[,3], site_scores[,5], col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, xlab= "PC-2", ylab = "PC-4", main="PC-4 vs PC-2 for Pathogen Data, grouped by site in river")
legend("bottomleft", legend = unique(site_scores[,1]), col=c("#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"), pch=19, cex=1)

#look at principal components as explanatory variable
```
## PCA Loadings (PC1) ---> bodypath1 dataframe
```{r}
path_pca$scores[,1]
path_pc1scores <- as.data.frame(path_pca$scores[,1])

bodypath1 <- cbind(bodypath1, path_pc1scores) #adding PC1 scores as a column of bodypath1
library(dplyr)
names(bodypath1)[names(bodypath1)== "path_pca$scores[, 1]"] <- "PC1_scores"

write.csv(bodypath1, "wdata/bodypathogenanalysis_data2019.csv")

```

## HYPOTHESIS #1 Linear Analysis 
```{r}
# Hypothesis #1 ===  Body size, fecundity, and energy density of sockeye are negatively correlated to pathogen prevalence.

# response variables = size corrected body mass, energy density, total energy
# explanatory variables = pathogen richness, pathogen PC scores

# lm(Y ~ X)

#pathogen richness as explanatory
pathr_scbm_lm <- lm(bodypath1$sc_bodymass ~ bodypath1$path_richness)
summary(pathr_scbm_lm)
anova(pathr_scbm_lm)
ggplot(bodypath1, aes(bodypath1$path_richness, bodypath1$sc_bodymass)) + geom_point() + geom_smooth(method = "lm", col = "blue", ) + xlab("Pathogen Richness") + ylab("Size Corrected Body Mass")

pathr_ED_lm <- lm(bodypath1$EnergyDensity_mJ.kg_1 ~ bodypath1$path_richness)
summary(pathr_ED_lm)
anova(pathr_ED_lm)
ggplot(bodypath1, aes(bodypath1$path_richness, bodypath1$EnergyDensity_mJ.kg_1)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen Richness") + ylab("Energy Density (mJ/kg")

pathr_TE_lm <- lm(bodypath1$totalE ~ bodypath1$path_richness)
anova(pathr_TE_lm)
summary(pathr_TE_lm)
ggplot(bodypath1, aes(bodypath1$path_richness, bodypath1$totalE)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen Richness") + ylab("Total Energy (mJ)")


#pathogen PC Scores as explanatory
pathscore_scbm_lm <- lm(bodypath1$sc_bodymass ~ bodypath1$PC1_scores)
anova(pathscore_scbm_lm)
summary(pathscore_scbm_lm)
ggplot(bodypath1, aes(bodypath1$PC1_scores, bodypath1$sc_bodymass)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen PC1 Score") + ylab("Size Corrected Body Mass")


pathscore_ED_lm <- lm(bodypath1$EnergyDensity_mJ.kg_1 ~ bodypath1$PC1_scores)
anova(pathscore_ED_lm)
summary(pathscore_ED_lm)
ggplot(bodypath1, aes(bodypath1$PC1_scores, bodypath1$EnergyDensity_mJ.kg_1)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen PC1 Score") + ylab("Energy Density")


pathscore_TE_lm <- lm(bodypath1$totalE ~ bodypath1$PC1_scores)
anova(pathscore_TE_lm)
summary(pathscore_TE_lm)
ggplot(bodypath1, aes(bodypath1$PC1_scores, bodypath1$totalE)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen PC1 Score") + ylab("Total Energy")



#Richness Plots for Data Presentation
install.packages("gridExtra")
library(gridExtra)
richness_scbm_plot <- ggplot(bodypath1, aes(path_richness, sc_bodymass)) + geom_point() + geom_smooth(method = "lm", col = "blue", ) + xlab("Pathogen Richness") + ylab("Residuals for Size Corrected Body Mass") + theme(axis.text=element_text(size=12), axis.title=element_text(size=14, face="bold"))

richness_ED_plot <- ggplot(bodypath1, aes(path_richness, EnergyDensity_mJ.kg_1)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen Richness") + ylab("Energy Density (mJ/kg)") + theme(axis.text=element_text(size=12), axis.title=element_text(size=14, face="bold"))

richness_TE_plot <- ggplot(bodypath1, aes(path_richness, totalE)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen Richness") + ylab("Total Energy (mJ)") + theme(axis.text=element_text(size=12), axis.title=element_text(size=14, face="bold"))

grid.arrange(richness_scbm_plot, richness_ED_plot, richness_TE_plot, ncol = 3)


#Load Plots for Data Presentation
loads_scbm_plot <- ggplot(bodypath1, aes(PC1_scores, sc_bodymass)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen PC1 Score") + ylab("Residuals for Size Corrected Body Mass") + theme(axis.text=element_text(size=11), axis.title=element_text(size=14, face="bold"))

loads_ED_plot <- ggplot(bodypath1, aes(PC1_scores, EnergyDensity_mJ.kg_1)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen PC1 Score") + ylab("Energy Density") + theme(axis.text=element_text(size=11), axis.title=element_text(size=14, face="bold"))

loads_TE_plot <- ggplot(bodypath1, aes(PC1_scores, totalE)) + geom_point() + geom_smooth(method = "lm", col = "blue") + xlab("Pathogen PC1 Score") + ylab("Total Energy") + theme(axis.text=element_text(size=11), axis.title=element_text(size=14, face="bold"))

grid.arrange(loads_scbm_plot, loads_ED_plot, loads_TE_plot, ncol = 3)
```


## Hypothesis #2 Linear Analysis
```{r}
# Hypothesis #2 ===  Sockeye in early run-timing groups will have lower pathogen richness & loads than sockeye in later run-timing groups.

# response variables = pathogen richness, pathogen PC scores
# explanatory variables = site (b/c only "early run timing" fish taken for pathogens in CC)

# lm(Y ~ X)

bodypath1$site <- factor(bodypath1$site,
                             levels = c("CC",
                                        "TN",
                                        "MN",
                                        "GH",
                                        "SA",
                                        "MA",
                                        "LL"),
                             labels = c("CC",
                                        "TN",
                                        "MN",
                                        "GH",
                                        "SA",
                                        "MA",
                                        "LL"))

#Response Variable =  pathogen richness
pathr_site_lm <- lm(bodypath1$path_richness ~ bodypath1$site)
anova(pathr_site_lm)
pathr_site_lm
ggplot(bodypath1, aes(site, path_richness, fill = site)) + geom_boxplot() + xlab("Site") + ylab("Pathogen Richness") + scale_fill_manual(values = c("#1F78B4","#CAB2D6", "#FB9A99", "#33A02C","#FF7F00", "#E31A1C","#B2DF8A")) + geom_jitter()+ theme(axis.text=element_text(size=11), axis.title=element_text(size=14, face="bold"), title = element_text(size=16, face="bold"), legend.text = element_text(size=12))


#response variable = pathogen load (PC score)
pathscore_site_lm <- lm(bodypath1$PC1_scores ~ bodypath1$site)
anova(pathscore_site_lm)
ggplot(bodypath1, aes(bodypath1$site, bodypath1$PC1_scores, fill = site)) + geom_boxplot() + xlab("Site") + ylab("Pathogen PC1 Score") + scale_fill_manual(values = c("#1F78B4","#CAB2D6", "#FB9A99", "#33A02C","#FF7F00", "#E31A1C","#B2DF8A")) + geom_jitter()+ theme(axis.text=element_text(size=11), axis.title=element_text(size=14, face="bold"), title = element_text(size=16, face="bold"), legend.text = element_text(size=12))


#Plots for Data Presentation
richness_site_plot <- ggplot(bodypath1, aes(site, path_richness, fill = site)) + geom_boxplot() + xlab("Site") + ylab("Pathogen Richness") + scale_fill_manual(values = c("#1F78B4","#CAB2D6", "#FB9A99", "#33A02C","#FF7F00", "#E31A1C","#B2DF8A")) + geom_jitter()+ theme(axis.text=element_text(size=11), axis.title=element_text(size=14, face="bold"), title = element_text(size=16, face="bold"), legend.text = element_text(size=12))

loads_site_plot <- ggplot(bodypath1, aes(bodypath1$site, bodypath1$PC1_scores, fill = site)) + geom_boxplot() + xlab("Site") + ylab("Pathogen PC1 Score") + scale_fill_manual(values = c("#1F78B4","#CAB2D6", "#FB9A99", "#33A02C","#FF7F00", "#E31A1C","#B2DF8A")) + geom_jitter()+ theme(axis.text=element_text(size=11), axis.title=element_text(size=14, face="bold"), title = element_text(size=16, face="bold"), legend.text = element_text(size=12))

grid.arrange(richness_site_plot, loads_site_plot, ncol = 2)
```




## Bar Plots for each Pathogen, for prevalence/load over various locations in river
```{r}
??barplot
library(ggplot2)
??ggplot2
library(PNWColors)
names(pnw_palettes)
pal <- pnw_palette("Lake",9, type = "continuous")


ggplot(bodypath, aes(x = site, y = c_b_cys, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() + ylab("Prevalence of Candidatus branchiomonas cysticola") + xlab("Site") #lots of loads per river
ggplot(bodypath, aes(x = site, y = c_b_cys, fill = site)) + geom_boxplot() + scale_fill_brewer() + theme_classic() + ylab("Prevalence of Candidatus branchiomonas cysticola") + xlab("Site") #boxplot version of visualization

bodypath_cc <- bodypath[1:8,]
ggplot(bodypath_cc, aes(x = site, y = c_b_cys, fill = site)) + geom_boxplot() + scale_fill_brewer() + theme_minimal() + ylab("Prevalence of Candidatus branchiomonas cysticola") + xlab("Site") #boxplot version of visualization of just CC


ggplot(bodypath, aes(x = site, y = de_sal, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #not a lot of prevelance

ggplot(bodypath, aes(x = site, y = fa_mar, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #only one point of prevalence in TNL

ggplot(bodypath, aes(x = site, y = fl_psy, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() # good prevalence

ggplot(bodypath, aes(x = site, y = hkg, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() # lots of LOW river prevalence values, but one very high prevalence in MN (this may be the outlier)-- What do I do about this?

ggplot(bodypath, aes(x = site, y = ic_hof, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() # one prevalence/load noted in CC, low river

ggplot(bodypath, aes(x = site, y = ic_mul, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #mediocre prevalence

ggplot(bodypath, aes(x = site, y = ihnv, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #some prevalence in GK and one fish with presence in St. Annes

ggplot(bodypath, aes(x = site, y = lo_sal, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #lots of presence, mixed between Upper and Lower River

ggplot(bodypath, aes(x = site, y = pa_kab, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #presence in CC, but none up river

ggplot(bodypath, aes(x = site, y = pa_min, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #multiple fish with presence in PC

ggplot(bodypath, aes(x = site, y = pa_ther, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #one fish with presence in EW

ggplot(bodypath, aes(x = site, y = sch, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #one fish in PC

ggplot(bodypath, aes(x = site, y = sp_des, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #lots of mid-upper river prevalence in mulitple fish

ggplot(bodypath, aes(x = site, y = te_bry, fill = site, col = "black")) + geom_bar(stat = "identity", col = "black") + scale_fill_brewer() + theme_minimal() #lots of presence in GJ and some in MA and LL

#can i do a figure where I look at one river site, all pathogens? so 9 figures instead of x amount of pathogens

```

## Bodypath Fecundity Analysis
```{r}
attach(bodypath)
library(ggplot2)
library(lme4)
bodypath

#Sex & E density --> random effects of site and collection date
weightEdensity_lmer <- lmer(EnergyDensity_mJ.kg_1 ~ Sex + (1|site) + (1|Collection_Date), bodypath)
anova(weightEdensity_lmer) #non-significant
ggplot(bodypath, aes(x = Sex, y = EnergyDensity_mJ.kg_1, fill = site)) + geom_boxplot() + xlab("Sex") + ylab("Energy Density (mJ/kg)") + ggtitle("Energy density (mJ/kg) vs sex for Copper River sockeye at 9 sample sites")+theme_classic() +  scale_fill_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FF7F00", "#CAB2D6"))


#calculating fecundity (# of eggs / weight)
bodypath$fencundity1 <- (bodypath$Fem_Fecun_1_num / bodypath$Fem_Fecun_1_wt)
bodypath$fencundity2 <- bodypath$Fem_Fecun_2_num / bodypath$Fem_Fecun_2_wt
bodypath$fencundity3 <- bodypath$Fem_Fecun_3_num / bodypath$Fem_Fecun_3_wt
bodypath$avgfecundity <- ((bodypath$fencundity1+bodypath$fencundity2+bodypath$fencundity3)/3)


#E Density & Avg fecundity Analysis
Edensityfecun_lmer <- lmer(avgfecundity ~ EnergyDensity_mJ.kg_1 + (1|site) + (1|Collection_Date), bodypath)
anova(Edensityfecun_lmer)
summary(Edensityfecun_lmer)

ggplot(bodypath, aes(x = EnergyDensity_mJ.kg_1, y = avgfecundity, fill = site)) + geom_boxplot() + xlab("Energy Density (mJ/kg)") + ylab("Average Fecundity (# eggs/weight)") + ggtitle("Average Fecundity vs Energy density (mJ/kg) for Copper River sockeye at 9 sample sites")+theme_classic() +  scale_fill_manual(values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00", "#CAB2D6"))

```