---
title: "AH_AICc_scbodymass~SP"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for Size Corrected Body Mass~SpawningPopulation models
#' =====================================================

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading
# bc19 <- read.csv("bodycomp_2019.csv")
# bc20 <- read.csv("bodycomp_2020.csv")
# bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, Upper River river only

# bc_UR_total <- rbind(bc19[61:172,], bc20[61:120,], bc21[61:182,])
# write.csv(bc_UR_total, "upperriver_bodycomp_all.csv")
upperriver_bodycomp_all<-read.csv("upperriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
str(upperriver_bodycomp_all)
upperriver_bodycomp_all$Collection_Date <- as.Date(upperriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
upperriver_bodycomp_all$Year <- year(upperriver_bodycomp_all$Collection_Date)
str(upperriver_bodycomp_all)

#replace blank cell in Sex with NA 
upperriver_bodycomp_all$Sex[upperriver_bodycomp_all$Sex == ""] <- NA
str(upperriver_bodycomp_all)

write.csv(upperriver_bodycomp_all, "upperriver_bodycomp_all.csv")
```

### Import Data for models, check for NAs and eliminate as needed
```{r}
rm(list = ls())
upperriver_bodycomp_PCscores <- "upperriver_bodycomp_PCscores.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(upperriver_bodycomp_PCscores)[,-1]

### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location)) #FALSE
any(is.na(DataSet$Year)) #FALSE
any(is.na(DataSet$Sex)) #FALSE
any(is.na(DataSet$Collection_RiverMile_m)) # FALSE
any(is.na(DataSet$Elevation_m)) #FALSE


#### CHECK DIRECTION OF PC SCORE ###
library(ggplot2)
ggplot(DataSet, aes(x=Fish_Wt, y=bodysize_pc_g_mm)) +
  geom_point()
#so direction of PC score is positive, can check with other variables


# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#Make work metric (migratory difficulty metric where work = F x distance)
DataSet$Elevation_m <- as.numeric(DataSet$Elevation_m)
DataSet$Work <- round((DataSet$Collection_RiverMile_m * DataSet$Elevation_m) / (1000 * 1000), digits = 1) #in km^2
str(DataSet) 

#convert gonad_wt to grams from kilograms
DataSet$Gonad_Wt_g <- DataSet$Gonad_Wt * 1000

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
levels(DataSet$Collection_Location) # 7 unique locations
DataSet$Year<- as.factor(DataSet$Year)
levels(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)


#check gonad weight for NAs
any(is.na(DataSet$Gonad_Wt_g))
DataSet[is.na(DataSet$Gonad_Wt_g), ] #need to eliminate these rows or model selection will not work
DataSet <- DataSet[-c(8, 19, 20, 31, 35, 37, 50, 59, 70, 71, 73, 81, 84, 111, 112, 114),]
any(is.na(DataSet$Gonad_Wt_g)) #FALSE

```

### Calculating Size-Corrected Body Mass in DataSet 
```{r}
### Size corrected body mass should be the residuals of linear regression between weight ~ fish body size PC Score ###
# DataSet$bodysize_pc_g_mm = in the correct units already
DataSet$Fish_Wt_g <- DataSet$Fish_Wt*1000 #grams conversion
sizecorrected_bodymass_lm <- lm(DataSet$Fish_Wt_g ~ DataSet$bodysize_pc_g_mm) #linear regression for size corrected body mass
sizecorrected_bodymass_residuals <- residuals(sizecorrected_bodymass_lm) #residuals for regression
plot(sizecorrected_bodymass_residuals, DataSet$bodysize_pc_g_mm)
sizecorrected_bodymass <- as.data.frame(sizecorrected_bodymass_residuals)
DataSet <- cbind(DataSet, sizecorrected_bodymass) #adds the residuals to data set as a variable
str(DataSet)

write.csv(DataSet, "upperriver_bodycomp_SizeCorrectedBodyMass.csv") #should all be according to grams and mm values
```

### Reload data for model sets now that size corrected body mass has been calculated
```{r}
rm(list = ls())
upperriver_bodycomp_all<- "upperriver_bodycomp_SizeCorrectedBodyMass.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(upperriver_bodycomp_all)[,-1] # 221 observations, 91 variables

### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_RiverMile_m))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))
any(is.na(DataSet$Gonad_Wt_g))

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
levels(DataSet$Collection_Location) # 7 unique locations
DataSet$Year<- as.factor(DataSet$Year)
levels(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
DataSet$Gonad_Wt_g <- as.numeric(DataSet$Gonad_Wt_g)
str(DataSet)


ggplot(DataSet, aes(x = Fish_Wt_g, y = sizecorrected_bodymass_residuals)) + 
  geom_point() # no outliers

```

### Making Models for sizecorrectedbodymass~SP
```{r}
# Models for reference
scBodyMass_SP_modelset <- "scbodymass_spawningpopulation/SizeCorrectedBodyMass~SpawningPopulation_modelset.csv"

ModelSet<-read.csv(scBodyMass_SP_modelset)

#DataSet$Work <- factor(DataSet$Work) #This is an important fix, otherwise its numeric but in fact its discrete factors

#models
model1 <- lm(sizecorrected_bodymass_residuals~1, data=DataSet)
model2 <- lm(sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location, data = DataSet)
model3 <- lm(sizecorrected_bodymass_residuals~ Gonad_Wt_g + Sex, data = DataSet)
model4 <- lm(sizecorrected_bodymass_residuals~ Gonad_Wt_g + Year, data = DataSet)
model5 <- lm(sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location + Sex, data = DataSet)
model6 <- lm(sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location + Year, data = DataSet)
model7 <- lm(sizecorrected_bodymass_residuals~ Gonad_Wt_g + Sex + Year, data = DataSet)
model8 <- lm(sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location + Sex + Collection_Location:Sex, data = DataSet)
model9 <- lm(sizecorrected_bodymass_residuals~Gonad_Wt_g + Sex + Year + Sex:Year, data = DataSet)
model10 <- lm(sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location + Sex + Year, data = DataSet)

```

### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

#table of AIC results
mynames1 <- paste("model", as.character(1:10), sep = "")
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)

# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location + Year",
                      "sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location + Sex + Year",
                      "sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location",
                      "sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location + Sex",
                      "sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location + Sex + Collection_Location:Sex",
                      "sizecorrected_bodymass_residuals~ Gonad_Wt_g + Year",
                      "sizecorrected_bodymass_residuals~ Gonad_Wt_g + Collection_Location + Year + Collection_Location:Year",
                      "sizecorrected_bodymass_residuals~1",
                      "sizecorrected_bodymass_residuals~ Gonad_Wt_g + Sex",
                      "sizecorrected_bodymass_residuals~Gonad_Wt_g + Sex + Year + Sex:Year") 
colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "scbodymass_spawningpopulation/AICresults_SizeCorrectedBodyMass~SpawningPopulation.csv", row.names = FALSE)

```

### Model Averaging and Parameter Likelihoods
```{r}
# ---- Load necessary packages ----
library(MuMIn)

# List your models (already fit with na.action=na.fail)
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

# Model averaging based on AICc, conditional averaging (default is full=TRUE)
model_avg <- model.avg(models, rank = "AICc", full = TRUE)

# Summary with coefficients, SE, CIs
summary(model_avg)

# Full averaged coefficients
avg_coefs_full <- coef(model_avg, full = TRUE)

# Full averaged confidence intervals
avg_confint_full <- confint(model_avg, full = TRUE)

# Full averaged variance-covariance matrix and SE
avg_vcov_full <- vcov(model_avg, full = TRUE)
avg_se_full <- sqrt(diag(avg_vcov_full))

# Create tidy data frame with full averages
coefs_df_full <- as.data.frame(avg_coefs_full)
colnames(coefs_df_full) <- "Avg_Coef"
coefs_df_full$CI_Lower <- avg_confint_full[, 1]
coefs_df_full$CI_Upper <- avg_confint_full[, 2]
coefs_df_full$SE <- avg_se_full

# Calculate parameter importance (parameter likelihoods)
param_likelihoods <- sw(model_avg)
as.data.frame(param_likelihoods)

# Manually specify parameter likelihoods from sw(model_avg)
manual_likelihoods <- c(
  "(Intercept)" = 1.0,
  "Gonad_Wt_g" = 1.000000,
  "Collection_LocationGulkana Hatchery" = 1.0000, 
  "Collection_LocationLong Lake" = 1.0000,
  "Collection_LocationMahlo" = 1.0000,
  "Collection_LocationMentasta" = 1.0000,
  "Collection_LocationSt Anne" = 1.0000,
  "Collection_LocationTanada" = 1.0000,
  "Year2020" = 0.8735617,
  "Year2021" = 0.8735617, 
  "SexM" = 0.3836566,
  "SexM:Year2020" = 9.679284e-10,
  "SexM:Year2021" = 9.679284e-10,
  "Collection_LocationGulkana Hatchery:SexM" = 4.068750e-03,
  "Collection_LocationLong Lake:SexM" = 4.068750e-03,
  "Collection_LocationMahlo:SexM" = 4.068750e-03,
  "Collection_LocationMentasta:SexM" = 4.068750e-03,
  "Collection_LocationSt Anne:SexM" = 4.068750e-03,
  "Collection_LocationTanada:SexM" = 4.068750e-03
)


# Add ParamLikelihoods by matching rownames
coefs_df_full$ParamLikelihood <- manual_likelihoods[rownames(coefs_df_full)]

# View final table
print(coefs_df_full)

write.csv(coefs_df_full, "scbodymass_spawningpopulation/scBodyMass_SpawningPopulation_ModelAvg_Coefs_withLikelihoods.csv", row.names = TRUE)


```