---
title: "AH_AICc_totalenergy~RTG"
author: "Abby Host"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for Total Energy~RunTimingGroup models
#' =====================================================

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)

#data loading
bc19 <- read.csv("bodycomp_2019.csv")
bc20 <- read.csv("bodycomp_2020.csv")
bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, lower river only

bc_LR_total <- rbind(bc19[1:60,], bc20[1:60,], bc21[1:60,])
write.csv(bc_LR_total, "lowerriver_bodycomp_all.csv")
lowerriver_bodycomp_all<-read.csv("lowerriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
lowerriver_bodycomp_all$Collection_Date <- as.Date(lowerriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
lowerriver_bodycomp_all$Year <- year(lowerriver_bodycomp_all$Collection_Date)

#replace blank cell in Sex with NA 
lowerriver_bodycomp_all$Sex[lowerriver_bodycomp_all$Sex == ""] <- NA
str(lowerriver_bodycomp_all)

write.csv(lowerriver_bodycomp_all, "lowerriver_bodycomp_all.csv")

```
### Add Total Energy as a Variable
```{r}
# Total energy = PDry_1 * Fish_Wt == mJ energy
lowerriver_bodycomp_all$TotalEnergy <- lowerriver_bodycomp_all$EnergyPDry_1 * lowerriver_bodycomp_all$Fish_Wt
str(lowerriver_bodycomp_all)

write.csv(lowerriver_bodycomp_all, "lowerriver_bodycomp_TotalEnergy.csv")
```

### Import Data for models, check for NAs and eliminate as needed
```{r}
rm(list = ls())
lowerriver_bodycomp_all<- "lowerriver_bodycomp_TotalEnergy.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_all)[,-1]

### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$RunTimingGroup))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))
DataSet[is.na(DataSet$Sex), ] #row 115 has no sex value, eliminate it for models
DataSet <- DataSet[-115,] #excludes row missing sex file
any(is.na(DataSet$Sex))

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location) 
DataSet$RunTimingGroup <- as.factor(DataSet$RunTimingGroup)
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)
```

### Making Models for energydensity~RunTimingGroup
```{r}
# Models for reference
TotalEnergy_RTG_modelset <- "totalenergy_runtiminggroup/TotalEnergy~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(TotalEnergy_RTG_modelset)

#models
teModel1 <- lm(TotalEnergy ~ 1, data = DataSet)
teModel2 <- lm(TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup, data = DataSet)
teModel3 <- lm(TotalEnergy ~ Collection_RiverMile_m + Sex, data = DataSet)
teModel4 <- lm(TotalEnergy ~ Collection_RiverMile_m + Year, data = DataSet)
teModel5 <- lm(TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup + Sex, data = DataSet)
teModel6 <- lm(TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup + Year, data = DataSet)
teModel7 <- lm(TotalEnergy ~ Collection_RiverMile_m + Sex + Year, data = DataSet)
teModel8 <- lm(TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex, data = DataSet)
teModel9 <- lm(TotalEnergy ~ Collection_RiverMile_m + Sex + Year + Sex:Year, data = DataSet)
teModel10 <- lm(TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup + Sex + Year, data = DataSet)
```

### AICc Model Selection
```{r}
AIC(teModel1, teModel2, teModel3, teModel4, teModel5, teModel6, teModel7, teModel8, teModel9, teModel10)

teModels <- list(teModel1, teModel2, teModel3, teModel4, teModel5, teModel6, teModel7, teModel8, teModel9, teModel10)

# Generate AIC table
mynames_te <- paste("model", as.character(1:10), sep = "")
te_aicc <- aictab(teModels, modnames = mynames_te)
print(te_aicc) #so model 5 is preferred (lowest AIC score) followed by model 8 and then model 10

# Convert AIC table to a data frame for easier manipulation
TEaic_df <- as.data.frame(te_aicc)
TEaic_df$ModelName <- c("TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup + Sex",
                      "TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex",
                      "TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup + Sex + Year",
                      "TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup",
                      "TotalEnergy ~ Collection_RiverMile_m + Sex",
                      "TotalEnergy ~ Collection_RiverMile_m + Sex + Year",
                      "TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup + Year",
                      "TotalEnergy ~ Collection_RiverMile_m + Sex + Year + Sex:Year",
                      "TotalEnergy ~ Collection_RiverMile_m + Year",
                      "TotalEnergy ~ 1")
colnames(TEaic_df)[colnames(TEaic_df) == "Modnames"] <- "Model #"

write.csv(TEaic_df, file = "totalenergy_runtiminggroup/AICresults_TotalEnergy~RunTimingGroup.csv", row.names = FALSE)

```

### Model Averaging
```{r}
library(MuMIn)

 # Create a model selection table (this will give you AIC, AIC weights, etc.)
model_weights <- te_aicc$AICcWt ##Get the AIC weights from the AIC table
model_avg <- model.avg(teModels, weights = model_weights)
summary(model_avg)
avg_coefs <- coef(model_avg)
avg_confint <- confint(model_avg)
avg_se <- sqrt(diag(vcov(model_avg)))

# Convert the coefficients into a tidy data frame
coefs_df <- as.data.frame(avg_coefs)
colnames(coefs_df) <- "Avg_Coef"
coefs_df$CI_Lower <- avg_confint[, 1]  # Add lower bound of confidence intervals
coefs_df$CI_Upper <- avg_confint[, 2] # Add upper bound of confidence intervals
coefs_df$SE <- avg_se
print(coefs_df) #Model Averaging Coefficients for AIC model selection approach with body size as response variable

write.csv(coefs_df, file = "totalenergy_runtiminggroup/TotalEnergy~runtiminggroup_models_CoefEstimates.csv", row.names = TRUE)
```

### Figure that displays parameter estimates + CI for each parameter in the model set
```{r}
paramestimates_te <- "totalenergy_runtiminggroup/TotalEnergy~runtiminggroup_models_CoefEstimates.csv"

estimates_te<-read.csv(paramestimates_te)
str(estimates_te)

levels(factor(estimates_te$X))
estimates_te$X <- factor(estimates_te$X, 
                           levels = rev(c("(Intercept)", 
                                      "Collection_RiverMile_m",
                                      "RunTimingGroupMiddle", 
                                      "RunTimingGroupLate", 
                                      "SexM",
                                      "Year2020",
                                      "Year2021",
                                      "RunTimingGroupMiddle:SexM",
                                      "RunTimingGroupLate:SexM",
                                      "SexM:Year2020",
                                       "SexM:Year2021")))


library(ggplot2)
ggplot(estimates_te, aes(x = Avg_Coef, y = X)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

library(dplyr)
estimates_te_filtered <- estimates_te %>%
  filter(X != "Collection_RiverMile_m") #filter out collection river mile, as it is not necessary for the estimates

te_plot <- ggplot(estimates_te_filtered, aes(x = Avg_Coef, y = X)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

ggsave("totalenergy_runtiminggroup/TotalEnergy_ParamEstimates_Plot.png", plot=te_plot, height=8, width=12, units="in")
```


### Visualizing top selected model(s) from AIC 
```{r}
DataSet$RunTimingGroup <- factor(DataSet$RunTimingGroup,
                               levels = c("Early",
                                          "Middle",
                                          "Late"),
                               labels = c("Early",
                                          "Middle",
                                          "Late"))
### Model 5 ###
    #TotalEnergy ~ Collection_RiverMile_m + RunTimingGroup + Sex
ggplot(DataSet, aes(x = interaction(RunTimingGroup, Sex), y = TotalEnergy, fill = interaction(RunTimingGroup, Sex))) +
  stat_summary(fun = "mean", geom = "bar", position = "dodge") +
  labs(title = "Mean Total Energy by Run Timing Group and Sex",
       x = "Run Timing Group & Sex", y = "Mean Total Energy") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(DataSet, aes(x = interaction(RunTimingGroup, Sex), y = TotalEnergy, fill = interaction(RunTimingGroup, Sex))) +
  geom_violin() +
  labs(title = "Violin Plot of Total Energy by Run Timing Group and Sex",
       x = "Run Timing Group & Sex", y = "Total Energy") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(DataSet, aes(x = RunTimingGroup, y = TotalEnergy, color = Sex)) +
  geom_point() +
  geom_smooth(method = "lm", aes(group = Sex), se = FALSE) +
  labs(title = "Interaction between Run Timing Group and Sex on Total Energy",
       x = "Run Timing Group", y = "Total Energy")

ggplot(DataSet, aes(x = RunTimingGroup, y = TotalEnergy, fill = RunTimingGroup)) +
  geom_boxplot() +
  facet_wrap(~ Sex) +
  labs(title = "Total Energy by Run Timing Group and Sex",
       x = "Run Timing Group", y = "Total Energy")


```