---
title: "AH_AICc_scBodyMass~RTG"
author: "Abby Host"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for size corrected body mass~RunTimingGroup models
#' =====================================================

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)

#data loading
bc19 <- read.csv("bodycomp_2019.csv")
bc20 <- read.csv("bodycomp_2020.csv")
bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, lower river only

bc_LR_total <- rbind(bc19[1:60,], bc20[1:60,], bc21[1:60,])
write.csv(bc_LR_total, "lowerriver_bodycomp_all.csv")
lowerriver_bodycomp_all<-read.csv("lowerriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
lowerriver_bodycomp_all$Collection_Date <- as.Date(lowerriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
lowerriver_bodycomp_all$Year <- year(lowerriver_bodycomp_all$Collection_Date)

#replace blank cell in Sex with NA 
lowerriver_bodycomp_all$Sex[lowerriver_bodycomp_all$Sex == ""] <- NA
str(lowerriver_bodycomp_all)

write.csv(lowerriver_bodycomp_all, "lowerriver_bodycomp_all.csv")

```

### Import Data for models, check for NAs and eliminate as needed
```{r}
rm(list = ls())
lowerriver_bodycomp_PCscores<- "lowerriver_bodycomp_PCscores.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_PCscores)[,-1]

### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$RunTimingGroup))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))
DataSet[is.na(DataSet$Sex), ] #ALL FALSE


# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location) 
DataSet$RunTimingGroup <- as.factor(DataSet$RunTimingGroup)
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)

```


### Calculating Size-Corrected Body Mass in DataSet 
```{r}
### Size corrected body mass should be the residuals of linear regression between weight ~ fish body size PC Score ###
# DataSet$bodysize_pc_g_mm = in the correct units already
DataSet$Fish_Wt_g <- DataSet$Fish_Wt*1000 #grams conversion
sizecorrected_bodymass_lm <- lm(DataSet$Fish_Wt_g ~ DataSet$bodysize_pc_g_mm) #linear regression for size corrected body mass
sizecorrected_bodymass_residuals <- residuals(sizecorrected_bodymass_lm) #residuals for regression
plot(sizecorrected_bodymass_residuals, DataSet$Fish_Leng_Total_mm)
sizecorrected_bodymass <- as.data.frame(sizecorrected_bodymass_residuals)
DataSet <- cbind(DataSet, sizecorrected_bodymass) #adds the residuals to data set as a variable

write.csv(DataSet, "lowerriver_bodycomp_SizeCorrectedBodyMass.csv") #should all be according to grams and mm values
```

### Reload data for model sets now that size corrected body mass has been calculated
```{r}
rm(list = ls())
lowerriver_bodycomp_all<- "lowerriver_bodycomp_SizeCorrectedBodyMass.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_all)[,-1]

### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$RunTimingGroup))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location) 
DataSet$RunTimingGroup <- as.factor(DataSet$RunTimingGroup)
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)

ggplot(DataSet, aes(x = Fish_Wt_g, y = sizecorrected_bodymass_residuals)) + 
  geom_point() #one major outlier

# Find the max and min residual values
max_resid <- max(DataSet$sizecorrected_bodymass_residuals, na.rm = TRUE)
min_resid <- min(DataSet$sizecorrected_bodymass_residuals, na.rm = TRUE)

# Identify the rows with these extreme values
DataSet[which(DataSet$sizecorrected_bodymass_residuals == max_resid), ]
DataSet[which(DataSet$sizecorrected_bodymass_residuals == min_resid), ] #row 127, eliminate and see how shape adjusts

ggplot(DataSet[-(127),], aes(x = Fish_Wt_g, y = sizecorrected_bodymass_residuals)) + 
  geom_point() #much more normal, so eliminate for now

DataSet <- DataSet[-(127),] #eliminates outlier residual
```

### Making Models for energydensity~RunTimingGroup
```{r}
# Models for reference
scBodyMass_RTG_modelset <- "scbodymass_runtiminggroup/SizeCorrectedBodyMass~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(scBodyMass_RTG_modelset)

#models
scbmModel1 <- lm(sizecorrected_bodymass_residuals ~ 1, data = DataSet)
scbmModel2 <- lm(sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup, data = DataSet)
scbmModel3 <- lm(sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + Sex, data = DataSet)
scbmModel4 <- lm(sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + Year, data = DataSet)
scbmModel5 <- lm(sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup + Sex, data = DataSet)
scbmModel6 <- lm(sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup + Year, data = DataSet)
scbmModel7 <- lm(sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + Sex + Year, data = DataSet)
scbmModel8 <- lm(sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex, data = DataSet)
scbmModel9 <- lm(sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + Sex + Year + Sex:Year, data = DataSet)
scbmModel10 <- lm(sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup + Sex + Year, data = DataSet)
```

### AICc Model Selection
```{r}
AIC(scbmModel1, scbmModel2, scbmModel3, scbmModel4, scbmModel5, scbmModel6, scbmModel7, scbmModel8, scbmModel9, scbmModel10)

scbmModels <- list(scbmModel1, scbmModel2, scbmModel3, scbmModel4, scbmModel5, scbmModel6, scbmModel7, scbmModel8, scbmModel9, scbmModel10)

# Generate AIC table
mynames_scbm <- paste("model", as.character(1:10), sep = "")
scbm_aicc <- aictab(scbmModels, modnames = mynames_scbm)
print(scbm_aicc) #so model 2 is preferred (lowest AIC score) followed by model 8 and then model 5

 # Convert AIC table to a data frame for easier manipulation
SCBMaic_df <- as.data.frame(scbm_aicc)
SCBMaic_df$ModelName <- c("sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup + Sex",
                          "sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex",
                          "sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup + Sex + Year",
                          "sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup",
                          "sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + RunTimingGroup + Year",
                          "sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + Sex",
                          "sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + Sex + Year",
                          "sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + Sex + Year + Sex:Year",
                          "sizecorrected_bodymass_residuals ~ 1",
                          "sizecorrected_bodymass_residuals ~ Collection_RiverMile_m + Year")
colnames(SCBMaic_df)[colnames(SCBMaic_df) == "Modnames"] <- "Model #"

write.csv(SCBMaic_df, file = "scbodymass_runtiminggroup/AICresults_SizeCorrectedBodyMass~RunTimingGroup.csv", row.names = FALSE)

```
### Model Averaging & Parameter Likelihoods 
```{r}
# Load necessary packages
library(MuMIn)

# List your models (already fit with na.action=na.fail)
models <- list(scbmModel1, scbmModel2, scbmModel3, scbmModel4, scbmModel5, scbmModel6, scbmModel7, scbmModel8, scbmModel9, scbmModel10)

# Model averaging based on AICc, conditional averaging (default is full=TRUE)
model_avg <- model.avg(models, rank = "AICc", full = TRUE)

# Summary with coefficients, SE, CIs
summary(model_avg)

# Full averaged coefficients
avg_coefs_full <- coef(model_avg, full = TRUE)

# Full averaged confidence intervals
avg_confint_full <- confint(model_avg, full = TRUE)

# Full averaged variance-covariance matrix and SE
avg_vcov_full <- vcov(model_avg, full = TRUE)
avg_se_full <- sqrt(diag(avg_vcov_full))

# Create tidy data frame with full averages
coefs_df_full <- as.data.frame(avg_coefs_full)
colnames(coefs_df_full) <- "Avg_Coef"
coefs_df_full$CI_Lower <- avg_confint_full[, 1]
coefs_df_full$CI_Upper <- avg_confint_full[, 2]
coefs_df_full$SE <- avg_se_full

# Calculate parameter importance (parameter likelihoods)
param_likelihoods <- sw(model_avg)
as.data.frame(param_likelihoods)

# Manually specify parameter likelihoods from sw(model_avg)
manual_likelihoods <- c(
  "(Intercept)" = 1.0,
  "Collection_RiverMile_m" = 0.9998668506,
  "RunTimingGroupLate" = 0.9970192243,
  "RunTimingGroupMiddle" = 0.9970192243,
  "SexM" = 0.9764046800,
  "Year2020" = 0.0779812188,
  "Year2021" = 0.0779812188,
  "RunTimingGroupLate:SexM" = 0.2698768913,
  "RunTimingGroupMiddle:SexM" = 0.2698768913,
  "SexM:Year2020" = 0.0003488707,
  "SexM:Year2021" = 0.0003488707 
)

# Add ParamLikelihoods by matching rownames
coefs_df_full$ParamLikelihood <- manual_likelihoods[rownames(coefs_df_full)]

# View final table
print(coefs_df_full)

write.csv(coefs_df_full, "scbodymass_runtiminggroup/SizeCorrectedBodyMass_ModelAvg_Coefs_withLikelihoods.csv", row.names = TRUE)

```



### Figure that displays parameter estimates + CI for each parameter in the model set
```{r}
paramestimates_scbm <- "scbodymass_runtiminggroup/SizeCorrectedBodyMass_ModelAvg_Coefs_withLikelihoods.csv"

estimates_scbm<-read.csv(paramestimates_scbm)
str(estimates_scbm)

levels(factor(estimates_scbm$Parameter))
estimates_scbm$Parameter <- factor(estimates_scbm$Parameter, 
                           levels = rev(c("(Intercept)", 
                                      "Collection_RiverMile_m",
                                      "RunTimingGroupMiddle", 
                                      "RunTimingGroupLate", 
                                      "SexM",
                                      "Year2020",
                                      "Year2021",
                                      "RunTimingGroupMiddle:SexM",
                                      "RunTimingGroupLate:SexM",
                                      "SexM:Year2020",
                                       "SexM:Year2021")))


library(ggplot2)
ggplot(estimates_scbm, aes(x = Avg_Coef, y = Parameter)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

library(dplyr)
estimates_scbm_filtered <- estimates_scbm %>%
  filter(Parameter != "Collection_RiverMile_m") #filter out collection river mile, as it is not necessary for the estimates

scbm_plot <- ggplot(estimates_scbm_filtered, aes(x = Avg_Coef, y = Parameter)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

ggsave("scbodymass_runtiminggroup/SizeCorrectedBodyMass_ParamEstimates_Plot.png", plot=scbm_plot, height=8, width=12, units="in")
```
