---
title: "AH_AICc_fineness~RTG"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for fineness~RunTimingGroup models
#' =====================================================

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)

#data loading
bc19 <- read.csv("bodycomp_2019.csv")
bc20 <- read.csv("bodycomp_2020.csv")
bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, lower river only

bc_LR_total <- rbind(bc19[1:60,], bc20[1:60,], bc21[1:60,])
write.csv(bc_LR_total, "lowerriver_bodycomp_all.csv")
lowerriver_bodycomp_all<-read.csv("lowerriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
lowerriver_bodycomp_all$Collection_Date <- as.Date(lowerriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
lowerriver_bodycomp_all$Year <- year(lowerriver_bodycomp_all$Collection_Date)

#replace blank cell in Sex with NA 
lowerriver_bodycomp_all$Sex[lowerriver_bodycomp_all$Sex == ""] <- NA
str(lowerriver_bodycomp_all)

write.csv(lowerriver_bodycomp_all, "lowerriver_bodycomp_all.csv")

```
### Checking for NAs for PC score
```{r}
rm(list = ls())
lowerriver_bodycomp_all <- "lowerriver_bodycomp_all.csv"
lowerriver_bodycomp_all<-read.csv("lowerriver_bodycomp_all.csv")[,-1]

### Removing NAs that will mess up levels / model weight
any(is.na(lowerriver_bodycomp_all$Collection_Location))
any(is.na(lowerriver_bodycomp_all$RunTimingGroup))
any(is.na(lowerriver_bodycomp_all$Year))
any(is.na(lowerriver_bodycomp_all$Sex))
lowerriver_bodycomp_all[is.na(lowerriver_bodycomp_all$Sex), ] #row 115 has no sex value, eliminate it for models
lowerriver_bodycomp_all <- lowerriver_bodycomp_all[-115,] #excludes row missing sex file
any(is.na(lowerriver_bodycomp_all$Sex))

#checking NA
any(is.na(lowerriver_bodycomp_all$Fish_Leng_2))
any(is.na(lowerriver_bodycomp_all$Fish_Ht))
any(is.na(lowerriver_bodycomp_all$Fish_Grth)) #Na's present, will need to omit them for PC score
lowerriver_bodycomp_all[is.na(lowerriver_bodycomp_all$Fish_Grth), ] #row 64 has NA
```

### Estimate Girth Values for NA rows
```{r}
ggplot(lowerriver_bodycomp_all, aes(x=Fish_Leng_1, y = Fish_Grth)) + 
  geom_point() #length relationship to girth

girth_leng_lm <- lm(Fish_Grth ~ Fish_Leng_1, data = lowerriver_bodycomp_all)
summary(girth_leng_lm) # Adjusted R-squared:  0.3044 

# Subset the data for female F fish only
allfemale_lowerriver_bodycomp <- lowerriver_bodycomp_all[lowerriver_bodycomp_all$Sex == "F", ]

# Perform PCA on the subset of female F fish
pca_model_allF <- princomp(allfemale_lowerriver_bodycomp[,c(12,14,16)], cor=T, scores=T, covmat = NULL)

summary(pca_model_allF, loadings=T, cutoff=0.001) #summary of PC analysis

# Create a new dataframe with PCA scores for the female F fish subset
allfemale_lowerriver_bodycomp <- cbind(allfemale_lowerriver_bodycomp, pca_model_allF$scores[, 1])  # First principal component

# Create the linear model for predicting Fish_Grth based on the first principal component
girth_pc_lm <- lm(Fish_Grth ~ pca_model_allF$scores[, 1], data = allfemale_lowerriver_bodycomp)

# View the summary of the linear model
summary(girth_pc_lm) #R squared value is 0.6942
plot(girth_pc_lm)


predicted_values <- predict(girth_pc_lm, newdata = allfemale_lowerriver_bodycomp)

allfemale_lowerriver_bodycomp$Predicted_Fish_Grth <- predicted_values # Add these predictions back to your dataset
View(allfemale_lowerriver_bodycomp)

### the predicted value for row 64 when all female fish is Fish_Grth = 30.00935

#plot the original data and the predicted values to see how well the model fits
ggplot(allfemale_lowerriver_bodycomp, aes(x = Predicted_Fish_Grth, y = Fish_Grth)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Grth, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Fish Growth",
       x = "Comparison PC",
       y = "Fish Growth") +
  theme_minimal() 

###### Now, back to using lowerriver_bodycomp_all #######
lowerriver_bodycomp_all$Fish_Grth[is.na(lowerriver_bodycomp_all$Fish_Grth)] <- 30.00935
any(is.na(lowerriver_bodycomp_all$Fish_Leng_2))
any(is.na(lowerriver_bodycomp_all$Fish_Ht))
any(is.na(lowerriver_bodycomp_all$Fish_Grth)) # no longer an NA present
```
### Estimating Fish_Wdth values for 2019, can I do this by sex?
```{r}
#Should I estimate via length, girth, height, or via PC score?
wdth_leng_lm <- lm(Fish_Wdth ~ Fish_Leng_1, data = lowerriver_bodycomp_all)
summary(wdth_leng_lm) # Adjusted R-squared: 0.4258

          ### OR ###

wdth_grth_lm <- lm(Fish_Wdth ~ Fish_Grth, data = lowerriver_bodycomp_all)
summary(wdth_grth_lm) # Adjusted R-squared:  0.2273 

          ### OR ###

wdth_ht_lm <- lm(Fish_Wdth ~ Fish_Ht, data = lowerriver_bodycomp_all)
summary(wdth_ht_lm) #Adjusted R-squared:  0.4984 

          ### OR ###

pca_model_wdth <- princomp(lowerriver_bodycomp_all[,c(12,14,16, 19)], cor=T, scores=T, covmat = NULL)
lowerriver_bodycomp_wdth <- cbind(lowerriver_bodycomp_all, pca_model_wdth$scores[, 1])  # First principal component

# Create the linear model for predicting Fish_Grth based on the first principal component
wdth_pc_lm <- lm(Fish_Wdth ~ pca_model_wdth$scores[, 1], data = lowerriver_bodycomp_wdth)
summary(wdth_pc_lm) #Adjusted R-squared:  0.418 , so length is better for the estimates



        ###USE Fish_Ht to estimate###
wdth_Ht_lm <- lm(Fish_Wdth ~ Fish_Ht, data = lowerriver_bodycomp_all)
summary(wdth_Ht_lm)
plot(wdth_Ht_lm)
predicted_wdth_values <- predict(wdth_Ht_lm, newdata = lowerriver_bodycomp_all)
lowerriver_bodycomp_all$Predicted_Fish_Wdth <- predicted_wdth_values

ggplot(lowerriver_bodycomp_all, aes(x = Predicted_Fish_Wdth, y = Fish_Wdth)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Wdth, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Fish Growth",
       x = "Comparison PC",
       y = "Fish Growth") +
  theme_minimal() 

# Replace NAs in Fish_Wdth with predicted values
lowerriver_bodycomp_all$Fish_Wdth[is.na(lowerriver_bodycomp_all$Fish_Wdth)] <- lowerriver_bodycomp_all$Predicted_Fish_Wdth[is.na(lowerriver_bodycomp_all$Fish_Wdth)]

# Now your missing values in Fish_Wdth have been replaced by predicted values

#check NAs
any(is.na(lowerriver_bodycomp_all$Fish_Leng_2))
any(is.na(lowerriver_bodycomp_all$Fish_Ht))
any(is.na(lowerriver_bodycomp_all$Fish_Wdth))
any(is.na(lowerriver_bodycomp_all$Fish_Grth))# no longer an NA present

```

### Adding Fineness Ratio for lowerriver_bodycomp_all
```{r}
### Fineness Ratio = A fish's "fineness ratio" refers to the ratio of its body length to its maximum cross-sectional diameter

#fineness ratio 1 : fish length / fish height ** this is the way reported by literature / pictures

#calculating fineness ratio 1
lowerriver_bodycomp_all$fineness_1 <- (lowerriver_bodycomp_all$Fish_Leng_1+lowerriver_bodycomp_all$Fish_Leng_2) / (lowerriver_bodycomp_all$Fish_Ht)

str(lowerriver_bodycomp_all$fineness_1) #fineness_1 is numeric
mean(lowerriver_bodycomp_all$fineness_1) #4.15, where fineness ratios between 2 and 6 result in a decrease of the drag produced by the fish, and species with a fineness ratio of 4.5 have an optimum swimming capacity 


#Fineness Ratio 2: fish length / fish width *** "body length to its maximum cross-sectional diameter" ***
lowerriver_bodycomp_all$fineness_2 <- (lowerriver_bodycomp_all$Fish_Leng_1+lowerriver_bodycomp_all$Fish_Leng_2) / (lowerriver_bodycomp_all$Fish_Wdth)

str(lowerriver_bodycomp_all$fineness_2) #fineness_1 is numeric
mean(lowerriver_bodycomp_all$fineness_2) #7.786 is the average here

#create new data file that includes fineness data in the dataset for models
write.csv(lowerriver_bodycomp_all, "lowerriver_bodycomp_fineness.csv") 


#technically, I think you can also do fish length / fish width (the cross sectional diameter)-- I could do this but a lot of points would need to be estimated for width.
```

### Import Data for models
```{r}
rm(list = ls())
lowerriver_bodycomp_fineness <- "lowerriver_bodycomp_fineness.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_fineness)[,-1]

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location) 
DataSet$RunTimingGroup <- as.factor(DataSet$RunTimingGroup)
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)

```

### Making Models for fineness_1~RunTimingGroup
```{r}
# Models for reference
fineness_RTG_modelset <- "fineness_runtiminggroup/fineness~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(fineness_RTG_modelset) #eliminate model 2 and model 10 from the list

model1 <- lm(fineness_1~1, data=DataSet)
# model2 <- lm(fineness_1~Collection_RiverMile_m, data = DataSet)
model2 <- lm(fineness_1~Collection_RiverMile_m + RunTimingGroup, data = DataSet)
model3 <- lm(fineness_1~Collection_RiverMile_m + Sex, data = DataSet)
model4 <- lm(fineness_1~Collection_RiverMile_m + Year, data = DataSet)
model5 <- lm(fineness_1~Collection_RiverMile_m + RunTimingGroup + Sex, data = DataSet)
model6 <- lm(fineness_1~Collection_RiverMile_m + RunTimingGroup + Year, data = DataSet)
model7 <- lm(fineness_1~Collection_RiverMile_m + Sex + Year, data = DataSet)
model8 <- lm(fineness_1~Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex, data = DataSet)
# model10 <- lm(fineness_1~Collection_RiverMile_m + RunTimingGroup + Year + RunTimingGroup:Year, data = DataSet)
model9 <- lm(fineness_1~Collection_RiverMile_m + Sex + Year + Sex:Year, data = DataSet)
model10 <- lm(fineness_1~Collection_RiverMile_m + RunTimingGroup + Sex + Year, data = DataSet)
```

### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

#table of AIC results
mynames1 <- paste("model", as.character(1:10), sep = "")
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1) #Model 8 has the lowest AIC score, fineness_1~Collection_Location + RunTimingGroup + Sex + RunTimingGroup:Sex
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("fineness_1~Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex",
                      "fineness_1~Collection_RiverMile_m + RunTimingGroup",
                      "fineness_1~Collection_RiverMile_m + RunTimingGroup + Sex",
                      "fineness_1~Collection_RiverMile_m + RunTimingGroup + year",
                      "fineness_1~Collection_RiverMile_m + RunTimingGroup + Sex + Year",
                      "fineness_1~Collection_RiverMile_m + Year",
                      "fineness_1~Collection_RiverMile_m + Sex",
                      "fineness_1~Collection_RiverMile_m + Sex + Year",
                      "fineness_1~Collection_RiverMile_m + Sex + Year + Sex:Year",
                      "fineness_1~1")
colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "fineness_runtiminggroup/AICresults_fineness1~RunTimingGroup.csv", row.names = FALSE)

```

### Visualizing this model selection
```{r}
# best model again, is model 9: fineness_1~Collection_Location + RunTimingGroup + Sex + RunTimingGroup:Sex


```

### Making Models for fineness_2~RunTimingGroup
```{r}
# Models for reference
fineness_RTG_modelset <- "fineness_runtiminggroup/fineness~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(fineness_RTG_modelset)

f2_model1 <- lm(fineness_2~1, data=DataSet)
# model2 <- lm(fineness_1~Collection_RiverMile_m, data = DataSet)
f2_model2 <- lm(fineness_2~Collection_RiverMile_m + RunTimingGroup, data = DataSet)
f2_model3 <- lm(fineness_2~Collection_RiverMile_m + Sex, data = DataSet)
f2_model4 <- lm(fineness_2~Collection_RiverMile_m + Year, data = DataSet)
f2_model5 <- lm(fineness_2~Collection_RiverMile_m + RunTimingGroup + Sex, data = DataSet)
f2_model6 <- lm(fineness_2~Collection_RiverMile_m + RunTimingGroup + Year, data = DataSet)
f2_model7 <- lm(fineness_2~Collection_RiverMile_m + Sex + Year, data = DataSet)
f2_model8 <- lm(fineness_2~Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex, data = DataSet)
# model10 <- lm(fineness_1~Collection_RiverMile_m + RunTimingGroup + Year + RunTimingGroup:Year, data = DataSet)
f2_model9 <- lm(fineness_2~Collection_RiverMile_m + Sex + Year + Sex:Year, data = DataSet)
f2_model10 <- lm(fineness_2~Collection_RiverMile_m + RunTimingGroup + Sex + Year, data = DataSet)
```

### AICc Model Selection
```{r}
AIC(f2_model1, f2_model2, f2_model3, f2_model4, f2_model5, f2_model6, f2_model7, f2_model8, f2_model9, f2_model10)

#table of AIC results
mynames2 <- paste("model", as.character(1:10), sep = "")
models2 <- list(f2_model1, f2_model2, f2_model3, f2_model4, f2_model5, f2_model6, f2_model7, f2_model8, f2_model9, f2_model10)

# Generate AIC table
myaicc2 <- aictab(models2, modnames = mynames2)
print(myaicc2) #Model 10 has the lowest AIC score, "fineness_2~Collection_Location + RunTimingGroup + Sex + Year"
# Convert AIC table to a data frame for easier manipulation
aic_df2 <- as.data.frame(myaicc2)
aic_df2$ModelName <- c("fineness_2~Collection_RiverMile_m + RunTimingGroup + Sex + Year",
                      "fineness_2~Collection_RiverMile_m + RunTimingGroup + Year",
                      "fineness_2~Collection_RiverMile_m + Sex + Year",
                      "fineness_2~Collection_RiverMile_m + Sex + Year + Sex:Year",
                      "fineness_2~Collection_RiverMile_m + Year",
                      "fineness_2~Collection_RiverMile_m + RunTimingGroup + Sex",
                      "fineness_2~Collection_RiverMile_m + RunTimingGroup",
                      "fineness_2~Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex",
                      "fineness_2~Collection_RiverMile_m + Sex",
                      "fineness_2~1")
colnames(aic_df2)[colnames(aic_df2) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df2, file = "fineness_runtiminggroup/AICresults_fineness2~RunTimingGroup.csv", row.names = FALSE)

```

### Visualizing fineness_2 relationships for AMSS
```{r}
#best model from above is the global model, model 10 = fineness_2~Collection_RiverMile_m + RunTimingGroup + Sex + Year


### Since this is body size, Collection_rivermile_m should not need to be accounted for as fish don't change size drastically in river



```