---
title: "AH_AICc_scbodymass~GSI"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for Size Corrected Body Mass~GSI models
#' =====================================================


NOTE!!!! Need to ensure what level of assignment likelihood we are using for inclusion in GSI analysis!

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading
gsi20 <- read.csv("GSI_lowerriver20.csv")[,-1]
gsi21 <- read.csv("GSI_lowerriver21.csv")
#need to bind all together for total body comp GSI dataset, lower river only

gsi_LR_total <- rbind(gsi20[1:60,], gsi21[1:60,])
write.csv(gsi_LR_total, "lowerriver_GSI_all.csv")
lowerriver_GSI_all<-read.csv("lowerriver_GSI_all.csv")[,-1]
#all data is loaded now
#Year already included as a variable/column

#replace blank cell in Sex with NA 
lowerriver_GSI_all$Sex[lowerriver_GSI_all$Sex == ""] <- NA
str(lowerriver_GSI_all)

write.csv(lowerriver_GSI_all, "lowerriver_GSI_all.csv")

```

### Import Data for models, check for NAs and eliminate as needed
```{r}
rm(list = ls())
lowerriver_GSI_PCscores<- "lowerriver_GSI_PCscores.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_GSI_PCscores)[,-1]

### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$Group_Assignment))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex)) # All false!
```
### Calculating Size-Corrected Body Mass in DataSet 
```{r}
### Size corrected body mass should be the residuals of linear regression between weight ~ fish body size PC Score ###
# DataSet$bodysize_pc_g_mm = in the correct units already
DataSet$Fish_Wt_g <- DataSet$Fish_Wt*1000 #grams conversion
sizecorrected_bodymass_lm <- lm(DataSet$Fish_Wt_g ~ DataSet$bodysize_pc_g_mm) #linear regression for size corrected body mass
sizecorrected_bodymass_residuals <- residuals(sizecorrected_bodymass_lm) #residuals for regression
plot(sizecorrected_bodymass_residuals, DataSet$Fish_Leng_Total_mm)
sizecorrected_bodymass <- as.data.frame(sizecorrected_bodymass_residuals)
DataSet <- cbind(DataSet, sizecorrected_bodymass) #adds the residuals to data set as a variable

write.csv(DataSet, "lowerriver_GSI_SizeCorrectedBodyMass.csv") #should all be according to grams and mm values
```


### Import Data for models
```{r}
rm(list = ls())
lowerriver_GSI_scbm <- "lowerriver_GSI_SizeCorrectedBodyMass.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_GSI_scbm)[,-1] #83 variables, 120 observations b/c one row with NA sex is removed


### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$Group_Assignment))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
DataSet$Group_Assignment <- as.factor(DataSet$Group_Assignment)
levels(DataSet$Group_Assignment) #levels are not all consistent. Need to fix this

# Strip whitespace
DataSet$Group_Assignment <- trimws(DataSet$Group_Assignment)

# Standardize levels
DataSet$Group_Assignment <- factor(DataSet$Group_Assignment)
levels(DataSet$Group_Assignment)


# Clean up levels manually
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "Gulkana "] <- "Gulkana"
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "Gulkanahatchery"] <- "GulkanaHatchery"
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "KlutinaTonsinaOutlets"] <- "KlutinaTonsinaOutlet"
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "insufficient genotypes"] <- "insufficient_genotypes"

# Then drop the insufficient genotypes
DataSet <- subset(DataSet, Group_Assignment != "insufficient_genotypes")
DataSet$Group_Assignment <- droplevels(DataSet$Group_Assignment)

# Confirm new levels
levels(DataSet$Group_Assignment) #should have 10 levels


DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet) #collection_rivermile_m is numeric

ggplot(DataSet, aes(x = Fish_Wt_g, y = sizecorrected_bodymass_residuals)) + 
  geom_point() #a couple outliers but nothing too crazy!

```

### Making Models for TotalEnergy~GSI,
```{r}
# Models for reference
scbm_GSI_modelset <- "scbodymass_GSI/SizeCorrectedBodyMass~GSI_modelset.csv"

ModelSet<-read.csv(scbm_GSI_modelset)

model1 <- lm(sizecorrected_bodymass_residuals~1, data=DataSet)
model2 <- lm(sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment, data = DataSet)
model3 <- lm(sizecorrected_bodymass_residuals~Collection_RiverMile_m + Sex, data = DataSet)
model4 <- lm(sizecorrected_bodymass_residuals~Collection_RiverMile_m + Year, data = DataSet)
model5 <- lm(sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment + Sex, data = DataSet)
model6 <- lm(sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment + Year, data = DataSet)
model7 <- lm(sizecorrected_bodymass_residuals~Collection_RiverMile_m + Sex + Year, data = DataSet)
model8 <- lm(sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment + Sex + Group_Assignment:Sex, data = DataSet)
model9 <- lm(sizecorrected_bodymass_residuals~Collection_RiverMile_m + Sex + Year + Sex:Year, data = DataSet)
model10 <- lm(sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment + Sex + Year, data = DataSet)


```

### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

#table of AIC results
mynames1 <- paste("model", as.character(1:10), sep = "")
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("sizecorrected_bodymass_residuals~Collection_RiverMile_m + Sex + Year",
                      "sizecorrected_bodymass_residuals~Collection_RiverMile_m + Sex",
                      "sizecorrected_bodymass_residuals~Collection_RiverMile_m + Sex + Year + Sex:Year",
                      "sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment + Sex + Year",
                      "sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment + Sex",
                      "sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment + Year",
                      "sizecorrected_bodymass_residuals~Collection_RiverMile_m + Year",
                      "sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment",
                      "sizecorrected_bodymass_residuals~Collection_RiverMile_m + Group_Assignment + Sex + Group_Assignment:Sex",
                      "sizecorrected_bodymass_residuals~1")


colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "scBodyMass_GSI/AICresults_SizeCorrectedBodyMass~GSI.csv", row.names = FALSE)


```

### Model Averaging and Parameter Likelihoods
```{r}
library(MuMIn)

# List your models (already fit with na.action=na.fail)
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

# Model averaging based on AICc, conditional averaging (default is full=TRUE)
model_avg <- model.avg(models, rank = "AICc", full = TRUE)

# Summary with coefficients, SE, CIs
summary(model_avg)

# Full averaged coefficients
avg_coefs_full <- coef(model_avg, full = TRUE)

# Full averaged confidence intervals
avg_confint_full <- confint(model_avg, full = TRUE)

# Full averaged variance-covariance matrix and SE
avg_vcov_full <- vcov(model_avg, full = TRUE)
avg_se_full <- sqrt(diag(avg_vcov_full))

# Create tidy data frame with full averages
coefs_df_full <- as.data.frame(avg_coefs_full)
colnames(coefs_df_full) <- "Avg_Coef"
coefs_df_full$CI_Lower <- avg_confint_full[, 1]
coefs_df_full$CI_Upper <- avg_confint_full[, 2]
coefs_df_full$SE <- avg_se_full

# Calculate parameter importance (parameter likelihoods)
param_likelihoods <- sw(model_avg)
as.data.frame(param_likelihoods)

# Manually specify parameter likelihoods from sw(model_avg)
manual_likelihoods <- c(
  "(Intercept)" = 1.0,
  "Collection_RiverMile_m" = 0.999530528,
  "Group_AssignmentChitina" = 0.274494353,
  "Group_AssignmentGulkana" = 0.274494353,
  "Group_AssignmentGulkanaHatchery" = 0.274494353,
  "Group_AssignmentKlutinaLake" = 0.274494353,
  "Group_AssignmentKlutinaTonsinaOutlet" = 0.274494353,
  "Group_AssignmentLowerGroups" = 0.274494353,
  "Group_AssignmentSlana" = 0.274494353,
  "Group_AssignmentTanadaCopperLakes" = 0.274494353,
  "Group_AssignmentTazlina" = 0.274494353,
  "SexM" = 0.915471040,
  "Year2020" = 0.681291194,
  "Year2021" = 0.681291194,
  "SexM:Year2020" = 0.130636880,
  "SexM:Year2021" = 0.130636880,
  "Group_AssignmentChitina:SexM" = 0.002107087,
  "Group_AssignmentGulkana:SexM" = 0.002107087, 
  "Group_AssignmentGulkanaHatchery:SexM" = 0.002107087, 
  "Group_AssignmentKlutinaLake:SexM" = 0.002107087,
  "Group_AssignmentKlutinaTonsinaOutlet:SexM" = 0.002107087,
  "Group_AssignmentLowerGroups:SexM" = 0.002107087, 
  "Group_AssignmentSlana:SexM" = 0.002107087, 
  "Group_AssignmentTanadaCopperLakes:SexM" = 0.002107087,
  "Group_AssignmentTazlina:SexM" = 0.002107087
)



# Add ParamLikelihoods by matching rownames
coefs_df_full$ParamLikelihood <- manual_likelihoods[rownames(coefs_df_full)]

# View final table
print(coefs_df_full)

write.csv(coefs_df_full, file = "scbodymass_GSI/SizeCorrectedBodyMass_GSI_ModelAvg_Coefs_withLikelihoods.csv", row.names = TRUE)




# ---- Step 10: Table for coefficients and threshold for parameter likelihoods ----
#threshold <- 0.1  # Set threshold for importance

# Add a new column to coefs_df that marks important vs non-important parameters
#coefs_df$Importance <- ifelse(coefs_df$ParamLikelihood > threshold, "Important", "Non-Important")

# ---- Color Code Important Parameters with Color Blind Friendly Colors ----
# Light green for important, light gray for non-important
#library(kableExtra)

# Create the table without adding duplicate headers
#coefs_table <- coefs_df %>%
  #arrange(desc(ParamLikelihood)) %>%
  #kable("html", escape = FALSE, align = c("l", "r", "r", "r", "r", "r", "l")) %>%
  # Apply color coding based on importance
  #kable_styling(bootstrap_options = c("striped", "hover")) %>%
  #row_spec(which(coefs_df$Importance == "Important"), background = "lightgreen", color = "black") %>%
  #row_spec(which(coefs_df$Importance == "Non-Important"), background = "lightgray", color = "black") # Adjust column width if needed

# Print or save the table
#coefs_table

```