---
title: "AH_AICc_bodysize~RTG"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for BodySizePC_1~RunTimingGroup models
#' =====================================================

### Loading Data
```{r}
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading
bc19 <- read.csv("bodycomp_2019.csv")
bc20 <- read.csv("bodycomp_2020.csv")
bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, lower river only

bc_LR_total <- rbind(bc19[1:60,], bc20[1:60,], bc21[1:60,])
write.csv(bc_LR_total, "lowerriver_bodycomp_all.csv")
lowerriver_bodycomp_all<-read.csv("lowerriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
lowerriver_bodycomp_all$Collection_Date <- as.Date(lowerriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
lowerriver_bodycomp_all$Year <- year(lowerriver_bodycomp_all$Collection_Date)

#replace blank cell in Sex with NA 
lowerriver_bodycomp_all$Sex[lowerriver_bodycomp_all$Sex == ""] <- NA
str(lowerriver_bodycomp_all)

write.csv(lowerriver_bodycomp_all, "lowerriver_bodycomp_all.csv")

```

### Checking for NAs for PC score
```{r}
rm(list = ls())
lowerriver_bodycomp_all <- "lowerriver_bodycomp_all.csv"
lowerriver_bodycomp_all<-read.csv("lowerriver_bodycomp_all.csv")[,-1]

### Removing NAs that will mess up levels / model weight
any(is.na(lowerriver_bodycomp_all$Collection_Location))
any(is.na(lowerriver_bodycomp_all$RunTimingGroup))
any(is.na(lowerriver_bodycomp_all$Year))
any(is.na(lowerriver_bodycomp_all$Sex))
lowerriver_bodycomp_all[is.na(lowerriver_bodycomp_all$Sex), ] #row 115 has no sex value, eliminate it for models
lowerriver_bodycomp_all <- lowerriver_bodycomp_all[-115,] #excludes row missing sex file
any(is.na(lowerriver_bodycomp_all$Sex))

#checking NA
any(is.na(lowerriver_bodycomp_all$Fish_Leng_2))
any(is.na(lowerriver_bodycomp_all$Fish_Ht))
any(is.na(lowerriver_bodycomp_all$Fish_Grth)) #Na's present, will need to omit them for PC score
lowerriver_bodycomp_all[is.na(lowerriver_bodycomp_all$Fish_Grth), ] #row 64 has NA, remove for PC
```


### Estimate Girth Values for NA rows
```{r}
ggplot(lowerriver_bodycomp_all, aes(x=Fish_Leng_1, y = Fish_Grth)) + 
  geom_point() #length relationship to girth

girth_leng_lm <- lm(Fish_Grth ~ Fish_Leng_1, data = lowerriver_bodycomp_all)
summary(girth_leng_lm) # Adjusted R-squared:  0.3044 

# Subset the data for female F fish only
allfemale_lowerriver_bodycomp <- lowerriver_bodycomp_all[lowerriver_bodycomp_all$Sex == "F", ]

# Perform PCA on the subset of female F fish
pca_model_allF <- princomp(allfemale_lowerriver_bodycomp[,c(12,14,16)], cor=T, scores=T, covmat = NULL)

summary(pca_model_allF, loadings=T, cutoff=0.001) #summary of PC analysis

# Create a new dataframe with PCA scores for the female F fish subset
allfemale_lowerriver_bodycomp <- cbind(allfemale_lowerriver_bodycomp, pca_model_allF$scores[, 1])  # First principal component

# Create the linear model for predicting Fish_Grth based on the first principal component
girth_pc_lm <- lm(Fish_Grth ~ pca_model_allF$scores[, 1], data = allfemale_lowerriver_bodycomp)

# View the summary of the linear model
summary(girth_pc_lm)
plot(girth_pc_lm)


predicted_values <- predict(girth_pc_lm, newdata = allfemale_lowerriver_bodycomp)

allfemale_lowerriver_bodycomp$Predicted_Fish_Grth <- predicted_values # Add these predictions back to your dataset

### the predicted value for row 64 when all female fish is Fish_Grth = 30.00935

#plot the original data and the predicted values to see how well the model fits
ggplot(allfemale_lowerriver_bodycomp, aes(x = Predicted_Fish_Grth, y = Fish_Grth)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Grth, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Fish Growth",
       x = "Comparison PC",
       y = "Fish Growth") +
  theme_minimal() 

###### Now, back to using lowerriver_bodycomp_all #######
lowerriver_bodycomp_all$Fish_Grth[is.na(lowerriver_bodycomp_all$Fish_Grth)] <- 30.00935
any(is.na(lowerriver_bodycomp_all$Fish_Leng_2))
any(is.na(lowerriver_bodycomp_all$Fish_Ht))
any(is.na(lowerriver_bodycomp_all$Fish_Grth)) # no longer an NA present
```

```{r}
# NOT NEEDED ANYMORE w/ PREVIOUS CHUNK
######### lowerriver_bodycomp_all_pc <- lowerriver_bodycomp_all[-64,] #new dataframe with no NA's for bodysize metrics

bc_pca1 <- princomp(lowerriver_bodycomp_all[,c(12,14,16,19)], cor=T, scores=T, covmat = NULL) #should work now without any NAs
summary(bc_pca1, loadings=T, cutoff=0.0001) #summary of PC analysis
bc_pca1$scores
screeplot(bc_pca1, type=c('lines'))
bodysize_pc <- bc_pca1$scores[,1]

#combine dataframe with column for body size PC scores
lowerriver_bodycomp_pc <- cbind(lowerriver_bodycomp_all, bodysize_pc) 

#Now, run AIC again but PC1 scores are the response variable / numeric
write.csv(lowerriver_bodycomp_pc, "lowerriver_bodycomp_PCscores.csv")
```


### Import Data for models
```{r}
rm(list = ls())
lowerriver_bodycomp_PCscores <- "lowerriver_bodycomp_PCscores.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_PCscores)[,-1] #79 variables, 179 observations b/c one row with NA sex is removed

#### CHECK DIRECTION OF PC SCORE ###
library(ggplot2)
ggplot(DataSet, aes(x=Fish_Leng_1, y=bodysize_pc)) +
  geom_point()
#so direction of PC score is positive, can check with other variables

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
DataSet$RunTimingGroup <- as.factor(DataSet$RunTimingGroup)
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet) #collection_rivermile_m is numeric

```


### Making Models for bodysize_pc~RunTimingGroup, includes collection location
```{r}
# Models for reference
bodysize_RTG_modelset <- "bodysize_runtiminggroup/bodysize~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(bodysize_RTG_modelset)

model1 <- lm(bodysize_pc~1, data=DataSet)
# model2 <- lm(bodysize_pc~Collection_Location, data = DataSet) , not using anymore
model2 <- lm(bodysize_pc~Collection_RiverMile_m + RunTimingGroup, data = DataSet)
model3 <- lm(bodysize_pc~Collection_RiverMile_m + Sex, data = DataSet)
model4 <- lm(bodysize_pc~Collection_RiverMile_m + Year, data = DataSet)
model5 <- lm(bodysize_pc~Collection_RiverMile_m + RunTimingGroup + Sex, data = DataSet)
model6 <- lm(bodysize_pc~Collection_RiverMile_m + RunTimingGroup + Year, data = DataSet)
model7 <- lm(bodysize_pc~Collection_RiverMile_m + Sex + Year, data = DataSet)
model8 <- lm(bodysize_pc~Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex, data = DataSet)
# model10 <- lm(bodysize_pc~Collection_Location + RunTimingGroup + Year + RunTimingGroup:Year, data = DataSet) ,   not using anymore
model9 <- lm(bodysize_pc~Collection_RiverMile_m + Sex + Year + Sex:Year, data = DataSet)
model10 <- lm(bodysize_pc~Collection_RiverMile_m + RunTimingGroup + Sex + Year, data = DataSet)

```


### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

#table of AIC results
mynames1 <- paste("model", as.character(1:10), sep = "")
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("bodysize_pc~Collection_RiverMile_m + RunTimingGroup + Sex",
                      "bodysize_pc~Collection_RiverMile_m + RunTimingGroup + Sex + Year",
                      "bodysize_pc~Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex", 
                      "bodysize_pc~Collection_RiverMile_m + Sex", 
                      "bodysize_pc~Collection_RiverMile_m + Sex + Year",
                      "bodysize_pc~Collection_RiverMile_m + Sex + Year + Sex:Year", 
                      "bodysize_pc~Collection_RiverMile_m + RunTimingGroup",
                      "bodysize_pc~Collection_RiverMile_m + RunTimingGroup + Year", 
                      "bodysize_pc~1", 
                      "bodysize_pc~Collection_RiverMile_m + Year")
colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "bodysize_runtiminggroup/AICresults_bodysize~RunTimingGroup.csv", row.names = FALSE)

```

### Model Averaging
```{r}
library(MuMIn)

 # Create a model selection table (this will give you AIC, AIC weights, etc.)
model_weights <- myaicc1$AICcWt ##Get the AIC weights from the AIC table
model_avg <- model.avg(models, weights = model_weights)
summary(model_avg)
avg_coefs <- coef(model_avg)
avg_confint <- confint(model_avg)
avg_se <- sqrt(diag(vcov(model_avg)))

# Convert the coefficients into a tidy data frame
coefs_df <- as.data.frame(avg_coefs)
colnames(coefs_df) <- "Avg_Coef"
coefs_df$CI_Lower <- avg_confint[, 1]  # Add lower bound of confidence intervals
coefs_df$CI_Upper <- avg_confint[, 2] # Add upper bound of confidence intervals
coefs_df$SE <- avg_se
print(coefs_df) #Model Averaging Coefficients for AIC model selection approach with body size as response variable

write.csv(coefs_df, file = "bodysize_runtiminggroup/bodysize~runtiminggroup_models_CoefEstimates.csv", row.names = TRUE)
```

### Visualizing Results from body size~RunTimingGroup Model 5
```{r}
#  Model 5
# bodysize_pc ~ Collection_RiverMile_m + RunTimingGroup + Sex
library(dplyr)
summary(model5)

DataSet$RunTimingGroup <- factor(DataSet$RunTimingGroup,
                               levels = c("Early",
                                          "Middle",
                                          "Late"),
                               labels = c("Early",
                                          "Middle",
                                          "Late"))

#boxplot
ggplot(data = DataSet, aes(x = RunTimingGroup, y = bodysize_pc, fill = Sex)) +
  geom_boxplot() +
  labs(title = "Bodysize PC by Run Timing Group and Sex",
       x = "Run Timing Group",
       y = "Bodysize PC",
       color = "Sex") +
  theme_minimal()

#violin plot
ggplot(data = DataSet, aes(x = RunTimingGroup, y = bodysize_pc, fill = Sex)) +
  geom_violin() +
  labs(title = "Bodysize PC by Run Timing Group and Sex",
       x = "Run Timing Group",
       y = "Bodysize PC",
       fill = "Sex") +
  theme_minimal()

#interaction plot
ggplot(data = DataSet, aes(x = RunTimingGroup, y = bodysize_pc, color = Sex)) +
  geom_point() + 
  geom_smooth(method = "lm", aes(group = Sex), se = TRUE) +  # Add regression lines for each 'Sex' group
  labs(title = "Interaction Between Run Timing Group and Sex on Bodysize PC",
       x = "Run Timing Group",
       y = "Bodysize PC") +
  theme_minimal()

#bar plot can show the mean value of bodysize_pc for each combination of RunTimingGroup and Sex, providing an overall comparison of group means.
ggplot(data = DataSet, aes(x = RunTimingGroup, y = bodysize_pc, fill = Sex)) +
  stat_summary(fun = "mean", geom = "bar", position = "dodge") +
  labs(title = "Mean Bodysize PC by Run Timing Group and Sex",
       x = "Run Timing Group",
       y = "Mean Bodysize PC",
       fill = "Sex") +
  theme_minimal()
```

### FOR AMSS
```{r}
#Body size ~ RunTimingGroup + Sex , in order to address hypothesis 1 and hypothesis 3

#Boxplot
g <- ggplot(data = DataSet, aes(x = RunTimingGroup, y = bodysize_pc, fill = Sex)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#1F78B4", "#E31A1C")) +  # Set color for Female and Male
  labs(x = "Run Timing Group",
       y = "Body Size PC Score",
       fill = "Sex") +
  theme_linedraw() +
  theme(
    axis.title = element_text(size = 26, face = "bold"),     # Increase axis title size
    axis.text = element_text(size = 24),      # Increase axis text size
    legend.title = element_text(size = 26, face = "bold"),   # Increase legend title size
    legend.text = element_text(size = 24)     # Increase legend text size
  ) 

ggsave("AMSS_2025/AMSS body size ~ RTG + Sex Plot.png", plot=g, height=8, width=16, units="in")



#Interaction Plot
ggplot(data = DataSet, aes(x = RunTimingGroup, y = bodysize_pc, color = Sex)) +
  geom_point() + 
  geom_smooth(method = "lm", aes(group = Sex), se = TRUE) +  # Add regression lines for each 'Sex' group
  labs(title = "Interaction Between Run Timing Group and Sex on Bodysize PC",
       x = "Run Timing Group",
       y = "Bodysize PC") +
  theme_minimal()

```





### Messing with Collection_Location
```{r}
#Linear regression between bodysize_pc and collection_location
bodysize_collectionlocation_lm <- lm(DataSet$bodysize_pc ~ DataSet$Collection_Location)

#residuals of the linear regression
bodysize_collectionlocation_resid <- residuals(bodysize_collectionlocation_lm)
plot(bodysize_collectionlocation_resid, DataSet$bodysize_pc)

#turning residuals into dataframe
bodysize_ColLoc <- as.data.frame(bodysize_collectionlocation_resid)
DataSet <- cbind(DataSet, bodysize_ColLoc) #now has new column where body size pc is a variable but its already accounted for collection_location


```

### Making Models for bodysize_ColLoc~RunTimingGroup, no collection location
```{r}
# Models for reference
bodysize_RTG_modelset <- "bodysize_runtiminggroup/bodysize~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(bodysize_RTG_modelset)

model1a <- lm(bodysize_collectionlocation_resid~1, data=DataSet)
model2a <- lm(bodysize_collectionlocation_resid~RunTimingGroup, data = DataSet)
model3a <- lm(bodysize_collectionlocation_resid~Sex, data = DataSet)
model4a <- lm(bodysize_collectionlocation_resid~Year, data = DataSet)
model5a <- lm(bodysize_collectionlocation_resid~RunTimingGroup + Sex, data = DataSet)
model6a <- lm(bodysize_collectionlocation_resid~RunTimingGroup + Year, data = DataSet)
model7a <- lm(bodysize_collectionlocation_resid~Sex + Year, data = DataSet)
model8a <- lm(bodysize_collectionlocation_resid~RunTimingGroup + Sex + RunTimingGroup:Sex, data = DataSet)
model9a <- lm(bodysize_collectionlocation_resid~RunTimingGroup + Year + RunTimingGroup:Year, data = DataSet)
model10a <- lm(bodysize_collectionlocation_resid~Sex + Year + Sex:Year, data = DataSet)
model11a <- lm(bodysize_collectionlocation_resid~RunTimingGroup + Sex + Year, data = DataSet)

```

### AICc Model Selection, models without Collection Location
```{r}
AIC(model1a, model2a, model3a, model4a, model5a, model6a, model7a, model8a, model9a, model10a, model11a)

#table of AIC results
mynames2 <- paste("model", as.character(1:11), sep = "")
models2 <- list(model1a, model2a, model3a, model4a, model5a, model6a, model7a, model8a, model9a, model10a, model11a)

# Generate AIC table
myaicc2 <- aictab(models2, modnames = mynames2)
print(myaicc2) #model 5 has the lowest AICc score followed by the global model (model 11)
# Convert AIC table to a data frame for easier manipulation
aic_df2 <- as.data.frame(myaicc2)
aic_df2$ModelName <- c("bodysize_collectionlocation_resid~RunTimingGroup + Sex",
                      "bodysize_collectionlocation_resid~RunTimingGroup + Sex + Year",
                      "bodysize_collectionlocation_resid~RunTimingGroup + Sex + RunTimingGroup:Sex",
                      "bodysize_collectionlocation_resid~Sex",
                      "bodysize_collectionlocation_resid~Sex + Year",
                      "bodysize_collectionlocation_resid~Sex + Year + Sex:Year",
                      "bodysize_collectionlocation_resid~RunTimingGroup",
                      "bodysize_collectionlocation_resid~RunTimingGroup + Year",
                      "bodysize_collectionlocation_resid~1",
                      "bodysize_collectionlocation_resid~Year",
                      "bodysize_collectionlocation_resid~RunTimingGroup + Year + RunTimingGroup:Year")
colnames(aic_df2)[colnames(aic_df2) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df2, file = "bodysize_runtiminggroup/AICresults_BodySizeCollectionLocationResiduals~RunTimingGroup.csv", row.names = FALSE)

```


### Model Averaging for body size models that already account for collection_location
```{r}
library(MuMIn)

# Create a model selection table (this will give you AIC, AIC weights, etc.)
model_weights2 <- myaicc2$AICcWt ##Get the AIC weights from the AIC table
model_avg2 <- model.avg(models2, weights = model_weights2)
summary(model_avg2)
avg_coefs2 <- coef(model_avg2)
avg_confint2 <- confint(model_avg2)

# Convert the coefficients into a tidy data frame
coefs_df2 <- as.data.frame(avg_coefs2)
colnames(coefs_df2) <- "Avg_Coef"
coefs_df2$CI_Lower <- avg_confint2[, 1]  # Add lower bound of confidence intervals
coefs_df2$CI_Upper <- avg_confint2[, 2]  # Add upper bound of confidence intervals
print(coefs_df2) #Model Averaging Coefficients for AIC model selection approach with body size as response variable

write.csv(coefs_df2, file = "bodysize_runtiminggroup/BodySizeCollectionLocationResiduals~RunTimingGroup_models_CoefEstimates.csv", row.names = TRUE)
```
