---
title: "AH_AICc_bodysize~SP"
author: "Abby Host"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for BodySizePC_1~SpawningPopulation models
#' =====================================================

### Loading Data
```{r}
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading
bc19 <- read.csv("bodycomp_2019.csv")
bc20 <- read.csv("bodycomp_2020.csv")
bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, lower river only

bc_LR_total <- rbind(bc19[1:60,], bc20[1:60,], bc21[1:60,])
write.csv(bc_LR_total, "lowerriver_bodycomp_all.csv")
lowerriver_bodycomp_all<-read.csv("lowerriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
lowerriver_bodycomp_all$Collection_Date <- as.Date(lowerriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
lowerriver_bodycomp_all$Year <- year(lowerriver_bodycomp_all$Collection_Date)

#replace blank cell in Sex with NA 
lowerriver_bodycomp_all$Sex[lowerriver_bodycomp_all$Sex == ""] <- NA
str(lowerriver_bodycomp_all)

write.csv(lowerriver_bodycomp_all, "lowerriver_bodycomp_all.csv")
