---
title: "AH_AICc_fecundity~GSI"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for Fecundity~GSI models
#' =====================================================

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading, use the bodysize_pc data because it will be a variable of interest
lowerriver_GSI_PCscores <- "lowerriver_GSI_PCscores.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_GSI_PCscores)[,-1]
```

### Removing NAs and subsetting female fish for fecundity
```{r}
### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$Group_Assignment))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex)) # All false

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
DataSet$Group_Assignment <- as.factor(DataSet$Group_Assignment)
levels(DataSet$Group_Assignment) #levels are not all consistent. Need to fix this

# Strip whitespace
DataSet$Group_Assignment <- trimws(DataSet$Group_Assignment)

# Standardize levels
DataSet$Group_Assignment <- factor(DataSet$Group_Assignment)
levels(DataSet$Group_Assignment)


# Clean up levels manually
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "Gulkana "] <- "Gulkana"
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "Gulkanahatchery"] <- "GulkanaHatchery"
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "KlutinaTonsinaOutlets"] <- "KlutinaTonsinaOutlet"
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "insufficient genotypes"] <- "insufficient_genotypes"

# Then drop the insufficient genotypes
DataSet <- subset(DataSet, Group_Assignment != "insufficient_genotypes")
DataSet <- subset(DataSet, Group_Assignment != "LowerGroups")
DataSet$Group_Assignment <- droplevels(DataSet$Group_Assignment)

# Confirm new levels
levels(DataSet$Group_Assignment) #should have 9 levels


DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet) #collection_rivermile_m is numeric

DataSetF <- subset(DataSet, Sex == "F")

```

## Calculating Fecundity for the DataSetF 
```{r}
DataSetF$Fecun_num_by_wt1 <- (DataSetF$Fem_Fecun_1_num/DataSetF$Fem_Fecun_1_wt)*(DataSetF$Gonad_Wt * 1000)
#unsure if there is enough of 2 and 3 subsamples to find averages as necessary, so just use the first sub sample here

# View DataSet.
head(DataSetF)
summary(DataSetF)
nrow(DataSetF)
str(DataSetF)

str(DataSetF) #collection_rivermile_m is numeric
```

### Making Models for fecundity~GSI, includes collection location
```{r}
# Models for reference
fecundity_GSI_modelset <- "fecundity_GSI/fecundity~GSI_modelset.csv"

ModelSet<-read.csv(fecundity_GSI_modelset)

model1 <- lm(Fecun_num_by_wt1~1, data=DataSetF)
model2 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc, data=DataSetF)
model3 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1, data=DataSetF)
model4 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + Group_Assignment, data=DataSetF)
model5 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1, data=DataSetF)
model6 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + Group_Assignment, data=DataSetF)
model7 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1 + Group_Assignment, data=DataSetF)
model8 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + Group_Assignment, data=DataSetF)

```

### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8)

#table of AIC results
mynames1 <- paste("model", as.character(1:8), sep = "")
models <- list(model1, model2, model3, model4, model5, model6, model7, model8)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc",
                      "Fecun_num_by_wt1~1",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + Group_Assignment",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + Group_Assignment",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + Group_Assignment",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1 + Group_Assignment")


colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "fecundity_GSI/AICresults_Fecundity~GSI.csv", row.names = FALSE)


```

### Model Averaging and Parameter Likelihoods
```{r}
library(MuMIn)

# List your models (already fit with na.action=na.fail)
models <- list(model1, model2, model3, model4, model5, model6, model7, model8)

# Model averaging based on AICc, conditional averaging (default is full=TRUE)
model_avg <- model.avg(models, rank = "AICc", full = TRUE)

# Summary with coefficients, SE, CIs
summary(model_avg)

# Full averaged coefficients
avg_coefs_full <- coef(model_avg, full = TRUE)

# Full averaged confidence intervals
avg_confint_full <- confint(model_avg, full = TRUE)

# Full averaged variance-covariance matrix and SE
avg_vcov_full <- vcov(model_avg, full = TRUE)
avg_se_full <- sqrt(diag(avg_vcov_full))

# Create tidy data frame with full averages
coefs_df_full <- as.data.frame(avg_coefs_full)
colnames(coefs_df_full) <- "Avg_Coef"
coefs_df_full$CI_Lower <- avg_confint_full[, 1]
coefs_df_full$CI_Upper <- avg_confint_full[, 2]
coefs_df_full$SE <- avg_se_full

# Calculate parameter importance (parameter likelihoods)
param_likelihoods <- sw(model_avg)
as.data.frame(param_likelihoods)

# Manually specify parameter likelihoods from sw(model_avg)
manual_likelihoods <- c(
  "(Intercept)" = 1.0,
  "Collection_RiverMile_m" = 0.8134145,
  "Group_AssignmentChitina" = 0.1724891,
  "Group_AssignmentGulkana" = 0.1724891,
  "Group_AssignmentGulkanaHatchery" = 0.1724891,
  "Group_AssignmentKlutinaLake" = 0.1724891,
  "Group_AssignmentKlutinaTonsinaOutlet" = 0.1724891,
  "Group_AssignmentLowerGroups" = 0.1724891,
  "Group_AssignmentSlana" = 0.1724891,
  "Group_AssignmentTanadaCopperLakes" = 0.1724891,
  "Group_AssignmentTazlina" = 0.1724891,
  "bodysize_pc" = 0.7315382,
  "EnergyPDry_1" = 0.2111615
)


# Add ParamLikelihoods by matching rownames
coefs_df_full$ParamLikelihood <- manual_likelihoods[rownames(coefs_df_full)]

# View final table
print(coefs_df_full)

write.csv(coefs_df_full, "fecundity_GSI/Fecundity_GSI_ModelAvg_Coefs_withLikelihoods.csv", row.names = TRUE)


```

### Using summed weighted parameter estimates for total energy by GSI ~ work (successful size for migration, as continuous variable)
```{r}
# Step 1: Extract intercept
intercept <- coefs_df_full["(Intercept)", "Avg_Coef"]

# Step 2: Extract Group_Assignment effects
GSI_effects <- coefs_df_full[grep("^Group_Assignment", rownames(coefs_df_full)), ]
GSI_effects <- GSI_effects[!grepl(":", rownames(GSI_effects)), ]  # remove interaction terms

# Extract location names (remove "Collection_Location" from row names)
GSI_effects$GSI <- gsub("Group_Assignment", "", rownames(GSI_effects))

# Step 3: Add intercept to each to get estimated body size
GSI_effects$Estimated_Fecundity <- intercept + GSI_effects$Avg_Coef

# Step 4: Add back the reference location (intercept only)
ref_location <- levels(DataSet$Group_Assignment)[1]  # Assumes first level is the reference
ref_row <- data.frame(
  Avg_Coef = intercept,
  CI_Lower = coefs_df_full["(Intercept)", "CI_Lower"],
  CI_Upper = coefs_df_full["(Intercept)", "CI_Upper"],
  SE = coefs_df_full["(Intercept)", "SE"],
  ParamLikelihood = coefs_df_full["(Intercept)", "ParamLikelihood"],
  GSI = ref_location,
  Estimated_Fecundity = intercept
)

# Step 5: Combine
GSI_estimates <- rbind(ref_row, GSI_effects)
rownames(GSI_estimates) <- NULL
GSI_estimates <- GSI_estimates[, c("GSI", setdiff(names(GSI_estimates), "GSI"))]

#write.csv(GSI_estimates, "fecundity_GSI/FecundityEstimates_GroupAssignments.csv", row.names = TRUE)

# Step 6: Compute average Work per location
library(dplyr)

# Check unique values
unique(DataSet$Group_Assignment)
avg_work <- DataSet %>%
  dplyr::group_by(Group_Assignment) %>%
  dplyr::summarise(Avg_Work = mean(Work_km2, na.rm = TRUE), .groups = "drop")

# Step 7: Merge with estimates
GSI_estimates <- merge(GSI_estimates, avg_work, by.x = "GSI", by.y = "Group_Assignment")

# Step 8: Linear regression of estimated body size ~ work
fecundity_work_model <- lm(Estimated_Fecundity ~ Avg_Work, data = GSI_estimates)
summary(fecundity_work_model)

# Step 9: Visualization
library(ggplot2)
ggplot(GSI_estimates, aes(x = Avg_Work, y = Estimated_Fecundity, label = GSI)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  geom_text(nudge_y = 0.05, size = 3) +
  labs(title = "Model-Averaged Estimated Fecundity vs. Migration Work",
       x = "Migration Work (km²)", y = "Estimated Fecundity") +
  theme_minimal() + 
   theme(
  plot.title = element_text(size = 16, face = "bold"),
  axis.title.x = element_text(size = 16, face = "bold"),
  axis.title.y = element_text(size = 16, face = "bold"),
  axis.text.x = element_text(size = 16),
  axis.text.y = element_text(size = 16),
  legend.title = element_text(size = 16, face = "bold"),
  legend.text = element_text(size = 16)
)


#Remove Chitina
GSI_estimates_noChitina <- GSI_estimates %>%
  filter(!GSI %in% c("Chitina"))

# Linear regression of estimated body size ~ work, no chitina
fecundity_work_model_noChitina <- lm(Estimated_Fecundity ~ Avg_Work, data = GSI_estimates_noChitina)
summary(fecundity_work_model_noChitina) #R squared decreases, so not a necessary removal

# Step 9: Visualization
library(ggplot2)
ggplot(GSI_estimates_noChitina, aes(x = Avg_Work, y = Estimated_Fecundity, label = GSI)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  geom_text(nudge_y = 0.05, size = 3) +
  labs(title = "Model-Averaged Estimated Fecundity vs. Migration Work",
       x = "Migration Work (km²)", y = "Estimated Fecundity") +
  theme_minimal() + 
   theme(
  plot.title = element_text(size = 16, face = "bold"),
  axis.title.x = element_text(size = 16, face = "bold"),
  axis.title.y = element_text(size = 16, face = "bold"),
  axis.text.x = element_text(size = 16),
  axis.text.y = element_text(size = 16),
  legend.title = element_text(size = 16, face = "bold"),
  legend.text = element_text(size = 16)
)


#Remove Gulkana Hatchery
GSI_estimates_noGH <- GSI_estimates %>%
  filter(!GSI %in% c("GulkanaHatchery"))

# Linear regression of estimated body size ~ work, no chitina
fecundity_work_model_noGH <- lm(Estimated_Fecundity ~ Avg_Work, data = GSI_estimates_noGH)
summary(fecundity_work_model_noGH) #R squared increases significantly for fit

# Step 9: Visualization
library(ggplot2)
ggplot(GSI_estimates_noGH, aes(x = Avg_Work, y = Estimated_Fecundity, label = GSI)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  geom_text(nudge_y = 0.05, size = 3) +
  labs(title = "Model-Averaged Estimated Fecundity vs. Migration Work",
       x = "Migration Work (km²)", y = "Estimated Fecundity") +
  theme_minimal() + 
   theme(
  plot.title = element_text(size = 16, face = "bold"),
  axis.title.x = element_text(size = 16, face = "bold"),
  axis.title.y = element_text(size = 16, face = "bold"),
  axis.text.x = element_text(size = 16),
  axis.text.y = element_text(size = 16),
  legend.title = element_text(size = 16, face = "bold"),
  legend.text = element_text(size = 16)
)


```

### Calculating actual parameter estimates according to intercept
```{r}
coefs_df_full$Actual_Param <- with(coefs_df_full, 
                                   Avg_Coef + coefs_df_full["(Intercept)", "Avg_Coef"])
coefs_df_full["(Intercept)", "Actual_Param"] <- coefs_df_full["(Intercept)", "Avg_Coef"]
```

### Estimates Figure
```{r}
# Figure that displays parameter estimates + CI for each parameter in teh model set
paramestimates_fecGSI <- "fecundity_GSI/Fecundity_GSI_ModelAvg_Coefs_withLikelihoods.csv"

estimates_fecGSI<-read.csv(paramestimates_fecGSI)
str(estimates_fecGSI)

levels(factor(estimates_fecGSI$X))
estimates_fecGSI$X <- factor(estimates_fecGSI$X, 
                           levels = rev(c( "(Intercept)",
                                           "Collection_RiverMile_m",
                                           "Group_AssignmentChitina",
                                           "Group_AssignmentGulkana",
                                           "Group_AssignmentGulkanaHatchery",
                                           "Group_AssignmentKlutinaLake",
                                           "Group_AssignmentKlutinaTonsinaOutlet",
                                           "Group_AssignmentLowerGroups",
                                           "Group_AssignmentSlana",
                                           "Group_AssignmentTanadaCopperLakes",
                                           "Group_AssignmentTazlina",
                                           "Year2021",
                                           "bodysize_pc",
                                           "EnergyPDry_1",
                                           "EnergyPDry_1:Group_AssignmentChitina",
                                           "EnergyPDry_1:Group_AssignmentGulkana",
                                           "EnergyPDry_1:Group_AssignmentGulkanaHatchery",
                                           "EnergyPDry_1:Group_AssignmentKlutinaLake",
                                           "EnergyPDry_1:Group_AssignmentKlutinaTonsinaOutlet",
                                           "EnergyPDry_1:Group_AssignmentSlana",
                                           "EnergyPDry_1:Group_AssignmentTanadaCopperLakes",
                                           "EnergyPDry_1:Group_AssignmentTazlina")))



ggplot(estimates_fecGSI, aes(x = Avg_Coef, y = X)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))



```