---
title: "AH_AICc_fecundity~RTG"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for Fecundity~RunTimingGroup models
#' =====================================================

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading, use the bodysize_pc data because it will be a variable of interest
lowerriver_bodycomp_PCscores <- "lowerriver_bodycomp_PCscores.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_PCscores)[,-1]
```

### Removing NAs and subsetting female fish for fecundity
```{r}
### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$RunTimingGroup))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex)) # All false

DataSetF <- subset(DataSet, Sex == "F")

```

## Calculating Fecundity for the DataSetF 
```{r}
# values i have for fecundity are # of eggs in a subsample and weight of eggs in a subsample-- so I think best to calculate #/g and then average the three subsamples 

DataSetF$Fecun_num_by_wt1 <- (DataSetF$Fem_Fecun_1_num/DataSetF$Fem_Fecun_1_wt)*DataSetF$Gonad_Wt
#unsure if there is enough of 2 and 3 subsamples to find averages as necessary, so just use the first sub sample here

# View DataSet.
head(DataSetF)
summary(DataSetF)
nrow(DataSetF)
str(DataSetF)

#make response variables factors
DataSetF$RunTimingGroup <- as.factor(DataSetF$RunTimingGroup)
DataSetF$Year<- as.factor(DataSetF$Year)
str(DataSetF) #collection_rivermile_m is numeric
```

### Making Models for fecundity~RunTimingGroup, includes collection location
```{r}
# Models for reference
fecundity_RTG_modelset <- "fecundity_runtiminggroup/fecundity~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(fecundity_RTG_modelset)

model1 <- lm(Fecun_num_by_wt1~1, data=DataSetF)
model2 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc, data=DataSetF)
model3 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1, data=DataSetF)
model4 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + RunTimingGroup, data=DataSetF)
model5 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + Year, data=DataSetF)
model6 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1, data=DataSetF)
model7 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc*EnergyPDry_1, data=DataSetF)
model8 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + RunTimingGroup, data=DataSetF)
model9 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc*RunTimingGroup, data=DataSetF)
model10 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + Year, data=DataSetF)
model11 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc*Year, data=DataSetF)
model12 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1 + RunTimingGroup, data=DataSetF)
model13 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1*RunTimingGroup, data=DataSetF)
model14 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1 + Year, data=DataSetF)
model15 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1*Year, data=DataSetF)
model16 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + RunTimingGroup + Year, data=DataSetF)
model17 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup, data=DataSetF)
model18 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + Year, data=DataSetF)
model19 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + RunTimingGroup + Year, data=DataSetF)
model20 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m +  EnergyPDry_1 + RunTimingGroup + Year, data=DataSetF)
model21 <- lm(Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup + Year, data=DataSetF)

```

### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12, model13, model14, model15, model16, model17, model18, model19, model20, model21)

#table of AIC results
mynames1 <- paste("model", as.character(1:21), sep = "")
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12, model13, model14, model15, model16, model17, model18, model19, model20, model21)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + Year",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + RunTimingGroup + Year",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + Year",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc*Year",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup + Year",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + RunTimingGroup",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc*RunTimingGroup",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + Year",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + bodysize_pc*EnergyPDry_1",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1 + Year",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + RunTimingGroup + Year",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1 + RunTimingGroup",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + RunTimingGroup",
                      "Fecun_num_by_wt1~Collection_RiverMile_m +  EnergyPDry_1 + RunTimingGroup + Year",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1*RunTimingGroup",
                      "Fecun_num_by_wt1~Collection_RiverMile_m + EnergyPDry_1*Year",
                      "Fecun_num_by_wt1~1")
colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "fecundity_runtiminggroup/AICresults_fecundity~RunTimingGroup.csv", row.names = FALSE)

```

### Model Averaging
```{r}
library(MuMIn)

 # Create a model selection table (this will give you AIC, AIC weights, etc.)
model_weights <- myaicc1$AICcWt ##Get the AIC weights from the AIC table
model_avg <- model.avg(models, weights = model_weights)
summary(model_avg)
avg_coefs <- coef(model_avg)
avg_confint <- confint(model_avg)
avg_se <- sqrt(diag(vcov(model_avg)))

# Convert the coefficients into a tidy data frame
coefs_df <- as.data.frame(avg_coefs)
colnames(coefs_df) <- "Avg_Coef"
coefs_df$CI_Lower <- avg_confint[, 1]  # Add lower bound of confidence intervals
coefs_df$CI_Upper <- avg_confint[, 2] # Add upper bound of confidence intervals
coefs_df$SE <- avg_se
print(coefs_df) #Model Averaging Coefficients for AIC model selection approach with body size as response variable

write.csv(coefs_df, file = "fecundity_runtiminggroup/fecundity~runtiminggroup_models_CoefEstimates.csv", row.names = TRUE)
```

### Parameter Likelihoods
```{r}
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12, model13, model14, model15, model16, model17, model18, model19, model20, model21)

# Assign model names
model_names <- paste0("Model_", seq_along(models))

# Compute AICc and model weights
aic_table <- aictab(cand.set = models, modnames = model_names)
weights <- aic_table$AICcWt  # Extract AICc weights

# Extract model coefficients
param_names <- unique(unlist(sapply(models, function(m) names(coef(m)))))

# Compute parameter likelihoods
param_likelihoods <- sapply(param_names, function(param) {
  # Identify models that include this parameter
  models_with_param <- sapply(models, function(m) param %in% names(coef(m)))
  
  # Sum AICc weights for models that include this parameter
  sum(weights[models_with_param])
})

# Format output as a data frame
param_likelihoods_df <- data.frame(Parameter = param_names, WeightedLikelihood = param_likelihoods)

# Make sure that coefs_df has a column with the parameter names
coefs_df$Parameter <- rownames(coefs_df)  # Add the parameter names to the dataframe
coefs_df <- coefs_df[, c("Parameter", "Avg_Coef", "CI_Lower", "CI_Upper", "SE")]


# Now, we will merge coefs_df with param_likelihoods_df by 'Parameter' to add the likelihoods
coefs_df <- merge(coefs_df, param_likelihoods_df, by = "Parameter", all.x = TRUE)

# Print the updated dataframe to see the result
print(coefs_df)

colnames(coefs_df)[colnames(coefs_df) == "WeightedLikelihood"] <- "ParamLikelihood"

coefs_df <- coefs_df %>%
  arrange(desc(ParamLikelihood)) #arrange dataframe in descending order according to ParamLikelihoods

# Optionally, write the results to a CSV file
write.csv(coefs_df, file = "fecundity_runtiminggroup/fecundity~runtiminggroup_models_CoefEstimates_withLikelihoods.csv", row.names = TRUE)


```


### Figure that displays parameter estimates + CI for each parameter in the model set
```{r}
paramestimates_fecundity <- "fecundity_runtiminggroup/fecundity~runtiminggroup_models_CoefEstimates.csv"

paramestimates_fecundity<-read.csv(paramestimates_fecundity)
str(paramestimates_fecundity)

levels(factor(paramestimates_fecundity$X))
paramestimates_fecundity$X <- factor(paramestimates_fecundity$X, 
                           levels = rev(factor(paramestimates_fecundity$X)))


library(ggplot2)
ggplot(paramestimates_fecundity, aes(x = Avg_Coef, y = X)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

library(dplyr)
paramestimates_fecundity_filtered <- paramestimates_fecundity %>%
  filter(X != "Collection_RiverMile_m")

fecundity_plot <- ggplot(paramestimates_fecundity_filtered, aes(x = Avg_Coef, y = X)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

ggsave("fecundity_runtiminggroup/Fecundity_ParamEstimates_Plot.png", plot=fecundity_plot, height=12, width=12, units="in")


```
