---
title: "AH_AICc_eggsize~RTG"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for EggSize~RunTimingGroup models
#' =====================================================


#### NOT planning on using for lower river (run timing group analysis) unless the spawning ground analysis leads us to think it may be valuable


### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading, use the bodysize_pc data because it will be a variable of interest
lowerriver_bodycomp_PCscores <- "lowerriver_bodycomp_PCscores.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_PCscores)[,-1]
```

### Removing NAs and subsetting female fish for fecundity
```{r}
### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$RunTimingGroup))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex)) # All false

DataSetF <- subset(DataSet, Sex == "F")

#Will be using the following metric
DataSetF$Fem_Egg_Sz_1

# View DataSet.
head(DataSetF)
summary(DataSetF)
nrow(DataSetF)
str(DataSetF)

#make response variables factors
DataSetF$RunTimingGroup <- as.factor(DataSetF$RunTimingGroup)
DataSetF$Year<- as.factor(DataSetF$Year)
str(DataSetF) #collection_rivermile_m is numeric
```

### Making Models for eggsize~RunTimingGroup, includes collection location
```{r}
# Models for reference
eggsize_RTG_modelset <- "eggsize_runtiminggroup/eggsize~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(eggsize_RTG_modelset)


model1 <- lm(Fem_Egg_Sz_1~1, data=DataSetF)
model2 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc, data=DataSetF)
model3 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1, data=DataSetF)
model4 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + RunTimingGroup, data=DataSetF)
model5 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + Year, data=DataSetF)
model6 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1, data=DataSetF)
model7 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + RunTimingGroup, data=DataSetF)
model8 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + Year, data=DataSetF)
model9 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1 + RunTimingGroup, data=DataSetF)
model10 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1*RunTimingGroup, data=DataSetF)
model11 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1 + Year, data=DataSetF)
model12 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + RunTimingGroup + Year, data=DataSetF)
model13 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup, data=DataSetF)
model14 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + Year, data=DataSetF)
model15 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + RunTimingGroup + Year, data=DataSetF)
model16 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m +  EnergyPDry_1 + RunTimingGroup + Year, data=DataSetF)
model17 <- lm(Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup + Year, data=DataSetF)

```

### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12, model13, model14, model15, model16, model17, model18, model19, model20, model21)

#table of AIC results
mynames1 <- paste("model", as.character(1:21), sep = "")
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12, model13, model14, model15, model16, model17, model18, model19, model20, model21)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup + Year",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1*RunTimingGroup",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m +  EnergyPDry_1 + RunTimingGroup + Year",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + RunTimingGroup",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1 + RunTimingGroup",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc*RunTimingGroup",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + RunTimingGroup + Year",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + RunTimingGroup",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + RunTimingGroup + Year",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1 + Year",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc*EnergyPDry_1",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + Year",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc",
                      "Fem_Egg_Sz_1~1",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1*Year",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + Year",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + Year",
                      "Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc*Year")
colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "eggsize_runtiminggroup/AICresults_eggsize~RunTimingGroup.csv", row.names = FALSE)

```
The top chosen models via AICc, with delta AICc values > 2.00 are:
1. Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup
2. Fem_Egg_Sz_1~Collection_RiverMile_m + bodysize_pc + EnergyPDry_1 + RunTimingGroup + Year
3. Fem_Egg_Sz_1~Collection_RiverMile_m + EnergyPDry_1*RunTimingGroup

### Model Averaging
```{r}
library(MuMIn)

 # Create a model selection table (this will give you AIC, AIC weights, etc.)
model_weights <- myaicc1$AICcWt ##Get the AIC weights from the AIC table
model_avg <- model.avg(models, weights = model_weights)
summary(model_avg)
avg_coefs <- coef(model_avg)
avg_confint <- confint(model_avg)
avg_se <- sqrt(diag(vcov(model_avg)))

# Convert the coefficients into a tidy data frame
coefs_df <- as.data.frame(avg_coefs)
colnames(coefs_df) <- "Avg_Coef"
coefs_df$CI_Lower <- avg_confint[, 1]  # Add lower bound of confidence intervals
coefs_df$CI_Upper <- avg_confint[, 2] # Add upper bound of confidence intervals
coefs_df$SE <- avg_se
print(coefs_df) #Model Averaging Coefficients for AIC model selection approach with body size as response variable

write.csv(coefs_df, file = "eggsize_runtiminggroup/eggsize~runtiminggroup_models_CoefEstimates.csv", row.names = TRUE)
```


### Parameter Likelihoods
```{r}
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12, model13, model14, model15, model16, model17, model18, model19, model20, model21)

# Assign model names
model_names <- paste0("Model_", seq_along(models))

# Compute AICc and model weights
aic_table <- aictab(cand.set = models, modnames = model_names)
weights <- aic_table$AICcWt  # Extract AICc weights

# Extract model coefficients
param_names <- unique(unlist(sapply(models, function(m) names(coef(m)))))

# Compute parameter likelihoods
param_likelihoods <- sapply(param_names, function(param) {
  # Identify models that include this parameter
  models_with_param <- sapply(models, function(m) param %in% names(coef(m)))
  
  # Sum AICc weights for models that include this parameter
  sum(weights[models_with_param])
})

# Format output as a data frame
param_likelihoods_df <- data.frame(Parameter = param_names, WeightedLikelihood = param_likelihoods)

# Make sure that coefs_df has a column with the parameter names
coefs_df$Parameter <- rownames(coefs_df)  # Add the parameter names to the dataframe
coefs_df <- coefs_df[, c("Parameter", "Avg_Coef", "CI_Lower", "CI_Upper", "SE")]


# Now, we will merge coefs_df with param_likelihoods_df by 'Parameter' to add the likelihoods
coefs_df <- merge(coefs_df, param_likelihoods_df, by = "Parameter", all.x = TRUE)

# Print the updated dataframe to see the result
print(coefs_df)

colnames(coefs_df)[colnames(coefs_df) == "WeightedLikelihood"] <- "ParamLikelihood"

coefs_df <- coefs_df %>%
  arrange(desc(ParamLikelihood)) #arrange dataframe in descending order according to ParamLikelihoods

# Optionally, write the results to a CSV file
write.csv(coefs_df, file = "eggsize_runtiminggroup/eggsize~runtiminggroup_models_CoefEstimates_withLikelihoods.csv", row.names = TRUE)


```

### Figure that displays parameter estimates + CI for each parameter in the model set
```{r}
paramestimates_eggsize <- "eggsize_runtiminggroup/eggsize~runtiminggroup_models_CoefEstimates.csv"

paramestimates_eggsize<-read.csv(paramestimates_eggsize)
str(paramestimates_eggsize)

levels(factor(paramestimates_eggsize$X))
paramestimates_eggsize$X <- factor(paramestimates_eggsize$X, 
                           levels = rev(factor(paramestimates_eggsize$X)))


library(ggplot2)
ggplot(paramestimates_eggsize, aes(x = Avg_Coef, y = X)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

library(dplyr)
paramestimates_eggsize_filtered <- paramestimates_eggsize %>%
  filter(X != "Collection_RiverMile_m")

eggsize_plot <- ggplot(paramestimates_eggsize_filtered, aes(x = Avg_Coef, y = X)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

ggsave("eggsize_runtiminggroup/eggsize_ParamEstimates_Plot.png", plot=eggsize_plot, height=12, width=12, units="in")


```

## Visualizing top selected model, Model 17

```{r}
DataSetF$RunTimingGroup <- factor(DataSetF$RunTimingGroup, 
                                    levels = c("Early", 
                                               "Middle", 
                                               "Late"))

library(ggplot2)
ggplot(DataSetF, aes(x = RunTimingGroup, y = Fem_Egg_Sz_1)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Fem_Egg_Sz_1 by RunTimingGroup", x = "RunTimingGroup", y = "Fem_Egg_Sz_1")

#Plot of linear relationship between body size and egg size, across run timing group
ggplot(DataSetF, aes(x = bodysize_pc, y = Fem_Egg_Sz_1)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  facet_wrap(~ RunTimingGroup) +
  theme_minimal() +
  labs(title = "Fem_Egg_Sz_1 by bodysize_pc and RunTimingGroup", x = "bodysize_pc", y = "Fem_Egg_Sz_1")

#Plot of linear relationship between energy content and egg size, across run timing group
ggplot(DataSetF, aes(x = EnergyPDry_1, y = Fem_Egg_Sz_1)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  facet_wrap(~ RunTimingGroup) +
  theme_minimal() +
  labs(title = "Fem_Egg_Sz_1 by energy content and RunTimingGroup", x = "Energy Content", y = "Fem_Egg_Sz_1")

```

