---
title: "AH_AICc_energydensity~RTG"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for EnergyDensity~RunTimingGroup models
#' =====================================================

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)

#data loading
bc19 <- read.csv("bodycomp_2019.csv")
bc20 <- read.csv("bodycomp_2020.csv")
bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, lower river only

bc_LR_total <- rbind(bc19[1:60,], bc20[1:60,], bc21[1:60,])
write.csv(bc_LR_total, "lowerriver_bodycomp_all.csv")
lowerriver_bodycomp_all<-read.csv("lowerriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
lowerriver_bodycomp_all$Collection_Date <- as.Date(lowerriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
lowerriver_bodycomp_all$Year <- year(lowerriver_bodycomp_all$Collection_Date)

#replace blank cell in Sex with NA 
lowerriver_bodycomp_all$Sex[lowerriver_bodycomp_all$Sex == ""] <- NA
str(lowerriver_bodycomp_all)

write.csv(lowerriver_bodycomp_all, "lowerriver_bodycomp_all.csv")
```


### Import Data for models, check for NAs and eliminate as needed
```{r}
rm(list = ls())
lowerriver_bodycomp_all<- "lowerriver_bodycomp_all.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_all)[,-1]

### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$RunTimingGroup))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))
DataSet[is.na(DataSet$Sex), ] #row 115 has no sex value, eliminate it for models
DataSet <- DataSet[-115,] #excludes row missing sex file
any(is.na(DataSet$Sex))

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location) 
DataSet$RunTimingGroup <- as.factor(DataSet$RunTimingGroup)
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)

```

### Making Models for bodysize_pc~RunTimingGroup
```{r}
# Models for reference
energydensity_RTG_modelset <- "energydensity_runtiminggroup/energydensity~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(energydensity_RTG_modelset)

#models
edModel1 <- lm(EnergyDensity_mJ.kg_1 ~ 1, data = DataSet)
 # not using anymore: edModel2 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_Location, data = DataSet)
edModel2 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup, data = DataSet)
edModel3 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + Sex, data = DataSet)
edModel4 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + Year, data = DataSet)
edModel5 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex, data = DataSet)
edModel6 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Year, data = DataSet)
edModel7 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + Sex + Year, data = DataSet)
edModel8 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex, data = DataSet)
# not using anymore: edModel10 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Year + RunTimingGroup:Year, data = DataSet)
edModel9 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + Sex + Year + Sex:Year, data = DataSet)
edModel10 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex + Year, data = DataSet)
```

### AICc Model Selection
```{r}
AIC(edModel1, edModel2, edModel3, edModel4, edModel5, edModel6, edModel7, edModel8, edModel9, edModel10)

edModels <- list(edModel1, edModel2, edModel3, edModel4, edModel5, edModel6, edModel7, edModel8, edModel9, edModel10)

# Generate AIC table
mynames_ed <- paste("model", as.character(1:10), sep = "")
ed_aicc <- aictab(edModels, modnames = mynames_ed)
print(ed_aicc) #so model 2 is preferred (lowest AIC score) followed by model 6 and then model 5

# Convert AIC table to a data frame for easier manipulation
EDaic_df <- as.data.frame(ed_aicc)
EDaic_df$ModelName <- c("EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup",
                      "EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Year",
                      "EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex",
                      "EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex + Year",
                      "EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex",
                      "EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + Year",
                      "EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + Sex + Year",
                      "EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + Sex + Year + Sex:Year",
                      "EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + Sex",
                      "EnergyDensity_mJ.kg_1 ~ 1")
colnames(EDaic_df)[colnames(EDaic_df) == "Modnames"] <- "Model #"

write.csv(EDaic_df, file = "energydensity_runtiminggroup/AICresults_EnergyDensity~RunTimingGroup.csv", row.names = FALSE)

```

### Model Averaging
```{r}
library(MuMIn)

 # Create a model selection table (this will give you AIC, AIC weights, etc.)
model_weights <- ed_aicc$AICcWt ##Get the AIC weights from the AIC table
model_avg <- model.avg(edModels, weights = model_weights)
summary(model_avg)
avg_coefs <- coef(model_avg)
avg_confint <- confint(model_avg)
avg_se <- sqrt(diag(vcov(model_avg)))

# Convert the coefficients into a tidy data frame
coefs_df <- as.data.frame(avg_coefs)
colnames(coefs_df) <- "Avg_Coef"
coefs_df$CI_Lower <- avg_confint[, 1]  # Add lower bound of confidence intervals
coefs_df$CI_Upper <- avg_confint[, 2] # Add upper bound of confidence intervals
coefs_df$SE <- avg_se
print(coefs_df) #Model Averaging Coefficients for AIC model selection approach with body size as response variable

write.csv(coefs_df, file = "energydensity_runtiminggroup/energydensity~runtiminggroup_models_CoefEstimates.csv", row.names = TRUE)
```




#' =====================================================
#' AICc code for EnergyPDry_1~RunTimingGroup models
#' =====================================================

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)

#data loading
bc19 <- read.csv("bodycomp_2019.csv")
bc20 <- read.csv("bodycomp_2020.csv")
bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, lower river only

bc_LR_total <- rbind(bc19[1:60,], bc20[1:60,], bc21[1:60,])
write.csv(bc_LR_total, "lowerriver_bodycomp_all.csv")
lowerriver_bodycomp_all<-read.csv("lowerriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
lowerriver_bodycomp_all$Collection_Date <- as.Date(lowerriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
lowerriver_bodycomp_all$Year <- year(lowerriver_bodycomp_all$Collection_Date)

#replace blank cell in Sex with NA 
lowerriver_bodycomp_all$Sex[lowerriver_bodycomp_all$Sex == ""] <- NA
str(lowerriver_bodycomp_all)

write.csv(lowerriver_bodycomp_all, "lowerriver_bodycomp_all.csv")
```


### Import Data for models, check for NAs and eliminate as needed
```{r}
rm(list = ls())
lowerriver_bodycomp_all<- "lowerriver_bodycomp_all.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_all)[,-1]

### Removing NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$RunTimingGroup))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))
DataSet[is.na(DataSet$Sex), ] #row 115 has no sex value, eliminate it for models
DataSet <- DataSet[-115,] #excludes row missing sex file
any(is.na(DataSet$Sex))

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location) 
DataSet$RunTimingGroup <- as.factor(DataSet$RunTimingGroup)
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)

```

### Making Models for bodysize_pc~RunTimingGroup
```{r}
# Models for reference
EnergyPDry_RTG_modelset <- "energydensity_runtiminggroup/EnergyPDry_1~RunTimingGroup_modelset.csv"

ModelSet<-read.csv(EnergyPDry_RTG_modelset)

#models
edModel1 <- lm(EnergyPDry_1 ~ 1, data = DataSet)
 # not using anymore: edModel2 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_Location, data = DataSet)
edModel2 <- lm(EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup, data = DataSet)
edModel3 <- lm(EnergyPDry_1 ~ Collection_RiverMile_m + Sex, data = DataSet)
edModel4 <- lm(EnergyPDry_1 ~ Collection_RiverMile_m + Year, data = DataSet)
edModel5 <- lm(EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex, data = DataSet)
edModel6 <- lm(EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup + Year, data = DataSet)
edModel7 <- lm(EnergyPDry_1 ~ Collection_RiverMile_m + Sex + Year, data = DataSet)
edModel8 <- lm(EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex, data = DataSet)
# not using anymore: edModel10 <- lm(EnergyDensity_mJ.kg_1 ~ Collection_RiverMile_m + RunTimingGroup + Year + RunTimingGroup:Year, data = DataSet)
edModel9 <- lm(EnergyPDry_1 ~ Collection_RiverMile_m + Sex + Year + Sex:Year, data = DataSet)
edModel10 <- lm(EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex + Year, data = DataSet)
```


### AICc Model Selection
```{r}
AIC(edModel1, edModel2, edModel3, edModel4, edModel5, edModel6, edModel7, edModel8, edModel9, edModel10)

edModels <- list(edModel1, edModel2, edModel3, edModel4, edModel5, edModel6, edModel7, edModel8, edModel9, edModel10)

# Generate AIC table
mynames_ed <- paste("model", as.character(1:10), sep = "")
ed_aicc <- aictab(edModels, modnames = mynames_ed)
print(ed_aicc) #so model 6 is preferred followed by the global model and then model 2

# Convert AIC table to a data frame for easier manipulation
EDaic_df <- as.data.frame(ed_aicc)
EDaic_df$ModelName <- c("EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup + Year",
                        "EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex + Year",
                        "EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup",
                        "EnergyPDry_1 ~ Collection_RiverMile_m + Year",
                        "EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex",
                        "EnergyPDry_1 ~ Collection_RiverMile_m + Sex + Year",
                        "EnergyPDry_1 ~ Collection_RiverMile_m + Sex + Year + Sex:Year",
                        "EnergyPDry_1 ~ Collection_RiverMile_m + RunTimingGroup + Sex + RunTimingGroup:Sex",
                        "EnergyPDry_1 ~ Collection_RiverMile_m + Sex",
                        "EnergyPDry_1 ~ 1")
colnames(EDaic_df)[colnames(EDaic_df) == "Modnames"] <- "Model #"

write.csv(EDaic_df, file = "energydensity_runtiminggroup/AICresults_EnergyPDry_1~RunTimingGroup.csv", row.names = FALSE)

```

### Model Averaging
```{r}
library(MuMIn)

 # Create a model selection table (this will give you AIC, AIC weights, etc.)
model_weights <- ed_aicc$AICcWt ##Get the AIC weights from the AIC table
model_avg <- model.avg(edModels, weights = model_weights)
summary(model_avg)
avg_coefs <- coef(model_avg)
avg_confint <- confint(model_avg)
avg_se <- sqrt(diag(vcov(model_avg)))

# Convert the coefficients into a tidy data frame
coefs_df <- as.data.frame(avg_coefs)
colnames(coefs_df) <- "Avg_Coef"
coefs_df$CI_Lower <- avg_confint[, 1]  # Add lower bound of confidence intervals
coefs_df$CI_Upper <- avg_confint[, 2] # Add upper bound of confidence intervals
coefs_df$SE <- avg_se
print(coefs_df) #Model Averaging Coefficients for AIC model selection approach with body size as response variable

write.csv(coefs_df, file = "energydensity_runtiminggroup/EnergyPDry_1~runtiminggroup_models_CoefEstimates.csv", row.names = TRUE)
```

