---
title: "AH_AICc_totalenergy~SP"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading
# bc19 <- read.csv("bodycomp_2019.csv")
# bc20 <- read.csv("bodycomp_2020.csv")
# bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, Upper River river only

# bc_UR_total <- rbind(bc19[61:172,], bc20[61:120,], bc21[61:182,])
# write.csv(bc_UR_total, "upperriver_bodycomp_all.csv")
upperriver_bodycomp_all<-read.csv("upperriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
str(upperriver_bodycomp_all)
upperriver_bodycomp_all$Collection_Date <- as.Date(upperriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
upperriver_bodycomp_all$Year <- year(upperriver_bodycomp_all$Collection_Date)
str(upperriver_bodycomp_all)

#replace blank cell in Sex with NA 
upperriver_bodycomp_all$Sex[upperriver_bodycomp_all$Sex == ""] <- NA
str(upperriver_bodycomp_all)

write.csv(upperriver_bodycomp_all, "upperriver_bodycomp_all.csv")
```

### Add Total Energy as a Variable
```{r}
# Total energy = PDry_1 * Fish_Wt == mJ energy
upperriver_bodycomp_all$EnergyPDry_1_mJ_g <- upperriver_bodycomp_all$EnergyPDry_1 / 1000
upperriver_bodycomp_all$Fish_Wt_g <- upperriver_bodycomp_all$Fish_Wt * 1000
upperriver_bodycomp_all$TotalEnergy_mJ <- upperriver_bodycomp_all$EnergyPDry_1_mJ_g * upperriver_bodycomp_all$Fish_Wt_g
str(upperriver_bodycomp_all)

write.csv(upperriver_bodycomp_all, "upperriver_bodycomp_TotalEnergy.csv")
```


### Import Data for models, check for NAs and eliminate as needed

```{r, include = FALSE}
rm(list = ls())
upperriver_bodycomp_TotalEnergy <- "upperriver_bodycomp_TotalEnergy.csv"
DataSet<-read.csv(upperriver_bodycomp_TotalEnergy)[,-1]

##### For the Upper River Data, I want to elimiate Power Creek Cordova, Eyak Weir Cordova, Bone Creek, Klutina River, and Upper Klutina, and Copper Lake data points as they don't apply to my spawning populations of interest ####
library(dplyr)

# Use filter() to exclude the specific collection locations
DataSet <- DataSet %>%
  filter(!Collection_Location %in% c("Power Creek Cordova", "Eyak Weir Cordova", "Bone Creek", "Copper Lake", "Klutina River", "Upper Klutina"))

#convert gonad_wt to grams from kilograms
DataSet$Gonad_Wt_g <- DataSet$Gonad_Wt * 1000

### Now, need to remove NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))
DataSet[is.na(DataSet$Sex), ] #row 87 and 110 has no sex value, eliminate it for models
#check gonad weight for NAs
any(is.na(DataSet$Gonad_Wt_g))
DataSet[is.na(DataSet$Gonad_Wt_g), ] #need to eliminate these rows or model selection will not work
DataSet[is.na(DataSet$TotalEnergy_mJ), ] #Row 35 does not have a Total Energy value, so eliminate for analysis
DataSet <- DataSet[-c(18,35,36,40,61,65,77,87,102,110,118,141,142,144,161,164,221, 222,224),] #excludes row missing sex file
any(is.na(DataSet$Sex)) #FALSE
any(is.na(DataSet$Gonad_Wt_g)) #FALSE
any(is.na(DataSet$TotalEnergy_mJ))



# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet) #220 observations and 82 variables

#Make work metric (migratory difficulty metric where work = F x distance)
DataSet$Elevation_m <- as.numeric(DataSet$Elevation_m)
DataSet$Work <- round((DataSet$Collection_RiverMile_m * DataSet$Elevation_m) / (1000 * 1000), digits = 1) #in km^2
str(DataSet) 



#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
levels(DataSet$Collection_Location) # 7 unique locations
DataSet$Year<- as.factor(DataSet$Year)
levels(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)


```

### Making Models for TotalEnergy_mJ~SpawningPopulation, includes SpawnStatus
```{r}
# Models for reference
totalenergy_SP_modelset <- "totalenergy_spawningpopulation/TotalEnergy~SP_modelset.csv"

ModelSet<-read.csv(totalenergy_SP_modelset)

model1 <- lm(TotalEnergy_mJ~1, data=DataSet)
model2 <- lm(TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location, data = DataSet)
model3 <- lm(TotalEnergy_mJ~ Gonad_Wt_g + Sex, data = DataSet)
model4 <- lm(TotalEnergy_mJ~Gonad_Wt_g + Year, data = DataSet)
model5 <- lm(TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location + Sex, data = DataSet)
model6 <- lm(TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location + Year, data = DataSet)
model7 <- lm(TotalEnergy_mJ~ Gonad_Wt_g + Sex + Year, data = DataSet)
model8 <- lm(TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location + Sex + Collection_Location:Sex, data = DataSet)
model9 <- lm(TotalEnergy_mJ~Gonad_Wt_g + Sex + Year + Sex:Year, data = DataSet)
model10 <- lm(TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location + Sex + Year, data = DataSet)
```

### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

teModels <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

# Generate AIC table
mynames_te <- paste("model", as.character(1:10), sep = "")
te_aicc <- aictab(teModels, modnames = mynames_te)
print(te_aicc) 

# Convert AIC table to a data frame for easier manipulation
TEaic_df <- as.data.frame(te_aicc)
TEaic_df$ModelName <- c("TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location + Sex + Year",
                        "TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location + Sex",
                        "TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location + Sex + Collection_Location:Sex",
                        "TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location + Year",
                        "TotalEnergy_mJ~ Gonad_Wt_g + Collection_Location",
                        "TotalEnergy_mJ~ Gonad_Wt_g + Sex + Year",
                        "TotalEnergy_mJ~Gonad_Wt_g + Sex + Year + Sex:Year",
                        "TotalEnergy_mJ~ Gonad_Wt_g + Sex",
                        "TotalEnergy_mJ~Gonad_Wt_g + Year",
                        "TotalEnergy_mJ~1")
colnames(TEaic_df)[colnames(TEaic_df) == "Modnames"] <- "Model #"

write.csv(TEaic_df, file = "totalenergy_spawningpopulation/AICresults_TotalEnergy~SpawningPopulation.csv", row.names = FALSE)

```

### Model Averaging and Parameter Likelihoods
```{r}
library(MuMIn)

# List your models (already fit with na.action=na.fail)
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10)

# Model averaging based on AICc, conditional averaging (default is full=TRUE)
model_avg <- model.avg(models, rank = "AICc", full = TRUE)

# Summary with coefficients, SE, CIs
summary(model_avg)

# Full averaged coefficients
avg_coefs_full <- coef(model_avg, full = TRUE)

# Full averaged confidence intervals
avg_confint_full <- confint(model_avg, full = TRUE)

# Full averaged variance-covariance matrix and SE
avg_vcov_full <- vcov(model_avg, full = TRUE)
avg_se_full <- sqrt(diag(avg_vcov_full))

# Create tidy data frame with full averages
coefs_df_full <- as.data.frame(avg_coefs_full)
colnames(coefs_df_full) <- "Avg_Coef"
coefs_df_full$CI_Lower <- avg_confint_full[, 1]
coefs_df_full$CI_Upper <- avg_confint_full[, 2]
coefs_df_full$SE <- avg_se_full

# Calculate parameter importance (parameter likelihoods)
param_likelihoods <- sw(model_avg)
as.data.frame(param_likelihoods)

# Manually specify parameter likelihoods from sw(model_avg)
manual_likelihoods <- c(
  "(Intercept)" = 1.0,
  "Gonad_Wt_g" = 1.000000,
  "Collection_LocationGulkana Hatchery" = 1.0000, 
  "Collection_LocationLong Lake" = 1.0000,
  "Collection_LocationMahlo" = 1.0000,
  "Collection_LocationMentasta" = 1.0000,
  "Collection_LocationSt Anne" = 1.0000,
  "Collection_LocationTanada" = 1.0000,
  "Year2020" = 0.9872105,
  "Year2021" = 0.9872105, 
  "SexM" = 0.9999564,
  "SexM:Year2020" = 1.541287e-10,
  "SexM:Year2021" = 1.541287e-10,
  "Collection_LocationGulkana Hatchery:SexM" = 8.631624e-05,
  "Collection_LocationLong Lake:SexM" = 8.631624e-05,
  "Collection_LocationMahlo:SexM" = 8.631624e-05,
  "Collection_LocationMentasta:SexM" = 8.631624e-05,
  "Collection_LocationSt Anne:SexM" = 8.631624e-05,
  "Collection_LocationTanada:SexM" = 8.631624e-05
)



# Add ParamLikelihoods by matching rownames
coefs_df_full$ParamLikelihood <- manual_likelihoods[rownames(coefs_df_full)]

# View final table
print(coefs_df_full)

write.csv(coefs_df_full, file = "totalenergy_spawningpopulation/TotalEnergy_SP_ModelAvg_Coefs_withLikelihoods.csv", row.names = TRUE)

```


### Using summed weighted parameter estimates for total energy by CL ~ work (successful size for migration, as continuous variable)
```{r}
# Step 1: Extract intercept
intercept <- coefs_df_full["(Intercept)", "Avg_Coef"]

# Step 2: Extract Collection_Location effects
location_effects <- coefs_df_full[grep("^Collection_Location", rownames(coefs_df_full)), ]
location_effects <- location_effects[!grepl(":", rownames(location_effects)), ]  # remove interaction terms

# Extract location names (remove "Collection_Location" from row names)
location_effects$Location <- gsub("Collection_Location", "", rownames(location_effects))

# Step 3: Add intercept to each to get estimated body size
location_effects$Estimated_TotalEnergy <- intercept + location_effects$Avg_Coef

# Step 4: Add back the reference location (intercept only)
ref_location <- levels(DataSet$Collection_Location)[1]  # Assumes first level is the reference
ref_row <- data.frame(
  Avg_Coef = intercept,
  CI_Lower = coefs_df_full["(Intercept)", "CI_Lower"],
  CI_Upper = coefs_df_full["(Intercept)", "CI_Upper"],
  SE = coefs_df_full["(Intercept)", "SE"],
  ParamLikelihood = coefs_df_full["(Intercept)", "ParamLikelihood"],
  Location = ref_location,
  Estimated_TotalEnergy = intercept
)

# Step 5: Combine
location_estimates <- rbind(ref_row, location_effects)
rownames(location_estimates) <- NULL
location_estimates <- location_estimates[, c("Location", setdiff(names(location_estimates), "Location"))]

# Step 6: Compute average Work per location
library(dplyr)
avg_work <- DataSet %>%
  dplyr::group_by(Collection_Location) %>%
  dplyr::summarise(Avg_Work = mean(Work, na.rm = TRUE), .groups = "drop")

# Step 7: Merge with estimates
location_estimates <- merge(location_estimates, avg_work, by.x = "Location", by.y = "Collection_Location")

# Step 8: Linear regression of estimated body size ~ work
te_work_model <- lm(Estimated_TotalEnergy ~ Avg_Work, data = location_estimates)
summary(te_work_model)

# Step 9: Visualization
library(ggplot2)
ggplot(location_estimates, aes(x = Avg_Work, y = Estimated_TotalEnergy, label = Location)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  geom_text(nudge_y = 0.1, size = 3) +
  labs(title = "Model-Averaged Estimated Total Energy vs. Migration Work",
       x = "Migration Work (km²)", y = "Estimated Total Energy (mJ)") +
  theme_minimal() + 
   theme(
  plot.title = element_text(size = 16, face = "bold"),
  axis.title.x = element_text(size = 16, face = "bold"),
  axis.title.y = element_text(size = 16, face = "bold"),
  axis.text.x = element_text(size = 16),
  axis.text.y = element_text(size = 16),
  legend.title = element_text(size = 16, face = "bold"),
  legend.text = element_text(size = 16)
)


#Remove Long Lake from the dataset
location_estimates_noLL <- location_estimates %>%
  filter(!Location %in% c("Long Lake"))

te_work_model2 <- lm(Estimated_TotalEnergy ~ Avg_Work, data = location_estimates_noLL)
summary(te_work_model2)

ggplot(location_estimates_noLL, aes(x = Avg_Work, y = Estimated_TotalEnergy, label = Location)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  geom_text(nudge_y = 0.1, size = 3) +
  labs(title = "Model-Averaged Estimated Total Energy vs. Migration Work",
       x = "Migration Work (km²)", y = "Estimated Total Energy (mJ)") +
  theme_minimal() +
  theme(
  plot.title = element_text(size = 16, face = "bold"),
  axis.title.x = element_text(size = 16, face = "bold"),
  axis.title.y = element_text(size = 16, face = "bold"),
  axis.text.x = element_text(size = 16),
  axis.text.y = element_text(size = 16),
  legend.title = element_text(size = 16, face = "bold"),
  legend.text = element_text(size = 16)
)
  




```

### Calculating actual parameter estimates according to intercept
```{r}
coefs_df_full$Actual_Param <- with(coefs_df_full, 
                                   Avg_Coef + coefs_df_full["(Intercept)", "Avg_Coef"])
coefs_df_full["(Intercept)", "Actual_Param"] <- coefs_df_full["(Intercept)", "Avg_Coef"]
```