---
title: "AH_AICc_bodysize~SP"
author: "Abby Host"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

#' =====================================================
#' AICc code for BodySizePC_1~SpawningPopulation models
#' =====================================================

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading
bc19 <- read.csv("bodycomp_2019.csv")
bc20 <- read.csv("bodycomp_2020.csv")
bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, Upper River river only

bc_UR_total <- rbind(bc19[61:172,], bc20[61:120,], bc21[61:180,])
write.csv(bc_UR_total, "upperriver_bodycomp_all.csv")
upperriver_bodycomp_all<-read.csv("upperriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
str(upperriver_bodycomp_all)
upperriver_bodycomp_all$Collection_Date <- as.Date(upperriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
upperriver_bodycomp_all$Year <- year(upperriver_bodycomp_all$Collection_Date)
str(upperriver_bodycomp_all)

#replace blank cell in Sex with NA 
upperriver_bodycomp_all$Sex[upperriver_bodycomp_all$Sex == ""] <- NA
str(upperriver_bodycomp_all)

write.csv(upperriver_bodycomp_all, "upperriver_bodycomp_all.csv")
```

### Checking for NAs for PC score 
```{r}
rm(list = ls())
upperriver_bodycomp_all <- "upperriver_bodycomp_all.csv"
upperriver_bodycomp_all<-read.csv("upperriver_bodycomp_all.csv")[,-1]

##### For the Upper River Data, I want to elimiate Power Creek Cordova, Eyak Weir Cordova, Bone Creek, and Copper Lake data points as they don't apply to my spawning populations of interest ####
library(dplyr)

# Assuming your data frame is named df, use filter() to exclude the specific collection locations
upperriver_bodycomp_all <- upperriver_bodycomp_all %>%
  filter(!Collection_Location %in% c("Power Creek Cordova", "Eyak Weir Cordova", "Bone Creek"))


### Now, need to remove NAs that will mess up levels / model weight
any(is.na(upperriver_bodycomp_all$Collection_Location))
any(is.na(upperriver_bodycomp_all$Collection_Region))
any(is.na(upperriver_bodycomp_all$Year))
any(is.na(upperriver_bodycomp_all$Sex))
upperriver_bodycomp_all[is.na(upperriver_bodycomp_all$Sex), ] #row 129 and 152 has no sex value, eliminate it for models
upperriver_bodycomp_all <- upperriver_bodycomp_all[-c(88,111),] #excludes row missing sex file
any(is.na(upperriver_bodycomp_all$Sex))

#checking NA
any(is.na(upperriver_bodycomp_all$Fish_Leng_1))
upperriver_bodycomp_all[is.na(upperriver_bodycomp_all$Fish_Leng_1), ]
any(is.na(upperriver_bodycomp_all$Fish_Leng_2))
upperriver_bodycomp_all[is.na(upperriver_bodycomp_all$Fish_Leng_2), ]
any(is.na(upperriver_bodycomp_all$Fish_Ht))
upperriver_bodycomp_all[is.na(upperriver_bodycomp_all$Fish_Ht), ]
any(is.na(upperriver_bodycomp_all$Fish_Grth)) 
upperriver_bodycomp_all[is.na(upperriver_bodycomp_all$Fish_Grth), ] 
any(is.na(upperriver_bodycomp_all$Fish_Wdth)) 
upperriver_bodycomp_all[is.na(upperriver_bodycomp_all$Fish_Wdth), ] 
## NAs present in each of these variables, will need to estimate for values before PC score can be run to quantify body size of these samples
```


### Estimate length_1 Values for NA rows
```{r}
#Determine best metric for estimating NAs for Leng_1
summary(lm(Fish_Leng_1 ~ Fish_Leng_2, data = upperriver_bodycomp_all)) #R = 0.06
summary(lm(Fish_Leng_1 ~ Fish_Ht, data = upperriver_bodycomp_all)) #R = 0.3118
summary(lm(Fish_Leng_1 ~ Fish_Wt, data = upperriver_bodycomp_all)) #R = 0.6648
summary(lm(Fish_Leng_1 ~ Fish_Grth, data = upperriver_bodycomp_all)) # Adjusted R-squared:  0.4019


# Subset the data for female F fish only
allF_upperriver_bodycomp_all <- upperriver_bodycomp_all[upperriver_bodycomp_all$Sex == "F", ]

summary(lm(Fish_Leng_1 ~ Fish_Grth, data = allF_upperriver_bodycomp_all))
leng1_F_lm <- lm(Fish_Leng_1 ~ Fish_Wt, data = allF_upperriver_bodycomp_all)
summary(leng1_F_lm) # R squared  0.3204 
plot(leng1_F_lm)


predicted_values_lengF <- predict(leng1_F_lm, newdata = allF_upperriver_bodycomp_all)

allF_upperriver_bodycomp_all$Predicted_Fish_Leng_1 <- predicted_values_lengF # Add these predictions back to your dataset


ggplot(allF_upperriver_bodycomp_all, aes(x = Predicted_Fish_Leng_1, y = Fish_Leng_1)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Leng_1, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Female Fish",
       x = "Predicted Fish Length",
       y = "Fish Length") +
  theme_minimal() 

# Replace NAs in Fish_Leng_1 with predicted values
allF_upperriver_bodycomp_all$Fish_Leng_1[is.na(allF_upperriver_bodycomp_all$Fish_Leng_1)] <- allF_upperriver_bodycomp_all$Predicted_Fish_Leng_1[is.na(allF_upperriver_bodycomp_all$Fish_Leng_1)]
## so now, the female subset has predicted values replacing the NAs for Leng_1


#Now, same for the male data
allM_upperriver_bodycomp_all <- upperriver_bodycomp_all[upperriver_bodycomp_all$Sex == "M", ] #subset of M from total data set

leng1_M_lm <- lm(Fish_Leng_1 ~ Fish_Wt, data = allM_upperriver_bodycomp_all) #making linear regression
summary(leng1_M_lm) # R squared is 0.6244 
plot(leng1_M_lm)
predicted_values_lengM <- predict(leng1_M_lm, newdata = allM_upperriver_bodycomp_all) #predicting width values from male subset data
allM_upperriver_bodycomp_all$Predicted_Fish_Leng_1 <- predicted_values_lengM

ggplot(allM_upperriver_bodycomp_all, aes(x = Predicted_Fish_Leng_1, y = Fish_Leng_1)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Leng_1, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Male Fish Length 1",
       x = "Comparison PC",
       y = "Fish Growth") +
  theme_minimal() 

# Replace NAs in Fish_Leng_1 with predicted values
allM_upperriver_bodycomp_all$Fish_Leng_1[is.na(allM_upperriver_bodycomp_all$Fish_Leng_1)] <- allM_upperriver_bodycomp_all$Predicted_Fish_Leng_1[is.na(allM_upperriver_bodycomp_all$Fish_Leng_1)]
## so now, the male subset has predicted values replacing the NAs 

### Now, combine the two data sets back into one, called lowerriver_bodycomp_all ###
upperriver_bodycomp_all <- rbind(allF_upperriver_bodycomp_all, allM_upperriver_bodycomp_all)

#Check Leng_1 NAs
any(is.na(upperriver_bodycomp_all$Fish_Leng_1)) #FALSE
```


### Estimate Girth Values for NA rows
```{r}
#Determine best metric for estimating NAs for Girth
summary(lm(Fish_Grth ~ Fish_Leng_1, data = upperriver_bodycomp_all)) # R = 0.3945 
summary(lm(Fish_Grth ~ Fish_Ht, data = upperriver_bodycomp_all)) #R = 0.8015 
summary(lm(Fish_Grth ~ Fish_Wt, data = upperriver_bodycomp_all)) #R = 0.7929 
summary(lm(Fish_Grth ~ Fish_Leng_2, data = upperriver_bodycomp_all)) # Adjusted R-squared = 0.09902 

# Subset the data for female F fish only
allF_upperriver_bodycomp_all <- upperriver_bodycomp_all[upperriver_bodycomp_all$Sex == "F", ]

summary(lm(Fish_Grth ~ Fish_Ht, data = allF_upperriver_bodycomp_all)) #R = 0.6379 
summary(lm(Fish_Grth ~ Fish_Wt, data = allF_upperriver_bodycomp_all)) #R =  0.6993 

grth_F_lm <- lm(Fish_Grth ~ Fish_Wt, data = allF_upperriver_bodycomp_all)
summary(grth_F_lm) # R squared  0.7 
plot(grth_F_lm)


predicted_values_grthF <- predict(grth_F_lm, newdata = allF_upperriver_bodycomp_all)

allF_upperriver_bodycomp_all$Predicted_Fish_Grth <- predicted_values_grthF # Add these predictions back to your dataset


ggplot(allF_upperriver_bodycomp_all, aes(x = Predicted_Fish_Grth, y = Fish_Grth)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Grth, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Female Fish",
       x = "Predicted Fish Girth",
       y = "Fish Girth") +
  theme_minimal() 

# Replace NAs in Fish_Grth with predicted values
allF_upperriver_bodycomp_all$Fish_Grth[is.na(allF_upperriver_bodycomp_all$Fish_Grth)] <- allF_upperriver_bodycomp_all$Predicted_Fish_Grth[is.na(allF_upperriver_bodycomp_all$Fish_Grth)]
## so now, the female subset has predicted values replacing the NAs for Grth


#Now, same for the male data
allM_upperriver_bodycomp_all <- upperriver_bodycomp_all[upperriver_bodycomp_all$Sex == "M", ] #subset of M from total data set

grth_M_lm <- lm(Fish_Grth ~ Fish_Wt, data = allM_upperriver_bodycomp_all) #making linear regression
summary(grth_M_lm) # R squared is 0.669
plot(grth_M_lm)
predicted_values_grthM <- predict(grth_M_lm, newdata = allM_upperriver_bodycomp_all) #predicting width values from male subset data
allM_upperriver_bodycomp_all$Predicted_Fish_Grth <- predicted_values_grthM

ggplot(allM_upperriver_bodycomp_all, aes(x = Predicted_Fish_Grth, y = Fish_Grth)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Grth, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Male Fish Girth",
       x = "Predicted Fish Girth",
       y = "Fish Girth") +
  theme_minimal() 

# Replace NAs in Fish_Wdth with predicted values
allM_upperriver_bodycomp_all$Fish_Grth[is.na(allM_upperriver_bodycomp_all$Fish_Grth)] <- allM_upperriver_bodycomp_all$Predicted_Fish_Grth[is.na(allM_upperriver_bodycomp_all$Fish_Grth)]
## so now, the male subset has predicted values replacing the NAs 

### Now, combine the two data sets back into one, called lowerriver_bodycomp_all ###
upperriver_bodycomp_all <- rbind(allF_upperriver_bodycomp_all, allM_upperriver_bodycomp_all)

#Check Leng_1 NAs
any(is.na(upperriver_bodycomp_all$Fish_Leng_1)) #FALSE
any(is.na(upperriver_bodycomp_all$Fish_Grth)) #FALSE

```

### Estimate Height Values for NA rows
```{r}
#Determine best metric for estimating NAs for Height
summary(lm(Fish_Ht ~ Fish_Leng_1, data = upperriver_bodycomp_all)) # R = 0.3118 
summary(lm(Fish_Ht ~ Fish_Grth, data = upperriver_bodycomp_all)) #R = 0.7962 
summary(lm(Fish_Ht ~ Fish_Wt, data = upperriver_bodycomp_all)) #R = 0.639
summary(lm(Fish_Ht ~ Fish_Leng_2, data = upperriver_bodycomp_all)) # Adjusted R-squared = 0.113 

# Subset the data for female F fish only
allF_upperriver_bodycomp_all <- upperriver_bodycomp_all[upperriver_bodycomp_all$Sex == "F", ]

summary(lm(Fish_Ht ~ Fish_Grth, data = allF_upperriver_bodycomp_all)) #R = 0.6354 


Ht_F_lm <- lm(Fish_Ht ~ Fish_Grth, data = allF_upperriver_bodycomp_all)
summary(Ht_F_lm) # R squared  0.64
plot(Ht_F_lm)


predicted_values_HtF <- predict(Ht_F_lm, newdata = allF_upperriver_bodycomp_all)

allF_upperriver_bodycomp_all$Predicted_Fish_Ht <- predicted_values_HtF # Add these predictions back to your dataset


ggplot(allF_upperriver_bodycomp_all, aes(x = Predicted_Fish_Ht, y = Fish_Ht)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Ht, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Female Fish Height",
       x = "Predicted Fish Height",
       y = "Fish Height") +
  theme_minimal() 

# Replace NAs in Fish_Grth with predicted values
allF_upperriver_bodycomp_all$Fish_Ht[is.na(allF_upperriver_bodycomp_all$Fish_Ht)] <- allF_upperriver_bodycomp_all$Predicted_Fish_Ht[is.na(allF_upperriver_bodycomp_all$Fish_Ht)]
## so now, the female subset has predicted values replacing the NAs for Grth


#Now, same for the male data
allM_upperriver_bodycomp_all <- upperriver_bodycomp_all[upperriver_bodycomp_all$Sex == "M", ] #subset of M from total data set

Ht_M_lm <- lm(Fish_Ht ~ Fish_Grth, data = allM_upperriver_bodycomp_all) #making linear regression
summary(Ht_M_lm) # R squared is 0.7112 
plot(Ht_M_lm)
predicted_values_HtM <- predict(Ht_M_lm, newdata = allM_upperriver_bodycomp_all) #predicting width values from male subset data
allM_upperriver_bodycomp_all$Predicted_Fish_Ht <- predicted_values_HtM

ggplot(allM_upperriver_bodycomp_all, aes(x = Predicted_Fish_Ht, y = Fish_Ht)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Ht, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Male Fish Height",
       x = "Predicted Fish Height",
       y = "Fish Height") +
  theme_minimal() 

# Replace NAs in Fish_Wdth with predicted values
allM_upperriver_bodycomp_all$Fish_Ht[is.na(allM_upperriver_bodycomp_all$Fish_Ht)] <- allM_upperriver_bodycomp_all$Predicted_Fish_Ht[is.na(allM_upperriver_bodycomp_all$Fish_Ht)]
## so now, the male subset has predicted values replacing the NAs 

### Now, combine the two data sets back into one, called lowerriver_bodycomp_all ###
upperriver_bodycomp_all <- rbind(allF_upperriver_bodycomp_all, allM_upperriver_bodycomp_all)

#Check Leng_1 NAs
any(is.na(upperriver_bodycomp_all$Fish_Leng_1)) #FALSE
any(is.na(upperriver_bodycomp_all$Fish_Grth)) #FALSE
any(is.na(upperriver_bodycomp_all$Fish_Ht)) #FALSE

```

### Estimate Width Values for NA rows
```{r}
#Determine best metric for estimating NAs for Wdth

allF_upperriver_bodycomp_all <- upperriver_bodycomp_all[upperriver_bodycomp_all$Sex == "F", ]
summary(lm(Fish_Wdth ~ Fish_Leng_1, data = allF_upperriver_bodycomp_all)) # R = 0.1972 
summary(lm(Fish_Wdth ~ Fish_Grth, data = allF_upperriver_bodycomp_all)) #R = 0.4876
summary(lm(Fish_Wdth ~ Fish_Wt, data = allF_upperriver_bodycomp_all)) #R =  0.5219 
summary(lm(Fish_Wdth ~ Fish_Ht, data = allF_upperriver_bodycomp_all)) # Adjusted R-squared = 0.2658

Wdth_F_lm <- lm(Fish_Wdth ~ Fish_Wt, data = allF_upperriver_bodycomp_all)
summary(Wdth_F_lm) # R squared  0.64
plot(Wdth_F_lm)


predicted_values_WdthF <- predict(Wdth_F_lm, newdata = allF_upperriver_bodycomp_all)

allF_upperriver_bodycomp_all$Predicted_Fish_Wdth <- predicted_values_WdthF # Add these predictions back to your dataset


ggplot(allF_upperriver_bodycomp_all, aes(x = Predicted_Fish_Wdth, y = Fish_Wdth)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Wdth, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Female Fish Width",
       x = "Predicted Fish Width",
       y = "Fish Width") +
  theme_minimal() 

# Replace NAs in Fish_Grth with predicted values
allF_upperriver_bodycomp_all$Fish_Wdth[is.na(allF_upperriver_bodycomp_all$Fish_Wdth)] <- allF_upperriver_bodycomp_all$Predicted_Fish_Wdth[is.na(allF_upperriver_bodycomp_all$Fish_Wdth)]
## so now, the female subset has predicted values replacing the NAs for Grth


#Now, same for the male data
allM_upperriver_bodycomp_all <- upperriver_bodycomp_all[upperriver_bodycomp_all$Sex == "M", ] #subset of M from total data set

Wdth_M_lm <- lm(Fish_Wdth ~ Fish_Wt, data = allM_upperriver_bodycomp_all) #making linear regression
summary(Wdth_M_lm) # R squared is 0.1235
plot(Wdth_M_lm)
predicted_values_WdthM <- predict(Wdth_M_lm, newdata = allM_upperriver_bodycomp_all) #predicting width values from male subset data
allM_upperriver_bodycomp_all$Predicted_Fish_Wdth <- predicted_values_WdthM

ggplot(allM_upperriver_bodycomp_all, aes(x = Predicted_Fish_Wdth, y = Fish_Wdth)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Wdth, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Male Fish Width",
       x = "Predicted Fish Width",
       y = "Fish Width") +
  theme_minimal() 

# Replace NAs in Fish_Wdth with predicted values
allM_upperriver_bodycomp_all$Fish_Wdth[is.na(allM_upperriver_bodycomp_all$Fish_Wdth)] <- allM_upperriver_bodycomp_all$Predicted_Fish_Wdth[is.na(allM_upperriver_bodycomp_all$Fish_Wdth)]
## so now, the male subset has predicted values replacing the NAs 

### Now, combine the two data sets back into one, called lowerriver_bodycomp_all ###
upperriver_bodycomp_all <- rbind(allF_upperriver_bodycomp_all, allM_upperriver_bodycomp_all)

#Check Leng_1 NAs
any(is.na(upperriver_bodycomp_all$Fish_Leng_1)) #FALSE
any(is.na(upperriver_bodycomp_all$Fish_Grth)) #FALSE
any(is.na(upperriver_bodycomp_all$Fish_Ht)) #FALSE
any(is.na(upperriver_bodycomp_all$Fish_Wdth)) #FALSE
```

### Making body size metric via PC score of Leng_1, Fish_Ht, and Fish_Grth
```{r}
str(upperriver_bodycomp_all)

## PC scores via linear regression for body size analysis ### 
bc_pca1 <- princomp(upperriver_bodycomp_all[,c(12,16,19)], cor=T, scores=T, covmat = NULL) #should work now without any NAs
summary(lm(upperriver_bodycomp_all$Fish_Leng_1 ~ bc_pca1$scores[,1])) #R = 0.6424

summary(bc_pca1, loadings=T, cutoff=0.0001) #summary of PC analysis
bc_pca1$scores
screeplot(bc_pca1, type=c('lines'))
bodysize_pc <- bc_pca1$scores[,1]

#combine dataframe with column for body size PC scores
upperriver_bodycomp_pc <- cbind(upperriver_bodycomp_all, bodysize_pc) 
str(upperriver_bodycomp_pc)
upperriver_bodycomp_pc <- upperriver_bodycomp_pc[,-(82:85)]
str(upperriver_bodycomp_pc)

#Now, run AIC again but PC1 scores are the response variable / numeric
write.csv(upperriver_bodycomp_pc, "upperriver_bodycomp_PCscores.csv")
```

### Import Data for models
```{r}
rm(list = ls())
upperriver_bodycomp_PCscores <- "upperriver_bodycomp_PCscores.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(upperriver_bodycomp_PCscores)[,-1] #81 variables, 246 observations b/c one row with NA sex is removed
any(is.na(DataSet$Fish_Leng_1)) #FALSE
any(is.na(DataSet$Fish_Grth)) #FALSE
any(is.na(DataSet$Fish_Ht)) #FALSE
any(is.na(DataSet$Fish_Wdth)) #FALSE

any(is.na(DataSet$Collection_Location)) #FALSE
any(is.na(DataSet$Year)) #FALSE
any(is.na(DataSet$Sex)) #FALSE
any(is.na(DataSet$Collection_Region)) # FALSE

#### CHECK DIRECTION OF PC SCORE ###
library(ggplot2)
ggplot(DataSet, aes(x=Fish_Leng_1, y=bodysize_pc)) +
  geom_point()
#so direction of PC score is positive, can check with other variables

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
levels(DataSet$Collection_Location) # 11 unique locations
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
DataSet$Collection_Region <- as.factor(DataSet$Collection_Region)
levels(DataSet$Collection_Region) # 4 Levels
DataSet$SpawnStatus <- as.factor(DataSet$SpawnStatus) #should be 4 levels
str(DataSet)

```

### Making Models for bodysize_pc~SpawningPopulation, includes SpawnStatus
```{r}
# Models for reference
bodysize_SP_modelset <- "bodysize_spawningpopulation/bodysize~SpawningPopulation_modelset.csv"

ModelSet<-read.csv(bodysize_SP_modelset)

model1 <- lm(bodysize_pc~1, data=DataSet)
model2 <- lm(bodysize_pc~ SpawnStatus + Collection_Location, data = DataSet)
model3 <- lm(bodysize_pc~ SpawnStatus + Sex, data = DataSet)
model4 <- lm(bodysize_pc~SpawnStatus + Year, data = DataSet)
model5 <- lm(bodysize_pc~ SpawnStatus + Collection_Region, data = DataSet)
model6 <- lm(bodysize_pc~ SpawnStatus + Collection_Location + Sex, data = DataSet)
model7 <- lm(bodysize_pc~ SpawnStatus + Collection_Region + Sex, data = DataSet)
summary(model7)
model8 <- lm(bodysize_pc~ SpawnStatus + Collection_Location + Year, data = DataSet)
model9 <- lm(bodysize_pc~SpawnStatus + Collection_Region + Year, data = DataSet)
model10 <- lm(bodysize_pc~ SpawnStatus + Sex + Year, data = DataSet)
model11 <- lm(bodysize_pc~ SpawnStatus + Collection_Region + Sex + Collection_Region:Sex, data = DataSet)
model12 <- lm(bodysize_pc~ SpawnStatus + Collection_Region + Year + Collection_Region:Year, data = DataSet)
model13 <- lm(bodysize_pc~SpawnStatus + Sex + Year + Sex:Year, data = DataSet)
model14 <- lm(bodysize_pc~ SpawnStatus + Collection_Location + Collection_Region + Sex + Year, data = DataSet)
```

### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12, model13, model14)

#table of AIC results
mynames1 <- paste("model", as.character(1:14), sep = "")
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12, model13, model14)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("bodysize_pc~SpawnStatus + Collection_Region + Sex",
                      "bodysize_pc~SpawnStatus + Collection_Region + Sex + Collection_Region:Sex",
                      "bodysize_pc~SpawnStatus + Collection_Location + Sex",
                      "bodysize_pc~SpawnStatus + Sex",
                      "bodysize_pc~SpawnStatus + Sex + Year",
                      "bodysize_pc~SpawnStatus + Collection_Location + Collection_Region + Sex + Year",
                      "bodysize_pc~SpawnStatus + Sex + Year + Sex:Year",
                      "bodysize_pc~SpawnStatus + Collection_Region",
                      "bodysize_pc~SpawnStatus + Collection_Region + Year",
                      "bodysize_pc~SpawnStatus + Collection_Location",
                      "bodysize_pc~SpawnStatus + Year",
                      "bodysize_pc~SpawnStatus + Collection_Location + Year",
                      "bodysize_pc~SpawnStatus + Collection_Region + Year + Collection_Region:Year",
                      "bodysize_pc~1")
colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "bodysize_spawningpopulation/AICresults_bodysize~SpawningPopulation.csv", row.names = FALSE)

```

### Model Averaging
```{r}
library(MuMIn)

 # Create a model selection table (this will give you AIC, AIC weights, etc.)
model_weights <- myaicc1$AICcWt ##Get the AIC weights from the AIC table
model_avg <- model.avg(models, weights = model_weights)
summary(model_avg)
avg_coefs <- coef(model_avg)
avg_confint <- confint(model_avg)
avg_se <- sqrt(diag(vcov(model_avg)))

# Convert the coefficients into a tidy data frame
coefs_df <- as.data.frame(avg_coefs)
colnames(coefs_df) <- "Avg_Coef"
coefs_df$CI_Lower <- avg_confint[, 1]  # Add lower bound of confidence intervals
coefs_df$CI_Upper <- avg_confint[, 2] # Add upper bound of confidence intervals
coefs_df$SE <- avg_se
print(coefs_df) #Model Averaging Coefficients for AIC model selection approach with body size as response variable

write.csv(coefs_df, file = "bodysize_spawningpopulation/bodysize~spawningpopulation_models_CoefEstimates.csv", row.names = TRUE)

### Of Note, Klutina Lake only has data for 2021 (males and females) which might be causing the NA values-- Klutina River is only 1 point, should I remove?
```

### Figure that displays parameter estimates + CI for each parameter in the model set
```{r}
paramestimates_bodysize <- "bodysize_spawningpopulation/bodysize~spawningpopulation_models_CoefEstimates.csv"

paramestimates_bodysize<-read.csv(paramestimates_bodysize)
str(paramestimates_bodysize)

levels(factor(paramestimates_bodysize$X))
paramestimates_bodysize$X <- factor(paramestimates_bodysize$X, 
                           levels = rev(factor(paramestimates_bodysize$X)))


library(ggplot2)
ggplot(paramestimates_bodysize, aes(x = Avg_Coef, y = X)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

library(dplyr)
paramestimates_bodysize_filtered <- paramestimates_bodysize %>%
  filter(!X %in% c("SpawnStatus0", "SpawnStatus1", "SpawnStatus2", "SpawnStatus3"))  # Filter out specific levels

bodysize_plot <- ggplot(paramestimates_bodysize_filtered, aes(x = Avg_Coef, y = X)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() +
  theme(axis.title = element_text(size = 24), 
        axis.text = element_text(size = 24))

ggsave("bodysize_spawningpopulation/BodySize_ParamEstimates_Plot.png", plot=bodysize_plot, height=12, width=12, units="in")


```