---
title: "AH_AICc_energydensity~SP"
author: "Abby Host"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

### Loading Data
```{r}
rm(list = ls())
library(AICcmodavg)
library(lubridate)
library(ggplot2)

#data loading
# bc19 <- read.csv("bodycomp_2019.csv")
# bc20 <- read.csv("bodycomp_2020.csv")
# bc21 <- read.csv("bodycomp_2021.csv")
#need to bind all together for total body comp dataset, Upper River river only

# bc_UR_total <- rbind(bc19[61:172,], bc20[61:120,], bc21[61:182,])
# write.csv(bc_UR_total, "upperriver_bodycomp_all.csv")
upperriver_bodycomp_all<-read.csv("upperriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
str(upperriver_bodycomp_all)
upperriver_bodycomp_all$Collection_Date <- as.Date(upperriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
upperriver_bodycomp_all$Year <- year(upperriver_bodycomp_all$Collection_Date)
str(upperriver_bodycomp_all)

#replace blank cell in Sex with NA 
upperriver_bodycomp_all$Sex[upperriver_bodycomp_all$Sex == ""] <- NA
str(upperriver_bodycomp_all)

write.csv(upperriver_bodycomp_all, "upperriver_bodycomp_all.csv")
```

### Import Data for models, check for NAs and eliminate as needed

```{r, include = FALSE}
rm(list = ls())
upperriver_bodycomp_all <- "upperriver_bodycomp_all.csv"
DataSet<-read.csv(upperriver_bodycomp_all)[,-1]

##### For the Upper River Data, I want to elimiate Power Creek Cordova, Eyak Weir Cordova, Bone Creek, Klutina River, and Upper Klutina, and Copper Lake data points as they don't apply to my spawning populations of interest ####
library(dplyr)

# Use filter() to exclude the specific collection locations
DataSet <- DataSet %>%
  filter(!Collection_Location %in% c("Power Creek Cordova", "Eyak Weir Cordova", "Bone Creek", "Copper Lake", "Klutina River", "Upper Klutina"))

#convert gonad_wt to grams from kilograms
DataSet$Gonad_Wt_g <- DataSet$Gonad_Wt * 1000

### Now, need to remove NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))
DataSet[is.na(DataSet$Sex), ] #row 87 and 110 has no sex value, eliminate it for models
DataSet[is.na(DataSet$EnergyPDry_1), ] #Row 35 does not have a Energy Content 1 value, so eliminate for analysis
#check gonad weight for NAs
any(is.na(DataSet$Gonad_Wt_g))
DataSet[is.na(DataSet$Gonad_Wt_g), ] #need to eliminate these rows or model selection will not work
DataSet <- DataSet[-c(18,35,36,40,61,65,77,87,102,110,118,141,142,144,161, 164,221, 222,224),] #excludes row missing sex file
any(is.na(DataSet$Sex)) #FALSE
any(is.na(DataSet$Gonad_Wt_g)) #FALSE
any(is.na(DataSet$EnergyPDry_1)) #FALSE


# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet) #220 observations and 82 variables

#Make work metric (migratory difficulty metric where work = F x distance)
DataSet$Elevation_m <- as.numeric(DataSet$Elevation_m)
DataSet$Work <- (DataSet$Collection_RiverMile_m * DataSet$Elevation_m) / (1000*1000) #so work is in km^2 
str(DataSet) 



#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
levels(DataSet$Collection_Location) # 7 unique locations
DataSet$Year<- as.factor(DataSet$Year)
levels(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)


```


### Making Models for EnergyPDry_1\~SpawningPopulation, includes SpawnStatus
```{r}
# Models for reference
energypdry_SP_modelset <- "energydensity_spawningpopulation/EnergyPDry_1~SpawningPopulation_modelset.csv"

ModelSet<-read.csv(energypdry_SP_modelset)

model1 <- lm(EnergyPDry_1~1, data=DataSet)
model2 <- lm(EnergyPDry_1~ Gonad_Wt_g + Work, data = DataSet)
model3 <- lm(EnergyPDry_1~ Gonad_Wt_g + Sex, data = DataSet)
model4 <- lm(EnergyPDry_1~Gonad_Wt_g + Year, data = DataSet)
model5 <- lm(EnergyPDry_1~ Gonad_Wt_g + Work + Sex, data = DataSet)
model6 <- lm(EnergyPDry_1~ Gonad_Wt_g + Work + Year, data = DataSet)
model7 <- lm(EnergyPDry_1~ Gonad_Wt_g + Sex + Year, data = DataSet)
model8 <- lm(EnergyPDry_1~ Gonad_Wt_g + Work + Sex + Work:Sex, data = DataSet)
model9 <- lm(EnergyPDry_1~ Gonad_Wt_g + Work + Year + Work:Year, data = DataSet)
model10 <- lm(EnergyPDry_1~Gonad_Wt_g + Sex + Year + Sex:Year, data = DataSet)
model11 <- lm(EnergyPDry_1~ Gonad_Wt_g + Work + Sex + Year, data = DataSet)
```

### AICc Model Selection

```{r}
AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11)

edModels <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11)

# Generate AIC table
mynames_ed <- paste("model", as.character(1:11), sep = "")
ed_aicc <- aictab(edModels, modnames = mynames_ed)
print(ed_aicc) #so selection order is:
              # K   AICc Delta_AICc AICcWt Cum.Wt      LL
              # model9  8 654.23       0.00   0.68   0.68 -318.77
              # model7  6 657.02       2.79   0.17   0.85 -322.31
              # model10 8 658.51       4.28   0.08   0.93 -320.91
              # model11 7 658.88       4.65   0.07   1.00 -322.17
              # model4  5 665.64      11.41   0.00   1.00 -327.68
              # model6  6 667.41      13.18   0.00   1.00 -327.51
              # model3  4 668.94      14.71   0.00   1.00 -330.38
              # model5  5 671.00      16.77   0.00   1.00 -330.36
              # model8  6 672.60      18.38   0.00   1.00 -330.10
              # model1  2 674.81      20.58   0.00   1.00 -335.38
              # model2  4 678.82      24.59   0.00   1.00 -335.32

# Convert AIC table to a data frame for easier manipulation
EDaic_df <- as.data.frame(ed_aicc)
EDaic_df$ModelName <- c("EnergyPDry_1~ Gonad_Wt_g + Work + Year + Work:Year",
                        "EnergyPDry_1~ Gonad_Wt_g + Sex + Year",
                        "EnergyPDry_1~Gonad_Wt_g + Sex + Year + Sex:Year",
                        "EnergyPDry_1~ Gonad_Wt_g + Work + Sex + Year",
                        "EnergyPDry_1~Gonad_Wt_g + Year",
                        "EnergyPDry_1~ Gonad_Wt_g + Work + Year",
                        "EnergyPDry_1~ Gonad_Wt_g + Sex",
                        "EnergyPDry_1~ Gonad_Wt_g + Work + Sex",
                        "EnergyPDry_1~ Gonad_Wt_g + Work + Sex + Work:Sex",
                        "EnergyPDry_1~1",
                        "EnergyPDry_1~ Gonad_Wt_g + Work")
colnames(EDaic_df)[colnames(EDaic_df) == "Modnames"] <- "Model #"

write.csv(EDaic_df, file = "energydensity_spawningpopulation/AICresults_EnergyPDry_1~SpawningPopulation.csv", row.names = FALSE)

```

### Model Averaging and Parameter Likelihoods
```{r}
# ---- Load necessary packages ----
library(MuMIn)
library(dplyr)

# ---- Step 1: Combine models into a named list ----
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11)
model_names <- paste0("Model_", seq_along(models))
names(models) <- model_names

# ---- Step 2: Run model selection (AICc) ----
model_sel <- model.sel(models)

# ---- Step 3: Model averaging (conditional averaging recommended) ----
model_avg <- model.avg(model_sel, full = FALSE)  # full = FALSE for conditional averaging
summary(model_avg)

# ---- Step 4: Extract averaged coefficients and confidence intervals ----
avg_coefs <- coef(model_avg)
avg_confint <- confint(model_avg)
avg_se <- sqrt(diag(vcov(model_avg)))

# ---- Step 5: Create tidy coefficient summary ----
coefs_df <- as.data.frame(avg_coefs)
colnames(coefs_df) <- "Avg_Coef"
coefs_df$CI_Lower <- avg_confint[, 1]
coefs_df$CI_Upper <- avg_confint[, 2]
coefs_df$SE <- avg_se
coefs_df$Parameter <- rownames(coefs_df)

# Reorder for clarity
coefs_df <- coefs_df[, c("Parameter", "Avg_Coef", "SE", "CI_Lower", "CI_Upper")]

# ---- Step 6: Helper function to normalize interaction term names ----
normalize_param_name <- function(name) {
  if (grepl(":", name)) {
    parts <- strsplit(name, ":")[[1]]
    paste(sort(parts), collapse = ":")
  } else {
    name
  }
}

# ---- Step 7: Calculate parameter likelihoods (relative importance) ----
weights <- model_sel$weight

# Extract all unique parameter names across models (normalize interaction terms)
param_names <- unique(unlist(sapply(models, function(m) {
  sapply(names(coef(m)), normalize_param_name)
})))

# Calculate parameter likelihoods safely
param_likelihoods <- sapply(param_names, function(param) {
  models_with_param <- sapply(models, function(m) {
    any(sapply(names(coef(m)), function(p) normalize_param_name(p) == param))
  })
  if (any(models_with_param)) {
    sum(weights[models_with_param])
  } else {
    0  # If not in any model, assign 0
  }
})

# ---- Step 8: Create param_likelihoods_df and merge cleanly ----
param_likelihoods_df <- data.frame(
  Parameter = param_names,
  ParamLikelihood = param_likelihoods
)

# Drop any old ParamLikelihood (if present), then merge cleanly
coefs_df <- coefs_df %>% select(-any_of("ParamLikelihood"))
coefs_df <- left_join(coefs_df, param_likelihoods_df, by = "Parameter")

# ---- Step 9: Sort by parameter likelihood ----
coefs_df <- coefs_df %>%
  arrange(desc(ParamLikelihood))

# ---- Step 9: View or export final result ----
print(coefs_df)
write.csv(coefs_df, "energydensity_spawningpopulation/energydensity_spawningpopulation_ModelAvg_Coefs_withLikelihoods.csv", row.names = FALSE)


# ---- Step 10: Table for coefficients and threshold for parameter likelihoods ----
threshold <- 0.1  # Set threshold for importance

# Add a new column to coefs_df that marks important vs non-important parameters
coefs_df$Importance <- ifelse(coefs_df$ParamLikelihood > threshold, "Important", "Non-Important")

# ---- Color Code Important Parameters with Color Blind Friendly Colors ----
# Light green for important, light gray for non-important
library(kableExtra)

# Create the table without adding duplicate headers
coefs_table <- coefs_df %>%
  arrange(desc(ParamLikelihood)) %>%
  kable("html", escape = FALSE, align = c("l", "r", "r", "r", "r", "r", "l")) %>%
  # Apply color coding based on importance
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  row_spec(which(coefs_df$Importance == "Important"), background = "lightgreen", color = "black") %>%
  row_spec(which(coefs_df$Importance == "Non-Important"), background = "lightgray", color = "black") # Adjust column width if needed

# Print or save the table
coefs_table

```







### Figure that displays parameter estimates + CI for each parameter in the model set
```{r}
paramestimates_energypdry <- "energydensity_spawningpopulation/energydensity_spawningpopulation_ModelAvg_Coefs_withLikelihoods.csv"

paramestimates_energy<-read.csv(paramestimates_energypdry)
str(paramestimates_energy)

levels(factor(paramestimates_energy$Parameter))
paramestimates_energy$Parameter <- factor(paramestimates_energy$Parameter, 
                           levels = rev(factor(paramestimates_energy$Parameter)))


library(ggplot2)
ggplot(paramestimates_energy, aes(x = Avg_Coef, y = Parameter)) + 
  geom_point(size = 3) +  # For the coefficient estimate as dots
  geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.2) + # Horizontal CI bars
  labs(x = "Parameter Estimate", y = "Parameter") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  theme_minimal() 
  # + theme(axis.title = element_text(size = 24), 
       # axis.text = element_text(size = 24))

```

### Visualizing Best Selected Models from above, for pre-spawn fish
```{r}
prespawn_data <- DataSet[DataSet$SpawnStatus == 0, ]
ggplot(prespawn_data, aes(x = Work, y = EnergyPDry_1)) +
  geom_point(alpha = 0.5, color = "darkblue") +
  geom_smooth(method = "loess", color = "red") +
  facet_wrap(~ Year) +
  theme_minimal() +
  labs(title = "Energy vs Work Faceted by Year") #can I visualize this without long lake? 

prespawn_data_noLL <- prespawn_data %>%
  filter(!Collection_Location %in% c("Long Lake"))

ggplot(prespawn_data_noLL, aes(x = Work, y = EnergyPDry_1)) +
  geom_point(alpha = 0.5, color = "darkblue") +
  geom_smooth(method = "lm", color = "red") +
  facet_wrap(~ Year) +
  theme_minimal() +
  labs(title = "Energy vs Work Faceted by Year")

```

### Figures for Copper River Workshop February 2025
```{r, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
# Pete wants a figure/visualization of energy content of various spawning populations

rm(list = ls())
upperriver_bodycomp_all <- "upperriver_bodycomp_all.csv"
DataSet<-read.csv(upperriver_bodycomp_all)[,-1]

##### For the Upper River Data, I want to elimiate Power Creek Cordova, Eyak Weir Cordova, Bone Creek, and Copper Lake data points as they don't apply to my spawning populations of interest ####
library(dplyr)

# Assuming your data frame is named df, use filter() to exclude the specific collection locations
DataSet <- DataSet %>%
  filter(!Collection_Location %in% c("Power Creek Cordova", "Eyak Weir Cordova", "Bone Creek", "Copper Lake", "Klutina River", "Upper Klutina"))


### Now, need to remove NAs that will mess up levels / model weight
any(is.na(DataSet$Collection_Location))
any(is.na(DataSet$Migratory_Difficulty))
any(is.na(DataSet$Year))
any(is.na(DataSet$Sex))
DataSet[is.na(DataSet$Sex), ] #row 87 and 110 has no sex value, eliminate it for models
DataSet <- DataSet[-c(87,110),] #excludes row missing sex file
any(is.na(DataSet$Sex))

#Response variable, check for NAs
any(is.na(DataSet$EnergyPDry_1))
DataSet[is.na(DataSet$EnergyPDry_1), ] #Row 35 does not have a Energy Content 1 value, so eliminate for analysis
DataSet <- DataSet[-c(35),]
any(is.na(DataSet$EnergyPDry_1)) # False

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
levels(DataSet$Collection_Location) # 7 unique locations
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
DataSet$Migratory_Difficulty <- as.factor(DataSet$Migratory_Difficulty)
levels(DataSet$Migratory_Difficulty) # 4 Levels
DataSet$Migratory_Difficulty <- factor(DataSet$Migratory_Difficulty,
                                       levels = c("Low",
                                                  "Middle",
                                                  "Middle-High",
                                                  "High")) #re-leveling
DataSet$SpawnStatus <- as.factor(DataSet$SpawnStatus) #should be 4 levels
str(DataSet)



DataSet2 <- DataSet %>%
  filter(Strontium_marked_Y.N != "NO READ")
DataSet2$Strontium_marked_Y.N <- as.factor(DataSet2$Strontium_marked_Y.N)
levels(DataSet2$Strontium_marked_Y.N) #Now only Y and N available


                #### Strontium Analysis of Energy ######
str(DataSet2)
#first I want to determine which collection_location levels contain fish samples with both Y and N strontium markings for comparison of energyPdry_1
locations_with_both <- DataSet2 %>%
  group_by(Collection_Location) %>%
  filter(any(Strontium_marked_Y.N == "Y") & any(Strontium_marked_Y.N == "N")) %>%
  pull(Collection_Location) %>%
  unique()

# Filter dataset to keep only the locations with both "Y" and "N" levels
strontium_data <- DataSet2 %>%
  filter(Collection_Location %in% locations_with_both)

#So all of this Y fish are in Gulkana or Fish creek with an exception of one return fish that was collected at Mentasta-- important to note! but for the sake of visualization, I am removing that fish
strontium_data <- strontium_data %>%
  filter(Collection_Location != "Mentasta")


library(ggplot2)
#Now, I want to further visualize this by year (2019, 2020, 2021)
# Boxplot comparing EnergyPDry_1 by Strontium Y/N and Year
ggplot(strontium_data, aes(x = Strontium_marked_Y.N, y = EnergyPDry_1, fill = Strontium_marked_Y.N)) +
  geom_boxplot() +
  facet_grid(~ Year) + 
  labs(title = "The energy content (mJ/kg) of strontium marked and non-marked sockeye from Gulkana Hatchery and Fish Creek \nduring the 2019-2021 sampling seasons.",
       x = "Strontium Level (Y/N)",
       y = "Energy (EnergyPDry_1)",
       fill = "Presence of \nStrontium Mark") + 
  theme_classic() +
  scale_x_discrete(labels = c("Y" = "Marked", "N" = "Non-Marked")) + 
  scale_fill_manual(values = c("Y" = "red", "N" = "blue"),
                    labels = c("Y" = "Marked", "N" = "Non-Marked"))  # Change legend labels




                ##### Energy Analysis of Pre-Spawn Fish #####

# use filter() to exclude the any partial/post/anomolous spawned fish
DataSet_prespawn <- DataSet %>%
  filter(!SpawnStatus %in% c("1","2","3"))

# use filter() to exclude the any partial/anomolous spawned fish
DataSet_prepostspawn <- DataSet %>%
  filter(!SpawnStatus %in% c("1","3"))



# Relevel the factor in one step
DataSet_prespawn$Collection_Location <- factor(DataSet_prespawn$Collection_Location,
                             levels = c("Long Lake", 
                                      "Mahlo", 
                                      "St Anne",
                                      "Mentasta", 
                                      "Tanada", 
                                      "Gulkana Hatchery", 
                                      "Fish Creek Gulkana"))

  # Faceted boxplot by Year and Collection Location
ggplot(DataSet_prespawn, aes(x = Collection_Location, y = EnergyPDry_1)) +
  geom_boxplot(aes(fill = Collection_Location), alpha = 0.6) +
  facet_wrap(~ Year) +
  labs(title = "Differences of energy content (mJ/kg) of pre-spawn sockeye sampled from different \nspawning locations in the Copper River Basin, separated by sampling year (2019-2021)",
       x = "Collection Location",
       y = "Energy Content (mJ/kg)") + 
   guides(fill = "none") + 
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 60, hjust = 1))




### Pre vs Post Spawn energy differences in sockeye for 2019-2021 only
# Ensure 'Year' is a factor variable (if not already)
DataSet_prepostspawn$Year <- as.factor(DataSet_prepostspawn$Year)

#Per Pete's request, filter data so that it includes collection_locations only that contain pre AND post data points:
library(dplyr)

location_summary <- DataSet %>%
  filter(SpawnStatus %in% c(0, 2)) %>%  # Keep only 0 and 2
  group_by(Collection_Location) %>%
  summarise(has_pre_spawn = any(SpawnStatus == 0), 
            has_post_spawn = any(SpawnStatus == 2)) %>%
  filter(has_pre_spawn & has_post_spawn)  # Keep only locations with both 0 and 2

# View the table
print(location_summary)

DataSet_prepostspawnLoc <- DataSet %>%
  filter(!SpawnStatus %in% c("1", "3")) %>%  # Exclude SpawnStatus 1 and 3
  group_by(Collection_Location) %>%
  filter(all(c(0, 2) %in% SpawnStatus)) %>%
  ungroup()  # Remove grouping after filtering


ggplot(DataSet_prepostspawnLoc, aes(x = SpawnStatus, y = EnergyPDry_1, fill = SpawnStatus)) +
  geom_boxplot(alpha = 0.6) + # Color for pre-spawn and post-spawn
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Differences of energy content (mJ/kg) between pre-spawn and \npost-spawn sockeye sampled in the Copper River Basin from 2019-2021",
       x = "Spawn Status",
       y = "Energy Content (mJ/kg)",
       fill = "SpawnStatus") +
  facet_wrap(~ Collection_Location) +
  theme_classic() +   
  scale_fill_manual(values = c("0" = "skyblue", "2" = "salmon"),
                    labels = c("0" = "Pre-Spawn", "2" = "Post-Spawn")) + 
  scale_x_discrete(labels = c("0" = "Pre-Spawn", "2" = "Post-Spawn"))



### Include partial spawn data for long lake
str(DataSet)
library(dplyr)

DataSet_prepartialspawnLoc <- DataSet %>%
  filter(!SpawnStatus %in% c("2", "3")) %>%  # Exclude SpawnStatus 2 and 3
  group_by(Collection_Location) %>%
  filter(all(c(0, 1) %in% SpawnStatus)) %>%
  ungroup()  # Remove grouping after filtering


gpartial <- ggplot(DataSet_prepartialspawnLoc, aes(x = SpawnStatus, y = EnergyPDry_1, fill = SpawnStatus)) +
  geom_boxplot(alpha = 0.6) + # Color for pre-spawn and post-spawn
  labs(title = "Differences of energy content (mJ/kg) between pre-spawn and \npartial-spawn sockeye sampled in the Copper River Basin from 2019-2021",
       x = "Spawn Status",
       y = "Energy Content (mJ/kg)",
       fill = "SpawnStatus") +
  facet_wrap(~ Collection_Location) +
  theme_classic() +   
  scale_fill_manual(values = c("0" = "skyblue", "1" = "purple"),
                    labels = c("0" = "Pre-Spawn", "1" = "Partial-Spawn")) + 
  scale_x_discrete(labels = c("0" = "Pre-Spawn", "1" = "Partial-Spawn"))



ggplot(DataSet_prepartialspawnLoc, aes(x = SpawnStatus, y = EnergyPDry_1, fill = SpawnStatus)) +
  geom_boxplot(alpha = 0.6) + # Color for pre-spawn and post-spawn
  labs(title = "Differences of energy content (mJ/kg) between pre-spawn and \npartial-spawn sockeye sampled in the Copper River Basin from 2019-2021",
       x = "Spawn Status",
       y = "Energy Content (mJ/kg)",
       fill = "SpawnStatus") +
  facet_wrap(~ Collection_Location) +
  theme_classic() +   
  scale_fill_manual(values = c("0" = "skyblue", "1" = "purple"),
                    labels = c("0" = "Pre-Spawn", "1" = "Partial-Spawn")) + 
  scale_x_discrete(labels = c("0" = "Pre-Spawn", "1" = "Partial-Spawn"))

```
