---
title: "AH_AICc_fineness~RTG"
author: "Abby Host"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

### Checking for NAs for PC score
```{r, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
rm(list = ls())
DataSet <- read.csv("lowerriver_bodycomp_PCscores.csv")
str(DataSet)
DataSet$Fish_Wdth_mm <- DataSet$Fish_Wdth * 10
DataSet$Fish_Wt_g <- DataSet$Fish_Wt * 1000
str(DataSet)

#eliminate unnecessary group assignments
# Standardize levels
DataSet$Collection_Location <- factor(DataSet$Collection_Location)
levels(DataSet$Collection_Location)



#check width values to determine if need to estimate
any(is.na(DataSet$Fish_Wdth_mm)) #True, need to estimate for lower river data
DataSet[is.na(DataSet$Fish_Wdth_mm), ]



###=================== Estimate Width Values ====================

# Subset the data for female F fish only
DataSetF <- DataSet[DataSet$Sex == "F", ]
summary(lm(Fish_Wdth_mm ~ Fish_Wt_g, data = DataSetF)) #R = 0.3731


Wdth_F_lm <- lm(Fish_Wdth_mm ~ Fish_Wt_g, data = DataSetF)
summary(Wdth_F_lm) # R squared  0.64
plot(Wdth_F_lm)


predicted_values_WdthF <- predict(Wdth_F_lm, newdata = DataSetF)

DataSetF$Predicted_Fish_Wdth_mm <- predicted_values_WdthF # Add these predictions back to your dataset


ggplot(DataSetF, aes(x = Predicted_Fish_Wdth_mm, y = Fish_Wdth_mm)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Wdth_mm, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Female Fish Wdth",
       x = "Predicted Fish Width",
       y = "Fish Width") +
  theme_minimal() 

# Replace NAs in Fish_Grth with predicted values
DataSetF$Fish_Wdth_mm[is.na(DataSetF$Fish_Wdth_mm)] <- DataSetF$Predicted_Fish_Wdth_mm[is.na(DataSetF$Fish_Wdth_mm)]
## so now, the female subset has predicted values replacing the NAs for Grth


#Now, same for the male data
DataSetM <- DataSet[DataSet$Sex == "M", ] #subset of M from total data set

Wdth_M_lm <- lm(Fish_Wdth_mm ~ Fish_Wt_g, data = DataSetM) #making linear regression
summary(Wdth_M_lm) # R squared is 0.6141
plot(Wdth_M_lm)
predicted_values_WdthM <- predict(Wdth_M_lm, newdata = DataSetM) #predicting width values from male subset data
DataSetM$Predicted_Fish_Wdth_mm <- predicted_values_WdthM

ggplot(DataSetM, aes(x = Predicted_Fish_Wdth_mm, y = Fish_Wdth_mm)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Wdth_mm, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Male Fish Width",
       x = "Predicted Fish Width",
       y = "Fish Width") +
  theme_minimal() 

# Replace NAs in Fish_Wdth with predicted values
DataSetM$Fish_Wdth_mm[is.na(DataSetM$Fish_Wdth_mm)] <- DataSetM$Predicted_Fish_Wdth_mm[is.na(DataSetM$Fish_Wdth_mm)]
## so now, the male subset has predicted values replacing the NAs 

### Now, combine the two data sets back into one, called lowerriver_bodycomp_all ###
DataSet <- rbind(DataSetF, DataSetM)

#Check Leng_1 NAs
any(is.na(DataSet$Fish_Leng_1_mm)) #FALSE
any(is.na(DataSet$Fish_Wdth_mm)) #FALSE


DataSet <- DataSet %>%
  group_by(Sex) %>%
  mutate(fineness = Fish_Leng_1_mm / Fish_Wdth_mm)

str(DataSet$fineness) #fineness_2 is numeric

#Now, run AIC again but PC1 scores are the response variable / numeric
write.csv(DataSet, "lowerriver_bodycomp_fineness.csv")

```



### Checking for NAs for PC score
```{r, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
rm(list = ls())
DataSet <- read.csv("lowerriver_GSI_PCscores.csv")
str(DataSet)
DataSet$Fish_Wdth_mm <- DataSet$Fish_Wdth * 10
str(DataSet)

#eliminate unnecessary group assignments
# Standardize levels
DataSet$Group_Assignment <- factor(DataSet$Group_Assignment)
levels(DataSet$Group_Assignment)


# Clean up levels manually
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "Gulkana "] <- "Gulkana"
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "Gulkanahatchery"] <- "GulkanaHatchery"
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "KlutinaTonsinaOutlets"] <- "KlutinaTonsinaOutlet"
levels(DataSet$Group_Assignment)[levels(DataSet$Group_Assignment) == "insufficient genotypes"] <- "insufficient_genotypes"

# Then drop the insufficient genotypes
DataSet <- subset(DataSet, Group_Assignment != "insufficient_genotypes")
DataSet <- subset(DataSet, Group_Assignment != "LowerGroups")
DataSet$Group_Assignment <- droplevels(DataSet$Group_Assignment)

# Confirm new levels
levels(DataSet$Group_Assignment)


#check width values to determine if need to estimate
any(is.na(DataSet$Fish_Wdth_mm)) #False, so have all width values I need

```

### Adding Fineness Ratio for lowerriver_bodycomp_all
```{r}
### Fineness Ratio = A fish's "fineness ratio" refers to the ratio of its body length to its maximum cross-sectional diameter

#Need to calculate fineness according to sex
library(dplyr)
# Fineness Ratio 2: fish length / fish width, dependent on sex
DataSet <- DataSet %>%
  group_by(Sex) %>%
  mutate(fineness = Fish_Leng_1_mm / Fish_Wdth_mm)

str(DataSet$fineness) #fineness_2 is numeric

# View the mean fineness ratio by sex
mean_fineness <- DataSet %>%
  group_by(Sex) %>%
  summarise(mean_fineness = mean(fineness, na.rm = TRUE))

print(mean_fineness)

# Create new data file that includes fineness data in the dataset for models
write.csv(DataSet, "lowerriver_GSI_fineness.csv")


```




### Making Models for fineness~RunTimingGroup, includes collection location
```{r}
# Models for reference
rm(list = ls())
library(lubridate)
DataSet <- read.csv("lowerriver_bodycomp_fineness.csv")
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
DataSet$RunTimingGroup <- as.factor(DataSet$RunTimingGroup)
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
DataSet$Collection_Date <- as.Date(DataSet$Collection_Date)
DataSet$juliandate <- as.numeric(
  DataSet$Collection_Date - as.Date(paste0(DataSet$Year, "-06-01"))
)
str(DataSet)
DataSet$RunTimingGroup <- factor(DataSet$RunTimingGroup)


model1 <- lm(fineness~1, data=DataSet)
model2 <- lm(fineness~Collection_RiverMile_m + RunTimingGroup, data = DataSet)
model3 <- lm(fineness~Collection_RiverMile_m + Sex, data = DataSet)
model4 <- lm(fineness~Collection_RiverMile_m + RunTimingGroup + Sex, data = DataSet)

summary(model4)

```


### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4)

library(AICcmodavg)
#table of AIC results
mynames1 <- paste("model", as.character(1:4), sep = "")
models <- list(model1, model2, model3, model4)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("fineness~Collection_RiverMile_m + RunTimingGroup",
                      "fineness~Collection_RiverMile_m + RunTimingGroup + Sex",
                      "fineness~Collection_RiverMile_m + Sex",
                      "fineness~1")
colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "fineness_runtiminggroup/AICresults_fineness~RunTimingGroup.csv", row.names = FALSE)



```


### Model Averaging
```{r}
library(MuMIn)

# List your models (already fit with na.action=na.fail)
models <- list(model1, model2, model3)

# Model averaging based on AICc, conditional averaging (default is full=TRUE)
model_avg <- model.avg(models, rank = "AICc", full = TRUE)

# Summary with coefficients, SE, CIs
summary(model_avg)

# Full averaged coefficients
avg_coefs_full <- coef(model_avg, full = TRUE)

# Full averaged confidence intervals
avg_confint_full <- confint(model_avg, full = TRUE)

# Full averaged variance-covariance matrix and SE
avg_vcov_full <- vcov(model_avg, full = TRUE)
avg_se_full <- sqrt(diag(avg_vcov_full))

# Create tidy data frame with full averages
coefs_df_full <- as.data.frame(avg_coefs_full)
colnames(coefs_df_full) <- "Avg_Coef"
coefs_df_full$CI_Lower <- avg_confint_full[, 1]
coefs_df_full$CI_Upper <- avg_confint_full[, 2]
coefs_df_full$SE <- avg_se_full

# Calculate parameter importance (parameter likelihoods)
param_likelihoods <- sw(model_avg)
as.data.frame(param_likelihoods)


# Manually specify parameter likelihoods from sw(model_avg)
manual_likelihoods <- c(
  "(Intercept)" = 1.0,
  "Collection_RiverMile_m" = 1.0,
  "RunTimingGroupMiddle" = 0.865978,
  "RunTimingGroupLate" = 0.865978,
  "SexM" = 0.134022
)

# Add ParamLikelihoods by matching rownames
coefs_df_full$ParamLikelihood <- manual_likelihoods[rownames(coefs_df_full)]

# View final table
print(coefs_df_full)

write.csv(coefs_df_full, file = "fineness_runtiminggroup/fineness~runtiminggroup_models_CoefEstimates_withLikelihoods.csv", row.names = TRUE)
```

### Calculating actual parameter estimates according to intercept
```{r}
coefs_df_full$Actual_Param <- with(coefs_df_full, 
                                   Avg_Coef + coefs_df_full["(Intercept)", "Avg_Coef"])
coefs_df_full["(Intercept)", "Actual_Param"] <- coefs_df_full["(Intercept)", "Avg_Coef"]


```







### Making Models for fineness~GSI, includes collection location
```{r}
# Models for reference
rm(list = ls())
DataSet <- read.csv("lowerriver_GSI_fineness.csv")
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
DataSet$Group_Assignment <- as.factor(DataSet$Group_Assignment)
DataSet$Sex<- as.factor(DataSet$Sex)
DataSet$Collection_Date <- as.Date(DataSet$Collection_Date)
DataSet$juliandate <- as.numeric(
  DataSet$Collection_Date - as.Date(paste0(DataSet$Year, "-06-01")))
DataSet$RunTimingGroup <- factor(DataSet$RunTimingGroup)
str(DataSet) #collection_rivermile_m is numeric


levels(DataSet$Group_Assignment) #levels are not all consistent. Need to fix this


#models for fineness
model1 <- lm(fineness~1, data=DataSet)
model2 <- lm(fineness~Collection_RiverMile_m + Sex, data = DataSet)
model3 <- lm(fineness~Collection_RiverMile_m + Group_Assignment, data = DataSet)
model4 <- lm(fineness~Collection_RiverMile_m + Sex + Group_Assignment, data = DataSet)

summary(model2)




```


### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4)

#table of AIC results
mynames1 <- paste("model", as.character(1:4), sep = "")
models <- list(model1, model2, model3, model4)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("fineness~Collection_RiverMile_m + Sex",
                      "fineness~Collection_RiverMile_m + Sex + Group_Assignment ",
                      "fineness~Collection_RiverMile_m + Group_Assignment",
                      "fineness~1")


colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "fineness_GSI/AICresults_fineness~GSI.csv", row.names = FALSE)

summary(model3)

```


### Model Averaging
```{r}
library(MuMIn)

# List your models (already fit with na.action=na.fail)
models <- list(model1, model2, model3, model4)

# Model averaging based on AICc, conditional averaging (default is full=TRUE)
model_avg <- model.avg(models, rank = "AICc", full = TRUE)

# Summary with coefficients, SE, CIs
summary(model_avg)

# Full averaged coefficients
avg_coefs_full <- coef(model_avg, full = TRUE)

# Full averaged confidence intervals
avg_confint_full <- confint(model_avg, full = TRUE)

# Full averaged variance-covariance matrix and SE
avg_vcov_full <- vcov(model_avg, full = TRUE)
avg_se_full <- sqrt(diag(avg_vcov_full))

# Create tidy data frame with full averages
coefs_df_full <- as.data.frame(avg_coefs_full)
colnames(coefs_df_full) <- "Avg_Coef"
coefs_df_full$CI_Lower <- avg_confint_full[, 1]
coefs_df_full$CI_Upper <- avg_confint_full[, 2]
coefs_df_full$SE <- avg_se_full

# Calculate parameter importance (parameter likelihoods)
param_likelihoods <- sw(model_avg)
as.data.frame(param_likelihoods)

# Manually specify parameter likelihoods from sw(model_avg)
manual_likelihoods <- c(
  "(Intercept)" = 1.0,
  "Collection_RiverMile_m" = 1.00000000,
  "Group_AssignmentChitina" = 0.00838759,
  "Group_AssignmentGulkana" = 0.00838759,
  "Group_AssignmentGulkanaHatchery" = 0.00838759,
  "Group_AssignmentKlutinaLake" = 0.00838759,
  "Group_AssignmentKlutinaTonsinaOutlet" = 0.00838759,
  "Group_AssignmentSlana" = 0.00838759,
  "Group_AssignmentTanadaCopperLakes" = 0.00838759,
  "Group_AssignmentTazlina" = 0.00838759,
  "SexM" = 0.99690290	
)



# Add ParamLikelihoods by matching rownames
coefs_df_full$ParamLikelihood <- manual_likelihoods[rownames(coefs_df_full)]

# View final table
print(coefs_df_full)

write.csv(coefs_df_full, file = "fineness_GSI/fineness_GSI_ModelAvg_Coefs_withLikelihoods.csv", row.names = TRUE)

```

### Calculating actual parameter estimates according to intercept
```{r}
coefs_df_full$Actual_Param <- with(coefs_df_full, 
                                   Avg_Coef + coefs_df_full["(Intercept)", "Avg_Coef"])
coefs_df_full["(Intercept)", "Actual_Param"] <- coefs_df_full["(Intercept)", "Avg_Coef"]
```





### Making Models for fineness~SP, includes gonad_wt_g
```{r}
# Models for reference
rm(list = ls())
DataSet <- read.csv("upperriver_bodycomp_fineness.csv")[-1]
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location)
levels(DataSet$Collection_Location) # 7 unique locations
DataSet$Year<- as.factor(DataSet$Year)
levels(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)


#check gonad weight for NAs
DataSet$Gonad_Wt_g <- DataSet$Gonad_Wt * 1000
any(is.na(DataSet$Gonad_Wt_g))
DataSet[is.na(DataSet$Gonad_Wt_g), ] #need to eliminate these rows or model selection will not work
DataSet <- DataSet[-c(125, 136, 137, 148, 152, 154, 167, 176, 187, 188, 190, 198, 201, 228, 229, 231),]
any(is.na(DataSet$Gonad_Wt_g)) #FALSE

#DataSet$Work <- factor(DataSet$Work) #This is an important fix, otherwise its numeric but in fact its discrete factors

model1 <- lm(fineness~1, data=DataSet)
model2 <- lm(fineness~ Gonad_Wt_g + Collection_Location, data = DataSet)
model3 <- lm(fineness~ Gonad_Wt_g + Sex, data = DataSet)
model4 <- lm(fineness~ Gonad_Wt_g + Collection_Location + Sex, data = DataSet)

summary(model4)


```

### AICc Model Selection
```{r}
AIC(model1, model2, model3, model4)

#table of AIC results
mynames1 <- paste("model", as.character(1:4), sep = "")
models <- list(model1, model2, model3, model4)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("fineness~ Gonad_Wt_g + Collection_Location",
                      "fineness~ Gonad_Wt_g + Collection_Location + Sex",
                      "fineness~ 1",
                      "fineness~ Gonad_Wt_g + Sex")
colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "fineness_spawningpopulation/AICresults_fineness~SpawningPopulation.csv", row.names = FALSE)

```


```{r}
# ---- Load necessary packages ----
library(MuMIn)

# List your models (already fit with na.action=na.fail)
models <- list(model1, model2, model3, model4)

# Model averaging based on AICc, conditional averaging (default is full=TRUE)
model_avg <- model.avg(models, rank = "AICc", full = TRUE)

# Summary with coefficients, SE, CIs
summary(model_avg)

# Full averaged coefficients
avg_coefs_full <- coef(model_avg, full = TRUE)

# Full averaged confidence intervals
avg_confint_full <- confint(model_avg, full = TRUE)

# Full averaged variance-covariance matrix and SE
avg_vcov_full <- vcov(model_avg, full = TRUE)
avg_se_full <- sqrt(diag(avg_vcov_full))

# Create tidy data frame with full averages
coefs_df_full <- as.data.frame(avg_coefs_full)
colnames(coefs_df_full) <- "Avg_Coef"
coefs_df_full$CI_Lower <- avg_confint_full[, 1]
coefs_df_full$CI_Upper <- avg_confint_full[, 2]
coefs_df_full$SE <- avg_se_full

# Calculate parameter importance (parameter likelihoods)
param_likelihoods <- sw(model_avg)
as.data.frame(param_likelihoods)

# Manually specify parameter likelihoods from sw(model_avg)
manual_likelihoods <- c(
  "(Intercept)" = 1.0,
  "Gonad_Wt_g" = 0.971629,
  "Collection_LocationGulkana Hatchery" = 0.964420, 
  "Collection_LocationLong Lake" = 0.964420,
  "Collection_LocationMahlo" = 0.964420,
  "Collection_LocationMentasta" = 0.964420,
  "Collection_LocationSt Anne" = 0.964420,
  "Collection_LocationTanada" = 0.964420,
  "SexM" = 0.340892
)


# Add ParamLikelihoods by matching rownames
coefs_df_full$ParamLikelihood <- manual_likelihoods[rownames(coefs_df_full)]

# View final table
print(coefs_df_full)

write.csv(coefs_df_full, file = "fineness_spawningpopulation/fineness_spawningpopulation_ModelAvg_Coefs_withLikelihoods.csv", row.names = TRUE)

```

### Calculating actual parameter estimates according to intercept
```{r}
coefs_df_full$Actual_Param <- with(coefs_df_full, 
                                   Avg_Coef + coefs_df_full["(Intercept)", "Avg_Coef"])
coefs_df_full["(Intercept)", "Actual_Param"] <- coefs_df_full["(Intercept)", "Avg_Coef"]
```















### Fineness in Upper River
```{r}
DataSet <- read.csv("upperriver_bodycomp_PCscores.csv")
#checking NA
any(is.na(DataSet$Fish_Leng_1_mm))
any(is.na(DataSet$Fish_Ht_mm))
any(is.na(DataSet$Fish_Grth_mm)) #No NA's
any(is.na(DataSet$Fish_Wdth)) #True, need to determine how many values
DataSet[is.na(DataSet$Fish_Wdth), ] #12 rows need to be filled in

DataSet$Fish_Wdth_mm <- DataSet$Fish_Wdth*10


# Subset the data for female F fish only
DataSetF <- DataSet[DataSet$Sex == "F", ]

summary(lm(Fish_Wdth_mm ~ bodysize_pc_g_mm, data = DataSetF)) #R = 0.4102
summary(lm(Fish_Wdth_mm ~ Fish_Wt_g, data = DataSetF)) #R =  0.5268, so use this for predicting
summary(lm(Fish_Wdth_mm ~ Fish_Grth_mm, data = DataSetF)) # Adjusted R-squared:  0.4942


width_F_lm <- lm(Fish_Wdth_mm ~ Fish_Wt_g, data = DataSetF)
summary(width_F_lm) # R squared  0.6396
plot(width_F_lm)


predicted_values_widthF_mm <- predict(width_F_lm, newdata = DataSetF)

DataSetF$Predicted_Fish_Wdth_mm <- predicted_values_widthF_mm # Add these predictions back to your dataset


ggplot(DataSetF, aes(x = Predicted_Fish_Wdth_mm, y = Fish_Wdth_mm)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Wdth_mm, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Female Fish",
       x = "Predicted Fish Width",
       y = "Fish Width") +
  theme_minimal() 

# Replace NAs in Fish_Wdth_mm with predicted values
DataSetF$Fish_Wdth_mm[is.na(DataSetF$Fish_Wdth_mm)] <- DataSetF$Predicted_Fish_Wdth_mm[is.na(DataSetF$Fish_Wdth_mm)]
## so now, the female subset has predicted values replacing the NAs for Wdth



#Now, same for the male data
DataSetM <- DataSet[DataSet$Sex == "M", ] #subset of M from total data set

Wdth_M_lm <- lm(Fish_Wdth_mm ~ Fish_Wt_g, data = DataSetM) #making linear regression
summary(Wdth_M_lm) 
plot(Wdth_M_lm)
predicted_values_WdthM_mm <- predict(Wdth_M_lm, newdata = DataSetM) #predicting width values from male subset data
DataSetM$Predicted_Fish_Wdth_mm <- predicted_values_WdthM_mm

ggplot(DataSetM, aes(x = Predicted_Fish_Wdth_mm, y = Fish_Wdth_mm)) +
  geom_point(aes(color = "Observed")) +
  geom_point(aes(y = Predicted_Fish_Wdth_mm, color = "Predicted")) +
  scale_color_manual(values = c("Observed" = "blue", "Predicted" = "red")) +
  labs(title = "Observed vs Predicted Male Fish Width",
       x = "Predicted Fish Width",
       y = "Fish Width") +
  theme_minimal() 

# Replace NAs in Fish_Leng_1 with predicted values
DataSetM$Fish_Wdth_mm[is.na(DataSetM$Fish_Wdth_mm)] <- DataSetM$Predicted_Fish_Wdth_mm[is.na(DataSetM$Fish_Wdth_mm)]
## so now, the male subset has predicted values replacing the NAs 

DataSet <- rbind(DataSetM, DataSetF)


### Calculating Upper River Fineness
DataSet <- DataSet %>%
  group_by(Sex) %>%
  mutate(fineness = Fish_Leng_1_mm / Fish_Wdth_mm)

str(DataSet$fineness) 


# Create new data file that includes fineness data in the upper river fish
write.csv(DataSet, "upperriver_bodycomp_fineness.csv")



```
