---
title: "AH_AICc_bodysize~RTG"
author: "Abby Host"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```


#' =====================================================
#' AICc code for BodySizePC_1~RunTimingGroup models
#' =====================================================

### Loading Data
```{r}
library(AICcmodavg)
library(lubridate)

#data loading
bc19 <- read.csv("ALHcode/AIC/bodycomp_2019.csv")
bc20 <- read.csv("ALHcode/AIC/bodycomp_2020.csv")
bc21 <- read.csv("ALHcode/AIC/bodycomp_2021.csv")
#need to bind all together for total body comp dataset, lower river only

bc_LR_total <- rbind(bc19[1:60,], bc20[1:60,], bc21[1:60,])
write.csv(bc_LR_total, "ALHcode/AIC/lowerriver_bodycomp_all.csv")
lowerriver_bodycomp_all<-read.csv("ALHcode/AIC/lowerriver_bodycomp_all.csv")[,-1]
#all data is loaded now

#need to add year to dataset
lowerriver_bodycomp_all$Collection_Date <- as.Date(lowerriver_bodycomp_all$Collection_Date)

# Create a new column 'year' from the collection_date
lowerriver_bodycomp_all$Year <- year(lowerriver_bodycomp_all$Collection_Date)

write.csv(lowerriver_bodycomp_all, "ALHcode/AIC/lowerriver_bodycomp_all.csv")

```


### Calculating PC Score for body size
```{r}
lowerriver_bodycomp_all <- "ALHcode/AIC/lowerriver_bodycomp_all.csv"
lowerriver_bodycomp_all<-read.csv("ALHcode/AIC/lowerriver_bodycomp_all.csv")[,-1]

#checking NA
any(is.na(lowerriver_bodycomp_all$Fish_Leng_2))
any(is.na(lowerriver_bodycomp_all$Fish_Ht))
any(is.na(lowerriver_bodycomp_all$Fish_Grth)) #Na's present, will need to omit them for PC score
lowerriver_bodycomp_all[is.na(lowerriver_bodycomp_all$Fish_Grth), ] #row 64 has NA, remove for PC

lowerriver_bodycomp_all_pc <- lowerriver_bodycomp_all[-64,] #new dataframe with no NA's for bodysize metrics
      # length1 vs girth, length2 v girth, height v girth-- best R2 value and estimate girth for missing value

bc_pca1 <- princomp(lowerriver_bodycomp_all_pc[,c(12,14,16,19)], cor=T, scores=T, covmat = NULL) #should work now without any NAs

summary(bc_pca1, loadings=T, cutoff=0.0001) #summary of PC analysis
bc_pca1$scores
screeplot(bc_pca1, type=c('lines'))
bodysize_pc <- bc_pca1$scores[,1]

#combine dataframe with column for body size PC scores
lowerriver_bodycomp_pc_new <- cbind(lowerriver_bodycomp_all_pc, bodysize_pc) 

#Now, run AIC again but PC1 scores are the response variable / numeric
write.csv(lowerriver_bodycomp_pc_new, "ALHcode/AIC/lowerriver_bodycomp_PCscores.csv")
```


### Import Data for models
```{r}
lowerriver_bodycomp_PCscores <- "ALHcode/AIC/lowerriver_bodycomp_PCscores.csv"

# Import the data. Be sure to check the structure of the data and that R is reading continuous and categorical variables appropriately.
DataSet<-read.csv(lowerriver_bodycomp_PCscores)[,-1]

# View DataSet.
head(DataSet)
summary(DataSet)
nrow(DataSet)
str(DataSet)

#make response variables factors
DataSet$Collection_Location <- as.factor(DataSet$Collection_Location) 
DataSet$RunTimingGroup <- as.factor(DataSet$RunTimingGroup)
DataSet$Year<- as.factor(DataSet$Year)
DataSet$Sex<- as.factor(DataSet$Sex)
str(DataSet)

```

# Making Models for bodysize_pc~RunTimingGroup
model1 <- lm(bodysize_pc~1, data=DataSet)
model2 <- lm(bodysize_pc~Collection_Location, data = DataSet)
model3 <- lm(bodysize_pc~Collection_Location + RunTimingGroup, data = DataSet)
model4 <- lm(bodysize_pc~Collection_Location + Sex, data = DataSet)
model5 <- lm(bodysize_pc~Collection_Location + Year, data = DataSet)
model6 <- lm(bodysize_pc~Collection_Location + RunTimingGroup + Sex, data = DataSet)
model7 <- lm(bodysize_pc~Collection_Location + RunTimingGroup + Year, data = DataSet)
model8 <- lm(bodysize_pc~Collection_Location + Sex + Year, data = DataSet)
model9 <- lm(bodysize_pc~Collection_Location + RunTimingGroup + Sex + RunTimingGroup:Sex, data = DataSet)
model10 <- lm(bodysize_pc~Collection_Location + RunTimingGroup + Year + RunTimingGroup:Year, data = DataSet)
model11 <- lm(bodysize_pc~Collection_Location + Sex + Year + Sex:Year, data = DataSet)
model12 <- lm(bodysize_pc~Collection_Location + RunTimingGroup + Sex + Year, data = DataSet)


AIC(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12)

#table of AIC results
mynames1 <- paste("model", as.character(1:12), sep = "")
models <- list(model1, model2, model3, model4, model5, model6, model7, model8, model9, model10, model11, model12)

# Generate AIC table
myaicc1 <- aictab(models, modnames = mynames1)
print(myaicc1)
# Convert AIC table to a data frame for easier manipulation
aic_df <- as.data.frame(myaicc1)
aic_df$ModelName <- c("bodysize_pc~Collection_Location + RunTimingGroup + Sex + Year",
                      "bodysize_pc~Collection_Location + RunTimingGroup + Sex",
                      "bodysize_pc~Collection_Location + RunTimingGroup + Sex + RunTimingGroup:Sex", 
                      "bodysize_pc~Collection_Location + Sex", 
                      "bodysize_pc~Collection_Location + Sex + Year",
                      "bodysize_pc~Collection_Location + Sex + Year + Sex:Year", 
                      "bodysize_pc~Collection_Location + RunTimingGroup + Year",
                      "bodysize_pc~Collection_Location + RunTimingGroup", 
                      "bodysize_pc~1", 
                      "bodysize_pc~Collection_Location", 
                      "bodysize_pc~Collection_Location + Year", 
                      "bodysize_pc~Collection_Location + RunTimingGroup + Year + RunTimingGroup:Year")
colnames(aic_df)[colnames(aic_df) == "Modnames"] <- "Model #"

# Write the data frame to a CSV file
write.csv(aic_df, file = "ALHcode/AIC/bodysize~runtiminggroup/AICresults_bodysize~RunTimingGroup.csv", row.names = FALSE)

#Now I have the model selection, best model, model weights, etc-- I can now figure out parameter estimates for model 12 (the best model, lowest AIC for bodysize)
# Identify the best model (based on the lowest AIC weight)
str(aic_df)
print(aic_df$AICcWt)

# Find the index of the best model (the one with the highest AIC weight)
best_model_index <- which.max(aic_df$AICcWt)
print(best_model_index)

best_model_name <- aic_df$ModelName[best_model_index]
best_model_aic_weight <- aic_df$AICcWt[best_model_index]
print(paste("Best model is:", best_model_name))
print(paste("AIC weight of the best model:", best_model_aic_weight)) #so model 12 is the best model

best_model_summary <- summary(model12) #Extract the best model and its summary
print(best_model_summary)

# Extract coefficients (parameter estimates) and standard errors
param_estimates <- best_model_summary$coefficients[, 1]  # Estimate
std_errors <- best_model_summary$coefficients[, 2]       # Standard Error
t_values <- best_model_summary$coefficients[, 3]          # t-values
p_values <- best_model_summary$coefficients[, 4]          # p-values

# Calculate 95% Confidence Intervals
conf_intervals <- confint(model12)[-(9),]  # Default is 95% CI

# ombine all the information into a data frame
param_df <- data.frame(
  Parameter = rownames(best_model_summary$coefficients),
  Estimate = param_estimates,
  Std_Error = std_errors,
  t_value = t_values,
  p_value = p_values,
  CI_Lower = conf_intervals[, 1],
  CI_Upper = conf_intervals[, 2]
)

# Print the table
print(param_df)

# Save the results to a CSV for your manuscript
write.csv(param_df, file = "ALHcode/AIC/bodysize~runtiminggroup/bodysize~runtiminggroup_model12_ParamEstimates.csv", row.names = FALSE)



###### Model Averaging can now be completed ######
install.packages("MuMIn")
library(MuMIn)

# Create a model selection table (this will give you AIC, AIC weights, etc.)
model_weights <- myaicc1$AICcWt ##Get the AIC weights from the AIC table
model_avg <- model.avg(models, weights = model_weights)
summary(model_avg)
avg_coefs <- coef(model_avg)
avg_confint <- confint(model_avg)

# Convert the coefficients into a tidy data frame
coefs_df <- as.data.frame(avg_coefs)
colnames(coefs_df) <- "Avg_Coef"
coefs_df$CI_Lower <- avg_confint[, 1]  # Add lower bound of confidence intervals
coefs_df$CI_Upper <- avg_confint[, 2]  # Add upper bound of confidence intervals
print(coefs_df) #Model Averaging Coefficients for AIC model selection approach with body size as response variable



#### CHECK DIRECTION OF PC SCORE ###
library(ggplot2)
ggplot(DataSet, aes(x=Fish_Leng_1, y=bodysize_pc)) +
  geom_point()
#so direction of PC score is positive, can check with other variables


# Visualizing the results from the AIC-selected model: Model 12
# bodysize_pc ~ Collection_Location + RunTimingGroup + Sex + Year
library(dplyr)

DataSet$RunTimingGroup <- factor(DataSet$RunTimingGroup,
                               levels = c("Early",
                                          "Middle",
                                          "Late"),
                               labels = c("Early",
                                          "Middle",
                                          "Late"))

ggplot(data=DataSet[-(114),], aes(x = Collection_Location, y = bodysize_pc, fill = Sex)) +
  geom_boxplot() +
  labs(title = "Body Size by Collection Location and Sex") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


ggplot(DataSet, aes(x = Year, y = bodysize_pc, fill = RunTimingGroup)) +
  geom_boxplot() +
  labs(title = "Body Size by Run Timing Group and Year") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

