---
title: "ALH_MigratoryDifficulty"
author: "Abby Host"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

### Collection Locations
```{r}
# Reset R, clear all objects
rm(list=ls()) 

# Set WD
DataSet<- read.csv("CollectionLocations.csv")
str(DataSet)
unique(DataSet$Collection)

DataSet <- DataSet %>%
  filter(!Collection %in% c("klutina river"))

DataSet <- DataSet %>%
  filter(!Collection %in% c("copper lake"))

unique(DataSet$Collection)

```

### Map for Manuscript

``` {r}
# Load libraries, install as needed
library(leaflet)
library(dplyr)
library(ggplot2)
library(ggmap)
library(dplyr)
library(sf)
library(tmap)


# Set factor levels for consistent legend order
DataSet$Collection <- factor(
  DataSet$Collection,
  levels = c(
    "baird canyon", "canyon creek", "chitina airport", "long lake",
    "upper klutina", "st anne", "mahlo", "mentasta", "tanada",
    "gulkana hatchery", "fish creek gulkana"
  )
)

# Define color palette (named vector)
pal_colors <- c(
  "baird canyon" = "#7C7C7CFF",
  "canyon creek" = "black",
  "chitina airport" = "#800000FF",
  "long lake" = "#AF6458FF",
  "upper klutina" = "#736F4CFF",
  "st anne" = "#BA6E1DFF",
  "mahlo" = "#205F4BFF",
  "mentasta" = "#68855CFF",
  "tanada" = "#9C9C5EFF",
  "gulkana hatchery" = "#A06177FF",
  "fish creek gulkana" = "#467378FF"
)

# Create a color mapping function for leaflet
pal <- colorFactor(palette = pal_colors, domain = DataSet$Collection)

# Create the leaflet map
leaflet_map <- leaflet(DataSet) %>%
  addProviderTiles(providers$Esri.WorldTopoMap) %>%
  addCircleMarkers(
    lng = ~dd_long,
    lat = ~dd_lat,
    radius = 8,
    color = ~pal(Collection),
    fillOpacity = 1,
    stroke = FALSE,
    popup = ~paste("<b>Collection Location:</b>", Collection),
    label = ~Collection,
    labelOptions = labelOptions(noHide = FALSE, direction = "top")
  ) %>%
  addLegend(
    position = "bottomright",
    pal = pal,
    values = ~Collection,
    title = "Collection Location",
    opacity = 1
  )

# Display map
leaflet_map
```





### Metrics for Migratory Difficulty
```{r}
DataSet$River_Slope <- (DataSet$elevation_M / DataSet$Dist_M)*500 # Slope of River (as defined by Crossin 2004)
DataSet$Work <- (DataSet$elevation_M*DataSet$Dist_M) / 1000 # metric for Work as defined by Crossin 2004

str(DataSet)
DataSet$Collection <- as.factor(DataSet$Collection)



library(ggplot2)

# Scatter plot to visualize the relationship between river distance and elevation
ggplot(DataSet, aes(x = Dist_M, y = elevation_M, color = Collection)) +
  geom_point(size = 3) +
  labs(title = "Migratory Difficulty: Elevation vs River Distance",
       x = "River Distance (m)", y = "Elevation (m)") +
  theme_minimal() +
  theme(legend.position = "bottom") 

# Color-coded Scatter Plot: Elevation and River Distance
# Min-Max Normalization for scaling both variables between 0 and 1
DataSet$scaled_elevation <- (DataSet$elevation_M - min(DataSet$elevation_M)) / (max(DataSet$elevation_M) - min(DataSet$elevation_M))
DataSet$scaled_distance <- (DataSet$Dist_M - min(DataSet$Dist_M)) / (max(DataSet$Dist_M) - min(DataSet$Dist_M))

# Combine them equally weighted
DataSet$combined_value <- DataSet$scaled_elevation + DataSet$scaled_distance
ggplot(DataSet, aes(x = Dist_M, y = elevation_M, color = combined_value)) +
  geom_point(size = 6) +  # Add points to the plot
  scale_color_gradient(low = "blue", high = "red") +  # Color gradient for combined_value
  geom_text(aes(label = Collection), vjust = -1, hjust = 0.5, size = 3, color = "black") +  # Add labels above each point
  labs(
    title = "Heatmap: Combined Elevation and River Distance",
    x = "River Distance (m)",
    y = "Elevation (m)",
    color = "Difficulty"
  ) +
  theme_minimal()

```

### River Slope & Work as units of migratory difficulty, leaflet interactive plots
```{r}
# Load libraries, install as needed
library(leaflet)
library(dplyr)
library(ggplot2)
library(ggmap)
library(dplyr)
library(sf)
library(tmap)

ggplot(DataSet[-9,], aes(x = Dist_M, y = elevation_M, color = Work)) +
  geom_point(size = 6) +  # Add points to the plot
  scale_color_gradient(low = "blue", high = "red") +  # Color gradient for combined_value
  geom_text(aes(label = Collection), vjust = -1, hjust = 0.5, size = 3, color = "black") +  # Add labels above each point
  labs(
    title = "Heatmap: Combined Elevation, River Distance, and Work (where W = (Distance*Elevation)/1000)",
    x = "River Distance (m)",
    y = "Elevation (m)",
    color = "Work"
  ) +
  theme_minimal()

# Define a color palette for the River_Slope with a red gradient
pal <- colorNumeric(palette = "Reds", domain = DataSet$River_Slope)

# Create the leaflet map
leaflet_map <- leaflet(DataSet) %>%
  addTiles() %>%  # Add default OpenStreetMap tiles
  addCircleMarkers(
    lng = ~dd_long, lat = ~dd_lat, 
    radius = 10,  # Adjust the size of the markers
    color = ~pal(River_Slope),  # Color the markers based on River_Slope
    stroke = FALSE, fillOpacity = 0.7,  # Adjust opacity
    popup = ~paste("Collection Location:", Collection, "<br>", "River Slope:", round(River_Slope,2)),  # Show Collection Location in popup
    label = ~Collection,  # Show Collection Location as label
    labelOptions = labelOptions(noHide = TRUE, direction = "top")
  ) %>%
  addLegend(
    position = "bottomright", 
    pal = pal, values = ~River_Slope, 
    title = "River Slope", opacity = 1
  )  # Add legend for River Slope

# Display the map
leaflet_map


# Define a color palette for the Work with a red to blue gradient
pal2 <- colorNumeric(palette = c("blue", "red"), domain = DataSet$Work)

# Create the leaflet map
leaflet_map1 <- leaflet(DataSet) %>%
  addTiles() %>%  # Add default OpenStreetMap tiles
  addCircleMarkers(
    lng = ~dd_long, lat = ~dd_lat, 
    radius = 10,  # Adjust the size of the markers
    color = ~pal2(Work),  # Color the markers based on DataSet$Work using the red to blue gradient
    stroke = FALSE, fillOpacity = 0.7,  # Adjust opacity
    popup = ~paste("Collection Location:", Collection, "<br>", "Work Value:", round(Work)),  # Show Collection Location and Work value in popup
    label = ~Collection,  # Show Collection Location as label
    labelOptions = labelOptions(noHide = TRUE, direction = "top")
  ) %>%
  addLegend(
    position = "bottomright", 
    pal = pal2, values = ~Work,  # Use DataSet$Work for legend
    title = "Work (where W = (Distance*Elevation)/1000)", opacity = 1
  )  # Add legend for DataSet$Work

leaflet_map1



```




## Spawning Population Maps - Distance (m) and Elevation (m) as units of migratory difficulty
```{r}
# Define a color palette for the River_Slope with a red gradient
pal <- colorNumeric(palette = "Purples", domain = DataSet$elevation_M)

# Create the leaflet map
leaflet_elevation <- leaflet(DataSet) %>%
  addTiles() %>%  # Add default OpenStreetMap tiles
  addCircleMarkers(
    lng = ~dd_long, lat = ~dd_lat, 
    radius = 10,  # Adjust the size of the markers
    color = ~pal(elevation_M),  # Color the markers based on River_Slope
    stroke = FALSE, fillOpacity = 1,  # Adjust opacity
    popup = ~paste("Collection Location:", Collection, "<br>", "Elevation (m):", elevation_M),  # Show Collection Location in popup
    label = ~Collection,  # Show Collection Location as label
    labelOptions = labelOptions(noHide = TRUE, direction = "top")
  ) %>%
  addLegend(
    position = "bottomright", 
    pal = pal, values = ~elevation_M, 
    title = "Elevation (m)", opacity = 1
  )  # Add legend for River Slope

# Display the map
leaflet_elevation



# Define a color palette for the distance with a blue gradient
pal2 <- colorNumeric(palette = "Blues", domain = DataSet$Dist_M)

# Create the leaflet map
leaflet_distance <- leaflet(DataSet) %>%
  addTiles() %>%  # Add default OpenStreetMap tiles
  addCircleMarkers(
    lng = ~dd_long, lat = ~dd_lat, 
    radius = 10,  # Adjust the size of the markers
    color = ~pal2(Dist_M),  # Color the markers based on DataSet$Work using the red to blue gradient
    stroke = FALSE, fillOpacity = 1,  # Adjust opacity
    popup = ~paste("Collection Location:", Collection, "<br>", "Distance from Flats (m):", round(Dist_M)),  # Show Collection Location and distance value in popup
    label = ~Collection,  # Show Collection Location as label
    labelOptions = labelOptions(noHide = TRUE, direction = "top")
  ) %>%
  addLegend(
    position = "bottomright", 
    pal = pal2, values = ~Dist_M,  # Use DataSet$Work for legend
    title = "Distance from Coopper River Flats (m)", opacity = 1
  )  # Add legend for DataSet$Work

leaflet_distance


#topographical map of elevation for spawning sites
leaflet(DataSet) %>%
  addTiles() %>%  # Adds default OpenStreetMap tiles
  addProviderTiles("OpenTopoMap") %>% # Add Stamen Terrain tiles for topographical map
  addCircleMarkers(
    lng = ~dd_long, lat = ~dd_lat, 
    radius = 10,  # Adjust the size of the markers
    color = ~pal(elevation_M),  # Color the markers based on DataSet$Elevation using the red to blue gradient
    stroke = FALSE, fillOpacity = 1,  # Adjust opacity
    popup = ~paste("Collection Location:", Collection, "<br>", "Elevation (m):", elevation_M),  # Show Collection Location and Elevation value in popup
    label = ~Collection,  # Show Collection Location as label
    labelOptions = labelOptions(noHide = TRUE, direction = "top")
  ) %>%
  addLegend(
    position = "bottomright", 
    pal = pal, values = ~elevation_M,  # Use DataSet$Elevation for legend
    title = "Elevation (m)", opacity = 1
  )  # Add legend for DataSet$Elevation


leaflet(DataSet) %>%
  addTiles() %>%  # Adds default OpenStreetMap tiles
  addProviderTiles("OpenTopoMap") %>% # Add Stamen Terrain tiles for topographical map
  addCircleMarkers(
    lng = ~dd_long, lat = ~dd_lat, 
    radius = 10,  # Adjust the size of the markers
    color = ~pal2(Dist_M),  # Color the markers based on DataSet$Work using the red to blue gradient
    stroke = FALSE, fillOpacity = 1,  # Adjust opacity
    popup = ~paste("Collection Location:", Collection, "<br>", "Distance (m):", Dist_M),  # Show Collection Location and Work value in popup
    label = ~Collection,  # Show Collection Location as label
    labelOptions = labelOptions(noHide = TRUE, direction = "top")
  ) %>%
  addLegend(
    position = "bottomright", 
    pal = pal2, values = ~Dist_M,  # Use DataSet$Work for legend
    title = "Distance (m)", opacity = 1
  )  # Add legend for DataSet$Work

```












#' =====================================================
#' The Code for Calculating Migratory Difficulty for Spawning Populations (Elevation) -- would need to be completed in CR_2, with the respective inputfiles present
#' =====================================================

### Pete's initial code
```{r, include = FALSE}
#-----
#Estimate river mile for Baird, Canyon, and Chitina for modeling, try using Pete's code
# Reset R, clear all objects
rm(list=ls()) 

# Set WD
DataSet<- read.csv("InputFiles/upperriver_CollectionLocations_LatLong.csv")
unique(DataSet$Col_Location_Lat) 
unique(DataSet$Col_Location_Long) 

#So confirms we have 10 lat/longs for the 3 locations

#Required packages
library(sf)
library(elevatr)
library(tmap)
library(raster)
library(plyr)
library(readxl)
library(lubridate)
library(tmap)
library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(classInt)


#Read in shape files
CopperT<-sf::read_sf("InputFiles/CR_ShapeFiles/CopperRTribs.shp")
class(CopperT)
#watershed boundary
CopperWB<-sf::read_sf("InputFiles/CR_ShapeFiles/CopperRiverWBD.shp")

#convert to coordinates
CopperT = st_transform(CopperT, "+init=epsg:4326")
CopperWB = st_transform(CopperWB, "+init=epsg:4326")

#Read in elevation data
dem_Copper<-get_elev_raster(CopperWB,,z=7)
elev_crop = crop(dem_Copper, CopperWB)

slope = terrain(elev_crop, opt = "slope")
aspect = terrain(elev_crop, opt = "aspect")

hill = hillShade(slope, aspect, angle = 40, direction = 270)
masked_CR <- mask(hill, CopperWB)

#River network
river_sf = st_as_sf(CopperT)

# Ensure CRS consistency between CopperT and elev_crop
CT <- st_transform(CopperT, crs(elev_crop))  # Transform CopperT to the CRS of the raster

# Extract coordinates (longitude and latitude) from CopperT
coordinates_xy <- st_coordinates(CT)[, 1:2]  # Keep only the first two columns (longitude and latitude)

# Extract elevation values for each point from the raster
elevation_values <- extract(elev_crop, coordinates_xy)

# Create a data frame with x, y coordinates and corresponding elevation values (in meters ASL)
elevation_df <- data.frame(
  x = coordinates_xy[, 1],  # Longitude
  y = coordinates_xy[, 2],  # Latitude
  elevation = unlist(elevation_values)  # Elevation, unlisted in case it's a list
)

# View the result
head(elevation_df)

#setwd("C:/Users/PeteRand/OneDrive - Prince William Sound Science Center/RWorkingDirectory/CopperSalmonGitHub/CopperSalmon/InputFiles/PlaceNames/")

Copper_PlaceNames<-read.csv(file="InputFiles/PlaceNames/Copper_PlaceNames.csv")
Copper_PlaceNames<-Copper_PlaceNames[c(-5,-6),]
placenames_sf = st_as_sf (Copper_PlaceNames,coords = c("Longitude","Latitude"),crs = 4326, agr = "constant")

#Read in receiver station positions
Receiver_Loc<-read.csv(file="InputFiles/GroundReceiverStations/Receiver_Loc_For2005.csv")
Receiver_Loc<-read.csv("InputFiles/GroundReceiverStations/Receiver_Loc_For2005.csv")
receivers_sf = st_as_sf (Receiver_Loc,coords = c("Longitude","Latitude"),crs = 4326, agr = "constant")

#This produces map with ground receiver telemetry stations as red points.

map_CR = tm_shape(masked_CR) +
  tm_raster(palette = gray(7:10 / 10), style = "cont", legend.show = FALSE) +tm_shape(river_sf)+tm_lines(col = "blue") +
  tm_compass(position = c("right", "top"), size = 2) +tm_graticules(x=c(-146,-142),y=c(61,62,63),labels.size=1.2)+
  tm_scale_bar(position = c("right", "bottom"), width = 0.15, text.size =.6)+
  tm_shape(placenames_sf)+ tm_symbols(col = "black", size = .7, scale = .8,border.lwd=NA)+
  tm_text("Site",just="left",scale=.8,xmod=.1,ymod=-.3)+
  tm_shape(receivers_sf)+ tm_symbols(col = "red", size = .7, scale = .8,border.lwd=NA)+
  tm_text("Site.",just="left",scale=.8,xmod=.1,ymod=-.3)+
  tm_xlab("Longitude", size = 1.5, rotation = 0, space = 0)+
  tm_ylab("Latitude", size = 1.5, rotation = 90, space = 0)

map_CR
```

### Elevation Calculations
```{r, include = FALSE}
# Assuming you already have all necessary packages and data

# Step 1: Make sure upperriver_sf is in the same CRS as your DEM
upperriver_sf <- st_transform(upperriver_sf, crs = crs(elev_crop))  # Transform upperriver_sf to the CRS of the raster

# Step 2: Extract coordinates from upperriver_sf
coordinates_xy <- st_coordinates(upperriver_sf)[, 1:2]  # 10 extracted lat/longs

# Step 3: Extract elevation values for each point from the DEM raster
elevation_values <- extract(elev_crop, coordinates_xy)

# Step 4: Add elevation values to the upperriver_sf data
upperriver_sf$elevation.m <- unlist(elevation_values)  # Add extracted elevations to your sf object

# Check the result to see if elevation values were added
print(upperriver_sf)

elevation_df <- data.frame(
  Collection_Location = upperriver_sf$Collection_Location,  # Assuming this is the column name
  Longitude = coordinates_xy[, 1],
  Latitude = coordinates_xy[, 2],
  "Elevation.m" = unlist(elevation_values), # Elevation values from raster extraction 
  "Distance.m" = Coll_distances
)

# View the result (optional)
head(elevation_df)
print(elevation_df)



# Add the river_distance from Coll_distances to your elevation dataframe
UpperRiverSpawning_MigratoryDifficulty_df <- data.frame(
  Collection_Location = upperriver_sf$Collection_Location,  # Assuming this is the column name
  Longitude = st_coordinates(upperriver_sf)[, 1],  # Longitude
  Latitude = st_coordinates(upperriver_sf)[, 2],  # Latitude
  Elevation_m = unlist(elevation_values),  # Elevation values from raster extraction 
  River_Distance_m = st_distance(upperriver_sf, mouth_of_river)  # Get river distance for each point
)

# View the result (optional)
head(UpperRiverSpawning_MigratoryDifficulty_df)
print(UpperRiverSpawning_MigratoryDifficulty_df)

write.csv(UpperRiverSpawning_MigratoryDifficulty_df, "UpperRiverSpawning_MigratoryDifficulty.csv")

```